### 2019-07-14 paper.tex
Updates from Overleaf

% Template for ICASSP-2019 paper; to be used with:
% spconf.sty - ICASSP/ICIP LaTeX style file, and
% IEEEbib.bst - IEEE bibliography style file.
% --------------------------------------------------------------------------
\documentclass{article}
\usepackage{spconf,amsmath,graphicx}
\usepackage[tight,footnotesize]{subfigure} 
\usepackage{booktabs}
\usepackage[utf8]{inputenc}
\usepackage[sort,nocompress]{cite}

\DeclareUnicodeCharacter{2212}{-}

% Example definitions.
% --------------------
\def\x{{\mathbf x}}
\def\L{{\cal L}}

% Title.
% ------
\title{<title>}

\makeatletter
\def\@name{<authors>}
\makeatother

\address{<address>}

\begin{document}
\ninept
%
\maketitle
%
\begin{abstract}
\end{abstract}
%
\begin{keywords}
\end{keywords}
%
\section{Introduction}
\label{sec:intro}

\section{Theoretical Background}
\label{sec:back}

\subsection{Optical Flow}
\label{ssec:featSelection}

\subsection{Pose Estimation}
\label{ssec:featSelection}

The main goal of a pose estimation feature is to take, as input, a video sequence that contains human movement and generate the key-points indicating the basic human anatomical positioning (Figure~\ref{fig:pose}). This process receives a frame that is then used on a feed-forward network able to predict both sets of 2D confidence maps ($S$) of body member positioning and 2D vector fields ($L$) that calculate the degree of association between these members. The set $S$ = ($S1$, $S2$, ..., $SJ$), being $J$ the number of body parts found, and $L$ = ($L1$, $L2$, ..., $LC$), being $C$ the number of limbs, are parsed by greedy inference. Lastly, the algorithm produces the 2D key-points indicating the posture of all human components of the frame~\cite{cao2016realtime}.

\begin{figure}[!htb]
\centering
\subfigure{\includegraphics[height=2.6cm]{Images/pose_00013.jpg}} \hspace*{0.1cm}
\subfigure{\includegraphics[height=2.6cm]{Images/pose_00020.jpg}} \hspace*{0.1cm}
\subfigure{\includegraphics[height=2.6cm]{Images/pose_00025.jpg}}
\caption{Pose estimation output examples.}
\label{fig:pose}
\end{figure}

\subsection{Multi-Stream Model}
\label{ssec:MModel}

The multi-stream model concept~\cite{simonyan2014,wang2015towards}, used in this work, is a learning architecture (Figure~\ref{fig:multistream}). Therefore, we proposed the use of an individual isolated deep learning network for each of the hand-crafted features that were used. This singular approach focused on specializing a network according to each of its inputs.

\begin{figure}[!htb]
\centering
\includegraphics[width=8.5cm]{Images/multi_Diagram.eps}
\caption{Basic structure of a multi-stream approach.}
\label{fig:multistream}
\end{figure}

The main goal of this architecture is the possibility of working with the same input, however, the learning process employs distinct hand-crafted features regarding different combinations of information such as spatial, temporal, or spatial-temporal information. Accordingly, each feature-specialized network is considered a stream. Subsequent to the individual results achieved for each feature, an ensemble of these networks calculates the final classification results.

\subsection{Ensemble}
\label{ssec:esb}

In order to improve accuracy, new architectures have been developed. Thus, a useful approach is ensemble. Therefore, by arranging an ensemble, a number of different learning approaches are joined~\cite{dietterich2000ensemble}. The architectures used in an ensemble can be either the same, for example all them being an association of VGGs, or a combination of distinct structures such as VGG16 and AlexNet. However, the concept of ensemble relies on training each of these networks according to a specific input. Finally, after each learner computes their individual results, the one that has the majority of votes will have its results associated to the input.

\section{Multi-Stream Strategy for Fall Detection}
\label{sec:model}

The methodology proposed in this work aims to implement and evaluate an architecture based on convolutional neural networks (CNNs) to verify the existence of falls in videos. A VGG-16 was the CNN opted for this study since it is a classic convoluting method that can yield satisfactory results. Therefore, we consider detecting falls as a binary video classification problem.

\begin{figure*}[!htb]
\centering
\includegraphics[width=14.0cm]{Images/Final_diagram.eps}
\caption{Diagram of the proposed multi-stream strategy for fall detection.}
\label{fig:methodology}
\end{figure*}

Since datasets related to specific actions, such as falling, do not contain enough information to fully train a CNN, it was necessary to undergo two prior training steps before training the network with the definite features (Figure~\ref{fig:methodology}). First, each of the VGG-16, used for the streams, were trained with the Imagenet dataset~\cite{deng2009imagenet}. Even though Imagenet is composed of RGB images, it is useful so that the network can learn basic representations. After this procedure, the UCF101 dataset~\cite{soomro2012ucf101} had its optical flow generated and used to train the temporal (optical flow) stream once again so the model could learn explicit movement. Once this pre-training process was completed the consecutive step consisted in fine-tuning the two last fully connected VGG-16 layers using dropout regularization. The data that is used to fine-tune these last layers are acquired from a feature generating process (Figure~\ref{fig:methodology}).

%\begin{figure}[!htb]
%\centering
%\includegraphics[height = 3.5cm]{Images/pre-train.eps}
%\caption{Diagram of the proposed multi-stream strategy for fall detection.}
%\label{fig:train}
%\end{figure}

As it can be seen in Figure~\ref{fig:methodology} the proposed hand-crafted features (optical flow, pose estimation and RGB) are generated; we used the Gunner-Farneback~\cite{lowhur2015dense} and Cao et al.~\cite{cao2016realtime} algorithms as the optical flow and pose extractors, respectively. For a first stream, concerning frame relational information, since falling is a fast event and does not occupy the entire video sequence, the generated optical flow images are stacked. This stacking process receives a block size of $L$ frames and gathers 2$L$ components ($L$ horizontal ($d_t^x$) + $L$ vertical ($d_t^y$) optical flow component vector fields) creating a stack $O$ = \{$d_t^x$, $d_t^y$, $d_{t+1}^x$, $d_{t+1}^y$, ..., $d_{t+L}^x$, $d_{t+L}^y$ \}. The total number of stacks is given by $N$-$L$+$1$, where $N$ is the number of frames in a video and $L$ the size of the sliding block. This arrangement makes it possible for the CNN to have temporal relations calculated as well.The stacking procedure can be better understood by observing Figure~\ref{fig:stack}.

\begin{figure}[!htb]
\centering
\includegraphics[height=1.9cm]{Images/stack1.png}
\caption{Optical flow stacking process representation proposed by N\'u\~nez-Marcos et al.~\cite{nunez2017vision}. Sliding window of length 6.}
\label{fig:stack}
\end{figure}

A second stream is focused on a spatial representation of the person's posture on a video. Therefore, with this stream the method was able to specialize a learner based on relevant calculations from joint and member positioning sequences, common to falling events. In addition, on account of deep neural networks being able, through their layers, to learn what are relevant features that it can use to describe an input, a third stream was constructed in our multi-stream learner. This perspective was used to train a stream of the architecture using the raw RGB pixel values as training data instead of extracting events from it, as mentioned previously.

After generating these hand-crafted features, the following step refers to a stream feature vector extractor. For each of the chosen hand-crafted streams, the generated images go through a modified CNN feature extractor so that a feature vector can be calculated and used in the fine-tuning process. This suggests that, after training the 14 first layers with both Imagenet and UCF101, the two last dense layers from the VGG-16 received the calculated feature vector, for each of the generated hand-crafted features, as inputs. This procedure permits the learning model to process numerous frame information and consider motion movement.

As a final part of our learner, it was imperative that the individual classifications achieved for a given input from each isolated stream were computed to obtain the final output. For this stage, an ensembling techniques was employed. This method was based on a Support Vector Machine (SVM), the stream outputs (between 0 and 1) are used to generate a ($x$, $y$, $z$) vector to be used, as input, to the SVM classifier. However, it is our understanding that the SVM is an additional learning process within the proposed architecture. Thus, it implies on being more costly than using an average method.

Although the optical flow learning architecture stream is based on the one used by N\'u\~nez-Marcos et al.~\cite{nunez2017vision}, in this study a multi-stream model was used. Therefore, as discussed, instead of focusing the results on a single classifier, multiple pre-classifiers were adopted. In addition, rather than operating with one hand-crafted feature, three features are considered.

\section{Experiments}
\label{sec:experiments}

 The datasets used in our experiments were the URFD~\cite{kwolek2014human} and FDD datasets. The URFD dataset encompasses a set of 70 videos being 30 videos of falls and 40 videos containing other activities that are considered not fall. FDD contains 191 realistic single camera surveillance videos from both elderly home environments, and office rooms. The primary metrics used for these evaluations were accuracy, specificity and sensitivity considering that most of the approaches presented in literature validate their systems using them.

\begin{table*}[!htb]
\renewcommand{\tabcolsep}{6.0mm}
\centering
\caption{FDD results for the best configuration values found by N\'u\~nez-Marcos et al.~\cite{nunez2017vision}.}
\label{tab:FDD}
\begin{tabular}{lccc}
\toprule
 & Sensitivity (\%) & Specificity (\%) & Accuracy (\%) \\
\midrule
Multi-stream (OF+PE+RGB) & 99.9  & 98.32 & 98.43 \\
Multi-stream (OF) & 99.9 & 96.17 & 96.43 \\
Multi-stream (RGB)& 100	 & 79.02 & 80.52\\
Multi-stream (PE) &	100	 & 60.15 & 63.01\\
\midrule
N\'u\~nez-Marcos et al.~\cite{nunez2017vision} & 99.0 & 97.00 & 97.00 \\
Zerrouki and Houacine~\cite{zerrouki2018combined} & - & - & 97.02 \\
Charfi et al.~\cite{charfi2012definition} & 98.0 & 99.60 & - \\
\midrule
\end{tabular}
\end{table*}

\begin{table*}[!htb]
\renewcommand{\tabcolsep}{6.0mm}
\centering
\caption{URFD results for the best configuration values found by N\'u\~nez-Marcos et al.~\cite{nunez2017vision}.}
\label{tab:URFD}
\begin{tabular}{lccc}
\toprule
 & Sensitivity (\%) & Specificity (\%) & Accuracy (\%) \\
 \midrule
Multi-stream (OF+PE+RGB) & 100 & 98.61 & 98.77 \\
Multi-stream (OF) & 100 & 96.34 & 96.75 \\
Multi-stream (RGB)& 100	& 96.61	& 96.99\\
Multi-stream (PE) &	94.41 &	93,09 &	93,24\\
\midrule
N\'u\~nez-Marcos et al.~\cite{nunez2017vision} & 100 & 92.00 & 95.00 \\
Zerrouki and Houacine~\cite{zerrouki2018combined} & - & - & 96.88 \\
Kwolek and Kepski~\cite{kwolek2015improving} & 100 & 92.50 & 95.71 \\
\midrule
\end{tabular}
\end{table*}

To the best of our knowledge, since there are no other works that use a frame stacking method as described in the previous section, and the basic architecture of a stream is similar, the main comparisons are made regarding N\'u\~nez-Marcos et al.~\cite{nunez2017vision} work. Results were also compared method-wise to Zerrouki and Houacine~\cite{zerrouki2018combined}, Kwolek and Kepski~\cite{kwolek2015improving} and Charfi et al.~\cite{charfi2012definition} since they have tested with the same datasets as ours.

Experiments were conducted by considering N\'u\~nez-Marcos et al.~\cite{nunez2017vision} hyper-parameter best configurations, so that the studies could be easily compared. Hence, tests were performed by dividing the data into training and testing sets with 80\% and 20\%, respectively. Considering falling a threatening situation, the \textit{fall} class was given a weight of two instead of one. This means that it is more important to detect a fall rather than having a critical false negative result. Learning rate values were tested with $10^{−3}$ to $10^{−5}$. The batch sizes ranged between powers of 2 and experiments ran in 500 to 1000 epochs. The optimization used for the networks parameters was Adam. The results of the 5-fold shuffled cross-validation can be seen in Tables~\ref{tab:FDD} and~\ref{tab:URFD}.

Although N\'u\~nez-Marcos et al.~\cite{nunez2017vision} did not use a shuffled 5-fold cross-validation to calculate the metric results and the optical flow image generator algorithm was different from the current approach, temporal tests were made considering a single stream using our optical flow and metrics so the results could be directly compared (Multi-stream (OF) row in Tables~\ref{tab:FDD} and~\ref{tab:URFD}). As it was presented in Tables~\ref{tab:FDD} and~\ref{tab:URFD}, our multi-stream learning model with three streams was capable of performing better than the other approaches.

The best configuration for this comparison was found when the learning rate value was tested with $10^{−4}$, batch size of 1024, \textit{fall} class with weight 2 and the optical flow sliding block with size 10. Further improvements can be seen since the best results found in N\'u\~nez-Marcos et al.~\cite{nunez2017vision} ran with about 3000 epochs compared to their work, that is, 500.

In Tables~\ref{tab:FDD} and~\ref{tab:URFD}, it is also possible to analyze the performance of our multi-stream proposal using a single stream. Although not many experiments were focused on improving the results for the individual stream, it can be observed that the isolated learners did not perform as good as the associated ones with these hyper-parameters. However, this proves that multi-stream model can assist on classification since an outlier result yielded by one of the streams can be corrected based on the other streams results.

Considering the data set classification, it is clear that the multi-stream with three streams used for this study outperformed the single VGG-16, the hidden Markov model, the SVM and the KNN methods used in N\'u\~nez-Marcos et al.~\cite{nunez2017vision}, Zerrouki and Houacine~\cite{zerrouki2018combined}, Charfi et al.~\cite{charfi2012definition}, and Kwolek and Kepski~\cite{kwolek2015improving}, respectively.

\section{Conclusions and Future Work}
\label{sec:conclusion}

In this work, we proposed and evaluated a multi-stream learning model based on convolutional neural networks to cope with a binary falling classification problem. Therefore, our approach consisted in extracting hand-crafted high-level features (optical flow, pose estimation) and the RGB video data itself from public data set videos and use each as an input for a distinct VGG-16 classifier. Results have demonstrated to be better than other similar literature works in most of the calculated metrics.

It is our understanding that a multi-stream model can assist on classification since an outlier result outputted by one of the streams can be corrected based on the other streams results. Using hand-crafted high-level features also assisted in covering unnecessary information from the video frames such as the background and other unimportant details. Therefore, the network could learn specific movement and posture related features. Moreover, these features can also assist on identity concealing if necessary.

For future work, we intend to continue investigating relevant high-level features used for fall detection. In addition, studies will be conducted to testing better hyper-parameters for the individual learners and use other architectures for each stream. Finally, experimentation will be done considering our method's general applicability.

\bibliographystyle{IEEEbib}
\bibliography{paper}

\end{document}

### 2019-07-14 paper.tex
1338

@@
 
-The main goal of a pose estimation feature is to take, as input, a video sequence that contains human movement and generate the key-points indicating the basic human anatomical positioning (Figure~\ref{fig:pose}).
-This process receives a frame that is then used on a feed-forward network able to predict both sets of 2D confidence maps ($S$) of body member positioning and 2D vector fields ($L$) that calculate the degree of association between these members.
-The set $S$ = ($S1$, $S2$, ..., $SJ$), being $J$ the number of body parts found, and $L$ = ($L1$, $L2$, ..., $LC$), being $C$ the number of limbs, are parsed by greedy inference.
-Lastly, the algorithm produces the 2D key-points indicating the posture of all human components of the frame~\cite{cao2016realtime}.
-
-\begin{figure}[!htb]
-\centering
-\subfigure{\includegraphics[height=2.6cm]{Images/pose_00013.jpg}} \hspace*{0.1cm}
-\subfigure{\includegraphics[height=2.6cm]{Images/pose_00020.jpg}} \hspace*{0.1cm}
-\subfigure{\includegraphics[height=2.6cm]{Images/pose_00025.jpg}}
-\caption{Pose estimation output examples.}
-\label{fig:pose}
-\end{figure}
-
 \subsection{Multi-Stream Model}
 \label{ssec:MModel}
-
-The multi-stream model concept~\cite{simonyan2014,wang2015towards}, used in this work, is a learning architecture (Figure~\ref{fig:multistream}).
-Therefore, we proposed the use of an individual isolated deep learning network for each of the hand-crafted features that were used.
-This singular approach focused on specializing a network according to each of its inputs.
-
-\begin{figure}[!htb]
-\centering
-\includegraphics[width=8.5cm]{Images/multi_Diagram.eps}
-\caption{Basic structure of a multi-stream approach.}
-\label{fig:multistream}
-\end{figure}
-
-The main goal of this architecture is the possibility of working with the same input, however, the learning process employs distinct hand-crafted features regarding different combinations of information such as spatial, temporal, or spatial-temporal information.
-Accordingly, each feature-specialized network is considered a stream.
-Subsequent to the individual results achieved for each feature, an ensemble of these networks calculates the final classification results.
 
@@
 
-In order to improve accuracy, new architectures have been developed.
-Thus, a useful approach is ensemble.
-Therefore, by arranging an ensemble, a number of different learning approaches are joined~\cite{dietterich2000ensemble}.
-The architectures used in an ensemble can be either the same, for example all them being an association of VGGs, or a combination of distinct structures such as VGG16 and AlexNet.
-However, the concept of ensemble relies on training each of these networks according to a specific input.
-Finally, after each learner computes their individual results, the one that has the majority of votes will have its results associated to the input.
-
 \section{Multi-Stream Strategy for Fall Detection}
 \label{sec:model}
-
-The methodology proposed in this work aims to implement and evaluate an architecture based on convolutional neural networks (CNNs) to verify the existence of falls in videos.
-A VGG-16 was the CNN opted for this study since it is a classic convoluting method that can yield satisfactory results.
-Therefore, we consider detecting falls as a binary video classification problem.
-
-\begin{figure*}[!htb]
-\centering
-\includegraphics[width=14.0cm]{Images/Final_diagram.eps}
-\caption{Diagram of the proposed multi-stream strategy for fall detection.}
-\label{fig:methodology}
-\end{figure*}
-
-Since datasets related to specific actions, such as falling, do not contain enough information to fully train a CNN, it was necessary to undergo two prior training steps before training the network with the definite features (Figure~\ref{fig:methodology}).
-First, each of the VGG-16, used for the streams, were trained with the Imagenet dataset~\cite{deng2009imagenet}.
-Even though Imagenet is composed of RGB images, it is useful so that the network can learn basic representations.
-After this procedure, the UCF101 dataset~\cite{soomro2012ucf101} had its optical flow generated and used to train the temporal (optical flow) stream once again so the model could learn explicit movement.
-Once this pre-training process was completed the consecutive step consisted in fine-tuning the two last fully connected VGG-16 layers using dropout regularization.
-The data that is used to fine-tune these last layers are acquired from a feature generating process (Figure~\ref{fig:methodology}).
-
-%\begin{figure}[!htb]
-%\centering
-%\includegraphics[height = 3.5cm]{Images/pre-train.eps}
-%\caption{Diagram of the proposed multi-stream strategy for fall detection.}
-%\label{fig:train}
-%\end{figure}
-
-As it can be seen in Figure~\ref{fig:methodology} the proposed hand-crafted features (optical flow, pose estimation and RGB) are generated; we used the Gunner-Farneback~\cite{lowhur2015dense} and Cao et al.~\cite{cao2016realtime} algorithms as the optical flow and pose extractors, respectively.
-For a first stream, concerning frame relational information, since falling is a fast event and does not occupy the entire video sequence, the generated optical flow images are stacked.
-This stacking process receives a block size of $L$ frames and gathers 2$L$ components ($L$ horizontal ($d_t^x$) + $L$ vertical ($d_t^y$) optical flow component vector fields) creating a stack $O$ = \{$d_t^x$, $d_t^y$, $d_{t+1}^x$, $d_{t+1}^y$, ..., $d_{t+L}^x$, $d_{t+L}^y$ \}.
-The total number of stacks is given by $N$-$L$+$1$, where $N$ is the number of frames in a video and $L$ the size of the sliding block.
-This arrangement makes it possible for the CNN to have temporal relations calculated as well.The stacking procedure can be better understood by observing Figure~\ref{fig:stack}.
-
-\begin{figure}[!htb]
-\centering
-\includegraphics[height=1.9cm]{Images/stack1.png}
-\caption{Optical flow stacking process representation proposed by N\'u\~nez-Marcos et al.~\cite{nunez2017vision}. Sliding window of length 6.}
-\label{fig:stack}
-\end{figure}
-
-A second stream is focused on a spatial representation of the person's posture on a video.
-Therefore, with this stream the method was able to specialize a learner based on relevant calculations from joint and member positioning sequences, common to falling events.
-In addition, on account of deep neural networks being able, through their layers, to learn what are relevant features that it can use to describe an input, a third stream was constructed in our multi-stream learner.
-This perspective was used to train a stream of the architecture using the raw RGB pixel values as training data instead of extracting events from it, as mentioned previously.
-
-After generating these hand-crafted features, the following step refers to a stream feature vector extractor.
-For each of the chosen hand-crafted streams, the generated images go through a modified CNN feature extractor so that a feature vector can be calculated and used in the fine-tuning process.
-This suggests that, after training the 14 first layers with both Imagenet and UCF101, the two last dense layers from the VGG-16 received the calculated feature vector, for each of the generated hand-crafted features, as inputs.
-This procedure permits the learning model to process numerous frame information and consider motion movement.
-
-As a final part of our learner, it was imperative that the individual classifications achieved for a given input from each isolated stream were computed to obtain the final output.
-For this stage, an ensembling techniques was employed.
-This method was based on a Support Vector Machine (SVM), the stream outputs (between 0 and 1) are used to generate a ($x$, $y$, $z$) vector to be used, as input, to the SVM classifier.
-However, it is our understanding that the SVM is an additional learning process within the proposed architecture.
-Thus, it implies on being more costly than using an average method.
-
-Although the optical flow learning architecture stream is based on the one used by N\'u\~nez-Marcos et al.~\cite{nunez2017vision}, in this study a multi-stream model was used.
-Therefore, as discussed, instead of focusing the results on a single classifier, multiple pre-classifiers were adopted.
-In addition, rather than operating with one hand-crafted feature, three features are considered.
 
@@
 
- The datasets used in our experiments were the URFD~\cite{kwolek2014human} and FDD datasets.
-The URFD dataset encompasses a set of 70 videos being 30 videos of falls and 40 videos containing other activities that are considered not fall.
-FDD contains 191 realistic single camera surveillance videos from both elderly home environments, and office rooms.
-The primary metrics used for these evaluations were accuracy, specificity and sensitivity considering that most of the approaches presented in literature validate their systems using them.
-
-\begin{table*}[!htb]
-\renewcommand{\tabcolsep}{6.0mm}
-\centering
-\caption{FDD results for the best configuration values found by N\'u\~nez-Marcos et al.~\cite{nunez2017vision}.}
-\label{tab:FDD}
-\begin{tabular}{lccc}
-\toprule
- & Sensitivity (\%) & Specificity (\%) & Accuracy (\%) \\
-\midrule
-Multi-stream (OF+PE+RGB) & 99.9  & 98.32 & 98.43 \\
-Multi-stream (OF) & 99.9 & 96.17 & 96.43 \\
-Multi-stream (RGB)& 100	 & 79.02 & 80.52\\
-Multi-stream (PE) &	100	 & 60.15 & 63.01\\
-\midrule
-N\'u\~nez-Marcos et al.~\cite{nunez2017vision} & 99.0 & 97.00 & 97.00 \\
-Zerrouki and Houacine~\cite{zerrouki2018combined} & - & - & 97.02 \\
-Charfi et al.~\cite{charfi2012definition} & 98.0 & 99.60 & - \\
-\midrule
-\end{tabular}
-\end{table*}
-
-\begin{table*}[!htb]
-\renewcommand{\tabcolsep}{6.0mm}
-\centering
-\caption{URFD results for the best configuration values found by N\'u\~nez-Marcos et al.~\cite{nunez2017vision}.}
-\label{tab:URFD}
-\begin{tabular}{lccc}
-\toprule
- & Sensitivity (\%) & Specificity (\%) & Accuracy (\%) \\
- \midrule
-Multi-stream (OF+PE+RGB) & 100 & 98.61 & 98.77 \\
-Multi-stream (OF) & 100 & 96.34 & 96.75 \\
-Multi-stream (RGB)& 100	& 96.61	& 96.99\\
-Multi-stream (PE) &	94.41 &	93,09 &	93,24\\
-\midrule
-N\'u\~nez-Marcos et al.~\cite{nunez2017vision} & 100 & 92.00 & 95.00 \\
-Zerrouki and Houacine~\cite{zerrouki2018combined} & - & - & 96.88 \\
-Kwolek and Kepski~\cite{kwolek2015improving} & 100 & 92.50 & 95.71 \\
-\midrule
-\end{tabular}
-\end{table*}
-
-To the best of our knowledge, since there are no other works that use a frame stacking method as described in the previous section, and the basic architecture of a stream is similar, the main comparisons are made regarding N\'u\~nez-Marcos et al.~\cite{nunez2017vision} work.
-Results were also compared method-wise to Zerrouki and Houacine~\cite{zerrouki2018combined}, Kwolek and Kepski~\cite{kwolek2015improving} and Charfi et al.~\cite{charfi2012definition} since they have tested with the same datasets as ours.
-
-Experiments were conducted by considering N\'u\~nez-Marcos et al.~\cite{nunez2017vision} hyper-parameter best configurations, so that the studies could be easily compared.
-Hence, tests were performed by dividing the data into training and testing sets with 80\% and 20\%, respectively.
-Considering falling a threatening situation, the \textit{fall} class was given a weight of two instead of one.
-This means that it is more important to detect a fall rather than having a critical false negative result.
-Learning rate values were tested with $10^{−3}$ to $10^{−5}$.
-The batch sizes ranged between powers of 2 and experiments ran in 500 to 1000 epochs.
-The optimization used for the networks parameters was Adam.
-The results of the 5-fold shuffled cross-validation can be seen in Tables~\ref{tab:FDD} and~\ref{tab:URFD}.
-
-Although N\'u\~nez-Marcos et al.~\cite{nunez2017vision} did not use a shuffled 5-fold cross-validation to calculate the metric results and the optical flow image generator algorithm was different from the current approach, temporal tests were made considering a single stream using our optical flow and metrics so the results could be directly compared (Multi-stream (OF) row in Tables~\ref{tab:FDD} and~\ref{tab:URFD}).
-As it was presented in Tables~\ref{tab:FDD} and~\ref{tab:URFD}, our multi-stream learning model with three streams was capable of performing better than the other approaches.
-
-The best configuration for this comparison was found when the learning rate value was tested with $10^{−4}$, batch size of 1024, \textit{fall} class with weight 2 and the optical flow sliding block with size 10.
-Further improvements can be seen since the best results found in N\'u\~nez-Marcos et al.~\cite{nunez2017vision} ran with about 3000 epochs compared to their work, that is, 500.
-
-In Tables~\ref{tab:FDD} and~\ref{tab:URFD}, it is also possible to analyze the performance of our multi-stream proposal using a single stream.
-Although not many experiments were focused on improving the results for the individual stream, it can be observed that the isolated learners did not perform as good as the associated ones with these hyper-parameters.
-However, this proves that multi-stream model can assist on classification since an outlier result yielded by one of the streams can be corrected based on the other streams results.
-
-Considering the data set classification, it is clear that the multi-stream with three streams used for this study outperformed the single VGG-16, the hidden Markov model, the SVM and the KNN methods used in N\'u\~nez-Marcos et al.~\cite{nunez2017vision}, Zerrouki and Houacine~\cite{zerrouki2018combined}, Charfi et al.~\cite{charfi2012definition}, and Kwolek and Kepski~\cite{kwolek2015improving}, respectively.
+Our method was evaluated in two publicly available datasets: URFD~\ref{} and FDD~\ref{}.
 
@@
 \label{sec:conclusion}
-
-In this work, we proposed and evaluated a multi-stream learning model based on convolutional neural networks to cope with a binary falling classification problem.
-Therefore, our approach consisted in extracting hand-crafted high-level features (optical flow, pose estimation) and the RGB video data itself from public data set videos and use each as an input for a distinct VGG-16 classifier.
-Results have demonstrated to be better than other similar literature works in most of the calculated metrics.
-
-It is our understanding that a multi-stream model can assist on classification since an outlier result outputted by one of the streams can be corrected based on the other streams results.
-Using hand-crafted high-level features also assisted in covering unnecessary information from the video frames such as the background and other unimportant details.
-Therefore, the network could learn specific movement and posture related features.
-Moreover, these features can also assist on identity concealing if necessary.
-
-For future work, we intend to continue investigating relevant high-level features used for fall detection.
-In addition, studies will be conducted to testing better hyper-parameters for the individual learners and use other architectures for each stream.
-Finally, experimentation will be done considering our method's general applicability.
 

### 2019-07-15 paper.tex
1443
Updates from Overleaf

@@
-% Template for ICASSP-2019 paper; to be used with:
-% spconf.sty - ICASSP/ICIP LaTeX style file, and
-% IEEEbib.bst - IEEE bibliography style file.
-% --------------------------------------------------------------------------
-\documentclass{article}
-\usepackage{spconf,amsmath,graphicx}
-\usepackage[tight,footnotesize]{subfigure} 
-\usepackage{booktabs}
-\usepackage[utf8]{inputenc}
-\usepackage[sort,nocompress]{cite}
+\documentclass[conference]{IEEEtran}
+\IEEEoverridecommandlockouts
+% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
+\usepackage{cite}
+\usepackage{amsmath,amssymb,amsfonts}
+\usepackage{algorithmic}
+\usepackage{graphicx}
+\usepackage{textcomp}
+\usepackage{xcolor}
+\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
+    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
+\begin{document}
 
-\DeclareUnicodeCharacter{2212}{-}
+\title{Paper Title*\\
+\thanks{Identify applicable funding agency here. If none, delete this.}
+}
 
-% Example definitions.
-% --------------------
-\def\x{{\mathbf x}}
-\def\L{{\cal L}}
+\author{\IEEEauthorblockN{1\textsuperscript{st} Given Name Surname}
+\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
+\textit{name of organization (of Aff.)}\\
+City, Country \\
+email address}
+\and
+\IEEEauthorblockN{2\textsuperscript{nd} Given Name Surname}
+\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
+\textit{name of organization (of Aff.)}\\
+City, Country \\
+email address}
+\and
+\IEEEauthorblockN{3\textsuperscript{rd} Given Name Surname}
+\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
+\textit{name of organization (of Aff.)}\\
+City, Country \\
+email address}
+\and
+\IEEEauthorblockN{4\textsuperscript{th} Given Name Surname}
+\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
+\textit{name of organization (of Aff.)}\\
+City, Country \\
+email address}
+\and
+\IEEEauthorblockN{5\textsuperscript{th} Given Name Surname}
+\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
+\textit{name of organization (of Aff.)}\\
+City, Country \\
+email address}
+\and
+\IEEEauthorblockN{6\textsuperscript{th} Given Name Surname}
+\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
+\textit{name of organization (of Aff.)}\\
+City, Country \\
+email address}
+}
 
-% Title.
-% ------
-\title{<title>}
+\maketitle
 
-\makeatletter
-\def\@name{<authors>}
-\makeatother
+\begin{abstract}
+This document is a model and instructions for \LaTeX.
+This and the IEEEtran.cls file define the components of your paper [title, text, heads, etc.]. *CRITICAL: Do Not Use Symbols, Special Characters, Footnotes, 
+or Math in Paper Title or Abstract.
+\end{abstract}
 
-\address{<address>}
+\begin{IEEEkeywords}
+component, formatting, style, styling, insert
+\end{IEEEkeywords}
 
-\begin{document}
-\ninept
-%
-\maketitle
-%
-\begin{abstract}
-\end{abstract}
-%
-\begin{keywords}
-\end{keywords}
-%
 \section{Introduction}
-\label{sec:intro}
 
-\section{Theoretical Background}
-\label{sec:back}
+\section{Related Work}
+
+\section{Background}
 
 \subsection{Optical Flow}
-\label{ssec:featSelection}
 
-\subsection{Pose Estimation}
-\label{ssec:featSelection}
+\subsection{Saliency}
 
-\subsection{Multi-Stream Model}
-\label{ssec:MModel}
+\section{Our Method}
 
-\subsection{Ensemble}
-\label{ssec:esb}
-
-\section{Multi-Stream Strategy for Fall Detection}
-\label{sec:model}
+\color{red}
+\centering
+\textbf{\textit{MAYBE}}
+\color{black}
 
 \section{Experiments}
-\label{sec:experiments}
 
-Our method was evaluated in two publicly available datasets: URFD~\ref{} and FDD~\ref{}.
+Our experiments were performed on two publicly available datasets, \textit{URFD}~\cite{kepski2014human} and \textit{FDD}~\cite{charfi2013optimised}.
 
-\section{Conclusions and Future Work}
-\label{sec:conclusion}
+\paragraph{URFD} dataset contains 70 videos: (i) 30 videos of falls; and (ii) 40 videos of daily living activities, recorded from a top-down and side view perspective by two Microsoft Kinect cameras.
+Each frame is labeled in three categories, whether the person is lying on the ground, not lying on the ground or in an intermediate pose.
+\paragraph{FDD} dataset is composed of 191 videos of which 107 are falls, recorded from a surveillance camera perspective by a single RGB camera. With every frame annotated between fall and not fall.
 
-\bibliographystyle{IEEEbib}
-\bibliography{paper}
+For the sake of comparison with other works in the literature we evaluated our method by three metrics: (i) Sensitivity reflecting the number of true positives, (ii) Specificity also known as the true negative rate, and (iii) Accuracy representing the overall performance of the method.
+
+We experimented with different class weights, and with further tunning of the hyper parameters we were able to set all classes with the same weight.
+
+learning rate 0.0001, kfold 5, minibatches of 1024, 500 epochs, optimization with adam, each fold result for the three stream combination
+
+The ensemble was performed by the svm approach discussed in section
+
+Compared ensembles techniques, SVM vs avarage
+
+Each individual stream does not perform greatly when used alone, but the ensemble of them has a significant improved result
+
+And the following results were obtained in the FDD dataset
+
+The false negative cases must be taken care since they would be responsible for serious injuries and such
+
+The following results were obatined in the URFD dataset
+
+\begin{table*}[t]
+\centering
+\caption{URFD comparison between individuas streams and ensemble.}
+\label{tab:urfd-ensem}
+\begin{tabular}{llcccl}
+\hline
+ &  & Sensitivity (\%) & Specificity (\%) & Accuracy (\%) &  \\ \hline
+ & Multi-stream (OF+RGB+Sal) & \textbf{100} & \textbf{98.77} & \textbf{98.84} &  \\
+ & Single-stream (OF) & \textbf{100} & 97.42 & 97.57 &  \\
+ & Single-stream (RGB) & \textbf{100} & 96.35 & 96.56 &  \\
+ & Single-stream (Sal) & 93.67 & 93.39 & 93.40 & \\ \hline
+\end{tabular}
+\end{table*}
+
+\begin{table*}[t]
+\centering
+\caption{URFD comparison between results.}
+\label{tab:urfd-our-their}
+\begin{tabular}{llcccl}
+\hline
+ &                              & Sensitivity (\%) & Specificity (\%) & Accuracy (\%)  &  \\ \hline
+ & Ours                         & \textbf{100}      & \textbf{98.77}   & \textbf{98.84} &  \\
+ & N\'u\~nez-Marcos et al.~\cite{nunez2017vision}      & \textbf{100}      & 92.00            & 95.00          &  \\
+ & Zerrouki and Houacine~\cite{zerrouki2018vision}  & -                & -                & 96.88          &  \\
+ & Bhandari et al.~\cite{bhandari2017novel}  & 96.66                & -                & 95.71          &  \\
+ & Harrou et al.~\cite{harrou2017vision}  & -                & -                & 96.66          &  \\
+ & Sase et al.~\cite{sase2018human}  & 81.00                & -                & 90.00          &  \\
+ & Kwolek and Kepski~\cite{kepski2014human}            & \textbf{100}     & 92.50            & 95.71          &  \\ \hline
+\end{tabular}
+\end{table*}
+
+\begin{table*}[t]
+\centering
+\caption{FDD comparison between individuas streams and ensemble.}
+\label{tab:fdd-ensem}
+\begin{tabular}{llcccl}
+\hline
+ &                      & Sensitivity (\%)  & Specificity (\%)  & Accuracy (\%)     &  \\ \hline
+ & Multi (OF+RGB+Sal)   & \textbf{99.43}    & \textbf{99.55}    & \textbf{99.51}    &  \\
+ & Single (OF)          & 99.07             & 99.12             & 99.11             &  \\
+ & Single (RGB)         & 98.85             & 98.41             & 98.55             &  \\
+ & Single (Sal)         & 88.39             & 92.40             & 91.25             & \\ \hline
+\end{tabular}
+\end{table*}
+
+\begin{table*}[t]
+\centering
+\caption{FDD comparison between results.}
+\label{tab:fdd-our-their}
+\begin{tabular}{llcccl}
+\hline
+ &                          & Sensitivity (\%)  & Specificity (\%)  & Accuracy (\%)     & \\ \hline
+ & Ours                     & \textbf{99.43}    & 99.55             & \textbf{99.51}    & \\
+ & N\'u\~nez-Marcos et al.~\cite{nunez2017vision}  & 99.0              & 97.00             & 97.00             & \\
+ & Zerrouki and Houacine~\cite{zerrouki2018vision}    & -                 & -                 & 97.02             & \\
+ & Harrou et al.~\cite{harrou2017vision}    & -                 & -                 & 97.02             & \\
+ & Charfi et al.~\cite{charfi2013optimised}            & 98.0              & \textbf{99.60}    & -                 & \\ \hline
+\end{tabular}
+\end{table*}
+
+ It is worth nothing that in health segments, as a general rule it is usually preferred to accuse a false negative over a false positive, for instance it is considered that a HIV test with a false positive result will cause major distress on the patient's life, and if that result were a false negative, eventually the decease shymtons would demand another test.
+This general rule doesn't stand in our scenario, even tough a false positive would trigger a help dispatch which could cause some hassle to the patient, the aftereffects of a fall are related to the time between a fall and the help arrival, as observed by et al.~\cite{}.
+
+\section{Future Work}
+
+\section*{Acknowledgment}
+
+\begin{thebibliography}{00}
+\end{thebibliography}
+
+\color{red}
+\centering
+EIGHT PAGES
 

### 2019-07-16 paper.tex
Updates from Overleaf

@@
 
-\section{Our Method}
+\section{Method}
 
-\color{red}
-\centering
-\textbf{\textit{MAYBE}}
-\color{black}
+An ensemble of VGG-16s were employed and evaluated to classify fall and not fall in video sequences, as seen in Figure~\ref{fig:overview} and further detailed bellow.
+
+% In this work we intended to employ and evaluate a CNN architecture capable of detecting the presence or not of falls in videos, thus approaching the problem as a binary classification.
+To this end, we select the CNN architecture VGG16, since it is well known, and yields satisfactory results.
+Furthermore, based on the results of Wang et al.~\cite{wang2015towards}, in which a multi-streamed CNN outperformed single-stream ones, a ensembled was also exerted to learn the influence of three selected streams, each stream fed with a hand-crafted feature, them being: (i) optical flow, (ii) rgb, and (iii) saliency map.
+
+\subsection{Transfer Learning}
+
+The selected datasets, further detailed in Section~\ref{sec:experiments}, possesses a relatively small amount of human fall samples in their videos, which would limit the CNNs learning capabilities to detect a fall event.
+Thus, the need to transfer learning from other datasets.
+
+The first 14 layers of the VGG-16 architecture were trained on the ImageNet~\cite{imagenet_cvpr09} dataset, and later on, these same layers were fine-tuned over the UCF101~\cite{soomro2012ucf101} dataset.
+The reasoning being that the network would initially learn low level features from the ImageNet classes, and focus these features on human activities with the UCF101 videos, Figure~\ref{fig:pre14}.
+
+The 14 initial layer's weights were then frozen, and the last two fully connected layers were separately fine-tuned, with dropout regularization, over the extracted hand-crafted features of the URFD~\cite{kepski2014human} and FDD~\cite{charfi2013optimised} datasets.
+This last fine-tuning was performed three times, one for each of the extracted hand-crafted features, Figure~\ref{fig:pos14}.
+
+\subsection{Hand-crafted Features}
+
+stacking MAYBE
+
+\subsection{Classification}
+
+svm
 
 \section{Experiments}
+\label{sec:experiments}
 
@@
 
-\begin{thebibliography}{00}
-\end{thebibliography}
+%\begin{thebibliography}{00}
+%\end{thebibliography}
+
+\bibliographystyle{IEEEtran}
+\bibliography{paper}
 

### 2019-07-16 paper.tex
Updates from Overleaf

@@
 
-\subsection{Saliency}
+\subsection{Saliency Map}
+\label{sec:saliency}
+
+Why were you selected?
 
@@
 The 14 initial layer's weights were then frozen, and the last two fully connected layers were separately fine-tuned, with dropout regularization, over the extracted hand-crafted features of the URFD~\cite{kepski2014human} and FDD~\cite{charfi2013optimised} datasets.
-This last fine-tuning was performed three times, one for each of the extracted hand-crafted features, Figure~\ref{fig:pos14}.
-
-\subsection{Hand-crafted Features}
-
-stacking MAYBE
+The last fine-tuning was performed three times, one for each of the extracted hand-crafted features, Figure~\ref{fig:pos14}.
 
 \subsection{Classification}
+\label{sec:classification}
 
-svm
+Wang et al.~\cite{wang2015towards} reported that networks employing multi-stream classifiers outperformed their single-streamed peers.
+Inspired on this finding, a SVM classifier fed with the outputs of each stream, between 0 and 1, generates a ($x$, $y$, $z$) vector.
+This vector is then fed to a second SVM that classifies between fall and not fall, Figure~\ref{fig:pos14}.
+
+\subsection{Streams Input}
+
+Two selected features were fed to the streams explained in Subsection~\ref{sec:classification}:(i) Optical Flow and (ii) Saliency Map.
+Furthermore, the RGB frame itself was fed to the third stream, Figure~\ref{fig:features}, given the neural networks capability to learn relevant features to describe their input.
+
+\paragraph{Optical Flow} represents the temporal relation between frames, and to fully gather this property it was used as a stack of optical flows on top of a sliding window of frames.
+The sliding window has a size of $L$ frames and gathers 2$L$ components ($L$ horizontal ($d_t^x$) + $L$ vertical ($d_t^y$) optical flow component vector fields) creating a stack $O$ = \{$d_t^x$, $d_t^y$, $d_{t+1}^x$, $d_{t+1}^y$, ..., $d_{t+L}^x$, $d_{t+L}^y$ \}.
+The total number of stacks is given by $N$-$L$+$1$, where $N$ is the number of frames in a video, Figure~\ref{fig:stacks, fig:features}.
+\paragraph{Saliency Map} is composed of pixels varying from 0 to 1, and was fed as a gray-scale image to the network, Figure~\ref{fig:features}.
 
@@
 
-\paragraph{URFD} dataset contains 70 videos: (i) 30 videos of falls; and (ii) 40 videos of daily living activities, recorded from a top-down and side view perspective by two Microsoft Kinect cameras.
+\paragraph{URFD dataset} contains 70 videos: (i) 30 videos of falls; and (ii) 40 videos of daily living activities, recorded from a top-down and side view perspective by two Microsoft Kinect cameras.
 Each frame is labeled in three categories, whether the person is lying on the ground, not lying on the ground or in an intermediate pose.
-\paragraph{FDD} dataset is composed of 191 videos of which 107 are falls, recorded from a surveillance camera perspective by a single RGB camera. With every frame annotated between fall and not fall.
+\paragraph{FDD dataset} is composed of 191 videos of which 107 are falls, recorded from a surveillance camera perspective by a single RGB camera. With every frame annotated between fall and not fall.
 

### 2019-07-17 paper.tex
Updates from Overleaf

@@
 \begin{IEEEkeywords}
-component, formatting, style, styling, insert
+Multi-stream, optical flow, saliency, video, deep learning
 \end{IEEEkeywords}
@@
 
+Ambient assisted living technologies have been rising in popularity as the world population grows older and more robust solutions became available.
+
 \section{Related Work}
+
+% threshold or ROI
+Sase et al.~\cite{sase2018human} detected regions of interest using background subtraction.
+If the region of interest was bellow a threshold a fall event was accused, the threshold was on third of the subject height in the frame.
+
+Bhandari et al.~\cite{bhandari2017novel} used Shi-Tomasi to determine regions of interest and Lucas-Kanade to track them.
+If the speed and motion of the region of interest surpassed a threshold, a fall event was detected.
+
+% SVM
+Zerrouki and Houacine~\cite{zerrouki2018combined} subtracted the background, applied a curvelet transform on this information and used a support vector machine (SVM) to classify the human pose.
+The classified pose was then passed to a hidden markov model, that recognized the activity.
+
+Qian et al.~\cite{qian2017recognizing} also employed a hidden markov model to detect falls.
+
+Yu et al.~\cite{yu2009fall} utilized particle filtering with a background subtraction to track the subject head, and detect falls.
+
+Yu et al.~\cite{yu2010robust} applyed a head tracking based on a gaussian model with a parzen window method to calculate density.
+
+Rougier et al.~\cite{rougier2011robust} detected falls with gaussian and human shape deformation.
+
+Regarding the subject's privacy, both Edgcomb et al.~\cite{edgcomb2012automated} and Lin et al.~\cite{lin2013fall} investigated privacy-prone features, such as bluring, silhouetting, and covering the body with shapes.
+
+Searching for a higher sensitivity, Harrou et al.~\cite{harrou2017vision} segmented the subject in the video and served it to a feature extractor.
+The extractor output would be compared with a employed multivariate exponentially-weighted moving average (MEWMA), and if it was considered alarming a SVM would then verify if a fall occured.
+
+In a mixed approach, Kwolek and Kepski~\cite{kwolek2015improving} used an accelerometer, that passed a given threshold would activate a K-nearest neighbors vision classifier to confirm the event.
+
+% CNN
+N\'u\~nez-Marcos et al.~\cite{nunez2017vision} extracted dense optical flow (OF) from images and fed them to a VGG-16 convolutional neural network (CNN).
+The extracted optical flow was fed in stacks to create a temporal relation between frames.
+
+Anishchenko et al.~\cite{anishchenko2018machine} employd a modified AlexNet to detect falls.
 
@@
 
+In this section, we describe a few relevant concepts applied in the proposed method.
+
 \subsection{Optical Flow}
+\label{sec:opticalflow}
+
+Optical flow is a hand-crafted feature that conveys movement information between the frames of a video, either by object movement or camera shift, Figure~\ref{fig:opticalflow}.
+Its ability to describe movement enables this feature to support the deep network towards detecting falls.
+
+The extraction process considers a video frame as $I$ and $I(x, y, t)$ a pixel in this frame.
+Another frame collected $dt$ time later, and the distance that the same pixel moved $(dx, dy)$, described in Equation~\ref{eq:of-dist}.
+
+Optical flow Equation~\ref{eq:of} is formed after applying a Taylor series approximation of right-hand side and dividing by $dt$, $f_t$ is the gradient given time, $f_x$, $f_y$, $u$, and $v$ are given in Equation~\ref{eq:of-grad}.
+Values of $u$ and $v$ can be achieved by different methods, such as the classical Lucas-Kanade~\cite{jain2018abnormal} or the one used in this work: Gunnar-Farneb{\"a}ck~\cite{lowhur2015dense}.
+
+\begin{equation}
+\label{eq:of-dist}
+I(x, y, t)=I(x+dx, y+dy, t+dt)
+\end{equation}
+\begin{equation}
+\label{eq:of}
+f_xu + f_yv + f_t=0
+\end{equation}
+\begin{equation}
+\label{eq:of-grad}
+f_x = \frac{\partial f}{\partial x}; \quad f_y = \frac{\partial f}{\partial y}u = \frac{\partial x}{\partial t}; \quad v = \frac{\partial y}{\partial t}
+\end{equation}
 
@@
 
-Why were you selected?
+Saliency was envisioned as a visualizing technique to understand the learning process behind a deep network.
+It can be extracted in many ways, one of those is the practice of feeding a image $I$ to the network and its class label $c$, freeze the weights on the network and compute the gradients of $c$ with respect to the pixels of $I$.
+Consider $S_c(I)$ to be the class score function for an image $I$ and, for this simple explanation, that it is a simple linear function, $S_c(I) = w_c^{T} + b_c$.
+With $w$ being the weights of the network and $b$ the bias, it is possible to see that the magnitude of elements of $w$ affects the importance of the corresponding pixels in $I$ for class $c$.
+
+The saliency map was chosen as a stream for its spatial relation to the frame, as the raw RGB frames are prone to interference, for instance from brightness variation, we believe the saliency is capable to overcome these variables.
+This work's saliency extractor is implemented after the paper of Sundararajan et al.~\cite{sundararajan2017axiomatic}.
 
@@
 The selected datasets, further detailed in Section~\ref{sec:experiments}, possesses a relatively small amount of human fall samples in their videos, which would limit the CNNs learning capabilities to detect a fall event.
-Thus, the need to transfer learning from other datasets.
+Hence, the importance of transfer learning.
 
@@
 
-For the sake of comparison with other works in the literature we evaluated our method by three metrics: (i) Sensitivity reflecting the number of true positives, (ii) Specificity also known as the true negative rate, and (iii) Accuracy representing the overall performance of the method.
+For the sake of comparison with other works we evaluated our method by three metrics: (i) Sensitivity reflecting the true positive rate, (ii) Specificity also known as the true negative rate, and (iii) Accuracy representing the overall performance of the method.
+We used a learning rate of $10^{-4}$, 500 epochs, 5-fold cross-validation, minibatches of $2^{10}$, and Adam optimization.
+We also experimented with different class weights, however, with further tuning of the hyper-parameters we were able to keep both classes on the same weight.
+The ensemble was performed by the double-SVM approach explained in Section~\ref{sec:classification}.
 
-We experimented with different class weights, and with further tunning of the hyper parameters we were able to set all classes with the same weight.
-
-learning rate 0.0001, kfold 5, minibatches of 1024, 500 epochs, optimization with adam, each fold result for the three stream combination
-
-The ensemble was performed by the svm approach discussed in section
-
-Compared ensembles techniques, SVM vs avarage
-
-Each individual stream does not perform greatly when used alone, but the ensemble of them has a significant improved result
-
-And the following results were obtained in the FDD dataset
-
-The false negative cases must be taken care since they would be responsible for serious injuries and such
-
-The following results were obatined in the URFD dataset
+Tables~\ref{tab:urfd-ensem} and~\ref{tab:urfd-our-their} shows the results obtained over the URFD dataset.
+In Table~\ref{tab:urfd-ensem} we compare each single-stream feature with their multi-stream counterpart.
+The higher single-stream accuracy was derived from the optical flow stream, at 97.57\%, and the multi-stream was still able to outperform it, at 98.84\%.
+Table~\ref{tab:urfd-our-their} compares our result with other works in the literature, whilst not all works measured their sensitivity and specificity, all of them reported their accuracy.
+Our method's accuracy and specificity performed better than theirs, and kept the same 100\% sensitivity.
 
@@
 \centering
-\caption{URFD comparison between individuas streams and ensemble.}
+\caption{URFD single-stream \textit{vs} multi-stream, decreasing accuracy.}
 \label{tab:urfd-ensem}
@@
 \centering
-\caption{URFD comparison between results.}
+\caption{URFD our method \textit{vs} literature, decreasing accuracy.}
 \label{tab:urfd-our-their}
@@
  &                                                      & Sensitivity (\%)  & Specificity (\%)  & Accuracy (\%)     & \\ \hline
- & Ours                         & \textbf{100}      & \textbf{98.77}   & \textbf{98.84} &  \\
+ & Lu et al.~\cite{lu2018deep}                          & -                 & -                 & \textbf{99.27}    & \\
+ & Ours                                                 & \textbf{100}      & \textbf{98.77}    & 98.84             & \\
+ & Panahi et al.~\cite{panahi2018human}                 & 97.05             & 97.02             & 97.14             & \\
+ & Zerrouki and Houacine~\cite{zerrouki2018combined}    & -                 & -                 & 96.88             & \\
+ & Harrou et al.~\cite{harrou2017vision}                & -                 & -                 & 96.66             & \\
+ & Abobakr et al.~\cite{abobakr2017skeleton}            & \textbf{100}      & 0.91              & 96.00             & \\
+ & Bhandari et al.~\cite{bhandari2017novel}             & 96.66             & -                 & 95.71             & \\
+ & Kwolek and Kepski~\cite{kwolek2015improving}         & \textbf{100}      & 92.50             & 95.71             & \\
  & N\'u\~nez-Marcos et al.~\cite{nunez2017vision}       & \textbf{100}      & 92.00             & 95.00             & \\
- & Zerrouki and Houacine~\cite{zerrouki2018vision}  & -                & -                & 96.88          &  \\
- & Bhandari et al.~\cite{bhandari2017novel}  & 96.66                & -                & 95.71          &  \\
- & Harrou et al.~\cite{harrou2017vision}  & -                & -                & 96.66          &  \\
- & Sase et al.~\cite{sase2018human}  & 81.00                & -                & 90.00          &  \\
- & Kwolek and Kepski~\cite{kepski2014human}            & \textbf{100}     & 92.50            & 95.71          &  \\ \hline
+ & Sase et al.~\cite{sase2018human}                     & 81.00             & -                 & 90.00             & \\ \hline
 \end{tabular}
@@
 
+Tables~\ref{tab:fdd-ensem} and~\ref{tab:fdd-our-their} reports the results extracted from the FDD dataset.
+Homologous to the URFD report, Table~\ref{tab:fdd-ensem} compares each single-stream with the multi-stream approach.
+The multi-stream achieved 99.51\% accuracy, and the highest single-stream score was again the optical flow, with 99.11\%.
+When comparing our results with the literature, in Table~\ref{tab:fdd-our-their}, our's outperformed every other one, regarding accuracy and sensitivity.
+And was 0.05\% worse then Charfi's et al.~\cite{charfi2013optimised} specificity.
+Our results also confirmed the findings of Wang et al.~\cite{wang2015towards}, since each feature stream did not perform great on their own, but when applyed together they contributed to state of the art results towards fall detection.
+
 \begin{table*}[t]
 \centering
-\caption{FDD comparison between individuas streams and ensemble.}
+\caption{FDD single-stream \textit{vs} multi-stream, decreasing accuracy.}
 \label{tab:fdd-ensem}
@@
 \centering
-\caption{FDD comparison between results.}
+\caption{FDD our method \textit{vs} literature, decreasing accuracy.}
 \label{tab:fdd-our-their}
@@
  & Ours                                                 & \textbf{99.43}    & 99.55             & \textbf{99.51}    & \\
- & N\'u\~nez-Marcos et al.~\cite{nunez2017vision}  & 99.0              & 97.00             & 97.00             & \\
- & Zerrouki and Houacine~\cite{zerrouki2018vision}    & -                 & -                 & 97.02             & \\
+ & Lu et al.~\cite{lu2018deep}                          & -                 & -                 & 99.36             & \\
+ & Sehairi et al.~\cite{sehairi2018elderly}             & -                 & -                 & 98.91             & \\
+ & Zerrouki and Houacine~\cite{zerrouki2018combined}    & -                 & -                 & 97.02             & \\
  & Harrou et al.~\cite{harrou2017vision}                & -                 & -                 & 97.02             & \\
- & Charfi et al.~\cite{charfi2013optimised}            & 98.0              & \textbf{99.60}    & -                 & \\ \hline
+ & Charfi et al.~\cite{charfi2012definition}            & 98.0              & \textbf{99.60}    & -                 & \\
+ & N\'u\~nez-Marcos et al.~\cite{nunez2017vision}       & 99.0              & 97.00             & 97.00             & \\ \hline
 \end{tabular}
@@
 
- It is worth nothing that in health segments, as a general rule it is usually preferred to accuse a false negative over a false positive, for instance it is considered that a HIV test with a false positive result will cause major distress on the patient's life, and if that result were a false negative, eventually the decease shymtons would demand another test.
-This general rule doesn't stand in our scenario, even tough a false positive would trigger a help dispatch which could cause some hassle to the patient, the aftereffects of a fall are related to the time between a fall and the help arrival, as observed by et al.~\cite{}.
+\section{Conclusion and Future Work}
 
-\section{Future Work}
+This paper proposes to detect human fall events, based on the employment of a multi-stream convolutional neural network.
+Each stream was served an extracted feature, them being: (i) optical flow, (ii) saliency map, and (iii) the RGB frame itself, the ensemble was a double SVM approach.
+The proposed method was tested on URFD and FDD datasets, and our solution outperformed the related literature, indicating that multi-stream approaches and the selected features can be useful to detect human fall events.
+
+It is worth discussing the selected features and some literature results.
+As et al.~\cite{chernbumroong2012elderly} noted that privacy concerns might arise on video-based approaches, the selected features are able to conceal one's identity.
+Despite these feature's performance, both optical flow and saliency map are timely and computational intensive to extract, which would halt their implementation in a real-time system.
+Considering this work's goal in exploring features to the fall detection problem, it is relevant to weight their extraction process against their results.
+And regarding other works in the literature, some seemed to dismiss the importance of the sensitivity metric, which quantifies the avoidance of false negatives.
+A World Health Organization report~\cite{who2007report}, enlightens the severity of an elderly fall, thus the importance of a high sensitivity metric.
+
+Observing the results in Table~\ref{tab:urfd-our-their} and~\ref{tab:fdd-our-their}, it is possible to notice a saturation of these datasets, and as reported by et al.~\cite{chernbumroong2012elderly} systems trained on artificial environments did not perform as well on real-life scenarios.
+Therefore, the importance of future work to come up with a more extensive dataset that better resembles the actual application setup.
+Methods wise, as explained above, the exploration of cheaper features and deep networks that could generate comparable results, should also be focused on.
 
@@
 
-\color{red}
-\centering
-EIGHT PAGES
-
 \end{document}

### 2019-07-17 paper.tex
Updates from Overleaf

@@
 
-Ambient assisted living technologies have been rising in popularity as the world population grows older and more robust solutions became available.
+With deteriorating health in advanced ages, even a minor fall can trigger a chain reaction of serious psychological and physical injuries to the elder population.
+Hence, the motivation for ambient assistant living solutions to both avoid falling from occurring and reducing the interval between a fall and help arrival.
+Many studies have been conducted to detect falls as soon as they happen, and can be split into two main categories.
+Hardware reliant solutions, such as accelerometers and IMUs.
+Which are met with frustration from the subjects, mainly towards forgetting to use the device, despite their fall detection performance.
+And vision-based solutions, which allied to machine learning techniques have shown promising results and, furthermore, not relying on the subject's setup to operate.
 
-\section{Related Work}
+Throughout the fall detection literature, techniques varies from threshold activion based, such as, Sase et al.~\cite{sase2018human} detecting regions of interest after a background subtraction, and a threshold activation function if the region of interest was bellow a third of the subject height in the frame.
+Bhandari et al.~\cite{bhandari2017novel} determined regions of interest via Shi-Tomasi, tracked them using Lucas-Kanade, and set a threshold on the region of interest's speed and motion.
+And Albawendi et al.~\cite{albawendi2018video} who used a threshold activation on silhouette shape.
+Another commonly used classification technique is support vector machine (SVM), used by Harrou et al.~\cite{harrou2017vision} that fed a feature extractor with the subject segmented from the frame.
+The extractor output would then be compared with a multivariate exponentially-weighted moving average (MEWMA), and classified by a SVM.
+Panahi et al.~\cite{panahi2018human} subtracted the background from depth images, fitted an ellipse in the subject's shape, and classified it with SVM.
+Abobakr et al.~\cite{abobakr2017skeleton} also subtracted the background from depth images, applied a random decision forest to estimate the subject's posture, and a SVM to classify it.
+Regarding the subject's privacy, both Edgcomb et al.~\cite{edgcomb2012automated} and Lin et al.~\cite{lin2013fall} investigated privacy-prone features, such as blurring, silhouetting, and covering the body with shapes.
 
-% threshold or ROI
-Sase et al.~\cite{sase2018human} detected regions of interest using background subtraction.
-If the region of interest was bellow a threshold a fall event was accused, the threshold was on third of the subject height in the frame.
+~\cite{xu2018survey}
+~\cite{yang2019.} % saliency
+~\cite{sehairi2018elderly} % KNN
+In a mixed approach, Kwolek and Kepski~\cite{kwolek2015improving} used an accelerometer, that passed a given threshold would activate a K-nearest neighbors vision classifier to confirm the event.
+% KNN
+~\cite{mastorakis2018.} % simulated db
 
-Bhandari et al.~\cite{bhandari2017novel} used Shi-Tomasi to determine regions of interest and Lucas-Kanade to track them.
-If the speed and motion of the region of interest surpassed a threshold, a fall event was detected.
+~\cite{sigal2018interpretable} % salinecy
 
-% SVM
-Zerrouki and Houacine~\cite{zerrouki2018combined} subtracted the background, applied a curvelet transform on this information and used a support vector machine (SVM) to classify the human pose.
-The classified pose was then passed to a hidden markov model, that recognized the activity.
+% markov
+Zerrouki et al.~\cite{zerrouki2018combined} that after subtracting the background, applied a curvelet transform and served it to a SVM to classify the human pose, and then a hidden markov model to recognize the activity.
 
@@
 
+% gaussian
 Yu et al.~\cite{yu2010robust} applyed a head tracking based on a gaussian model with a parzen window method to calculate density.
@@
 
-Regarding the subject's privacy, both Edgcomb et al.~\cite{edgcomb2012automated} and Lin et al.~\cite{lin2013fall} investigated privacy-prone features, such as bluring, silhouetting, and covering the body with shapes.
+~\cite{lu2018deep} % LSTM
 
-Searching for a higher sensitivity, Harrou et al.~\cite{harrou2017vision} segmented the subject in the video and served it to a feature extractor.
-The extractor output would be compared with a employed multivariate exponentially-weighted moving average (MEWMA), and if it was considered alarming a SVM would then verify if a fall occured.
-
-In a mixed approach, Kwolek and Kepski~\cite{kwolek2015improving} used an accelerometer, that passed a given threshold would activate a K-nearest neighbors vision classifier to confirm the event.
+~\cite{huang2018video} % CNN
 
@@
 
+% Harrou et al.~\cite{harrou2017vision} procurou sensitivity
+
 Observing the results in Table~\ref{tab:urfd-our-their} and~\ref{tab:fdd-our-their}, it is possible to notice a saturation of these datasets, and as reported by et al.~\cite{chernbumroong2012elderly} systems trained on artificial environments did not perform as well on real-life scenarios.

### 2019-07-17 paper.tex
Updates from Overleaf

@@
 
-Throughout the fall detection literature, techniques varies from threshold activion based, such as, Sase et al.~\cite{sase2018human} detecting regions of interest after a background subtraction, and a threshold activation function if the region of interest was bellow a third of the subject height in the frame.
+Throughout the fall detection literature, techniques varies from threshold activation based, such as, Sase et al.~\cite{sase2018human} detecting regions of interest after a background subtraction, and a threshold activation function if the region of interest was bellow a third of the subject height in the frame.
 Bhandari et al.~\cite{bhandari2017novel} determined regions of interest via Shi-Tomasi, tracked them using Lucas-Kanade, and set a threshold on the region of interest's speed and motion.
@@
 Regarding the subject's privacy, both Edgcomb et al.~\cite{edgcomb2012automated} and Lin et al.~\cite{lin2013fall} investigated privacy-prone features, such as blurring, silhouetting, and covering the body with shapes.
+Deep neural approaches were explored by Lu et al.~\cite{lu2018deep} who employed a 3D convolutional neural network (CNN) followed by a long short-term memory (LSTM).
+Huang et al.~\cite{huang2018video} extracted the human pose with OpenPose and classified it with a VGG-16 architecture.
+N\'u\~nez-Marcos et al.~\cite{nunez2017vision} extracted the dense optical flow (OF) and also served it to a VGG-16.
+And Anishchenko et al.~\cite{anishchenko2018machine} employed a modified AlexNet as classifier.
+A few different approaches were also reported, such as, K-nearest neighbor classifiers by Sehairi et al.~\cite{sehairi2018elderly} and Kwolek et al.~\cite{kwolek2015improving}.
+Hidden markov model by Zerrouki et al.~\cite{zerrouki2018combined} and Qian et al.~\cite{qian2017recognizing}.
+Particle filtering by Yu et al.~\cite{yu2009fall}.
+And gaussian models by Yu et al.~\cite{yu2010robust} and Rougier et al.~\cite{rougier2011robust}.
+Furthermore Xu et al.~\cite{xu2018new} produced a survey on fall detections systems.
 
-~\cite{xu2018survey}
-~\cite{yang2019.} % saliency
-~\cite{sehairi2018elderly} % KNN
-In a mixed approach, Kwolek and Kepski~\cite{kwolek2015improving} used an accelerometer, that passed a given threshold would activate a K-nearest neighbors vision classifier to confirm the event.
-% KNN
-~\cite{mastorakis2018.} % simulated db
+This work's main contribution is the development and evaluation of hand-crafted features to be used in a multi-stream learning model.
+To this end, we compare the effectiveness of three features extracted from videos frames: (i) optical flow, (ii) saliency map, and (iii) RGB features.
+These features a fed to a three-stream VGG-16 architecture, and their results compared with the literature.
 
-~\cite{sigal2018interpretable} % salinecy
+This paper is organized as follows.
+In Section~\ref{sec:method} we detail the proposed three-stream methodology.
+In Section~\ref{sec:experiments} the performed experiments and their results are compared to other works in the literature.
+Moreover, in Section~\ref{sec:conclusion} we elaborate on some points and future work suggestions.
 
-% markov
-Zerrouki et al.~\cite{zerrouki2018combined} that after subtracting the background, applied a curvelet transform and served it to a SVM to classify the human pose, and then a hidden markov model to recognize the activity.
+% ~\cite{yang2019.} % saliency
+% ~\cite{mastorakis2018.} % simulated db
 
-Qian et al.~\cite{qian2017recognizing} also employed a hidden markov model to detect falls.
+% ~\cite{sigal2018interpretable} % salinecy
 
-Yu et al.~\cite{yu2009fall} utilized particle filtering with a background subtraction to track the subject head, and detect falls.
+% \section{Background}
+% \label{background}
 
-% gaussian
-Yu et al.~\cite{yu2010robust} applyed a head tracking based on a gaussian model with a parzen window method to calculate density.
+% In this section, we describe a few relevant concepts applied in the proposed method.
 
-Rougier et al.~\cite{rougier2011robust} detected falls with gaussian and human shape deformation.
+% \subsection{Optical Flow}
+% \label{sec:opticalflow}
 
-~\cite{lu2018deep} % LSTM
-
-~\cite{huang2018video} % CNN
-
-% CNN
-N\'u\~nez-Marcos et al.~\cite{nunez2017vision} extracted dense optical flow (OF) from images and fed them to a VGG-16 convolutional neural network (CNN).
-The extracted optical flow was fed in stacks to create a temporal relation between frames.
-
-Anishchenko et al.~\cite{anishchenko2018machine} employd a modified AlexNet to detect falls.
-
-\section{Background}
-
-In this section, we describe a few relevant concepts applied in the proposed method.
-
-\subsection{Optical Flow}
-\label{sec:opticalflow}
-
-Optical flow is a hand-crafted feature that conveys movement information between the frames of a video, either by object movement or camera shift, Figure~\ref{fig:opticalflow}.
+% Optical flow is a hand-crafted feature that conveys movement information between the frames of a video, either by object movement or camera shift, Figure~\ref{fig:opticalflow}.
 Its ability to describe movement enables this feature to support the deep network towards detecting falls.
 
-The extraction process considers a video frame as $I$ and $I(x, y, t)$ a pixel in this frame.
+% The extraction process considers a video frame as $I$ and $I(x, y, t)$ a pixel in this frame.
 Another frame collected $dt$ time later, and the distance that the same pixel moved $(dx, dy)$, described in Equation~\ref{eq:of-dist}.
 
-Optical flow Equation~\ref{eq:of} is formed after applying a Taylor series approximation of right-hand side and dividing by $dt$, $f_t$ is the gradient given time, $f_x$, $f_y$, $u$, and $v$ are given in Equation~\ref{eq:of-grad}.
+% Optical flow Equation~\ref{eq:of} is formed after applying a Taylor series approximation of right-hand side and dividing by $dt$, $f_t$ is the gradient given time, $f_x$, $f_y$, $u$, and $v$ are given in Equation~\ref{eq:of-grad}.
 Values of $u$ and $v$ can be achieved by different methods, such as the classical Lucas-Kanade~\cite{jain2018abnormal} or the one used in this work: Gunnar-Farneb{\"a}ck~\cite{lowhur2015dense}.
 
-\begin{equation}
-\label{eq:of-dist}
-I(x, y, t)=I(x+dx, y+dy, t+dt)
-\end{equation}
-\begin{equation}
-\label{eq:of}
-f_xu + f_yv + f_t=0
-\end{equation}
-\begin{equation}
-\label{eq:of-grad}
-f_x = \frac{\partial f}{\partial x}; \quad f_y = \frac{\partial f}{\partial y}u = \frac{\partial x}{\partial t}; \quad v = \frac{\partial y}{\partial t}
-\end{equation}
+% \begin{equation}
+% \label{eq:of-dist}
+% I(x, y, t)=I(x+dx, y+dy, t+dt)
+% \end{equation}
+% \begin{equation}
+% \label{eq:of}
+% f_xu + f_yv + f_t=0
+% \end{equation}
+% \begin{equation}
+% \label{eq:of-grad}
+% f_x = \frac{\partial f}{\partial x}; \quad f_y = \frac{\partial f}{\partial y}u = \frac{\partial x}{\partial t}; \quad v = \frac{\partial y}{\partial t}
+% \end{equation}
 
-\subsection{Saliency Map}
-\label{sec:saliency}
+% \subsection{Saliency Map}
+% \label{sec:saliency}
 
-Saliency was envisioned as a visualizing technique to understand the learning process behind a deep network.
+% Saliency was envisioned as a visualizing technique to understand the learning process behind a deep network.
 It can be extracted in many ways, one of those is the practice of feeding a image $I$ to the network and its class label $c$, freeze the weights on the network and compute the gradients of $c$ with respect to the pixels of $I$.
@@
 
-The saliency map was chosen as a stream for its spatial relation to the frame, as the raw RGB frames are prone to interference, for instance from brightness variation, we believe the saliency is capable to overcome these variables.
+% The saliency map was chosen as a stream for its spatial relation to the frame, as the raw RGB frames are prone to interference, for instance from brightness variation, we believe the saliency is capable to overcome these variables.
 This work's saliency extractor is implemented after the paper of Sundararajan et al.~\cite{sundararajan2017axiomatic}.
@@
 \section{Method}
+\label{sec:method}
 
@@
 Two selected features were fed to the streams explained in Subsection~\ref{sec:classification}:(i) Optical Flow and (ii) Saliency Map.
-Furthermore, the RGB frame itself was fed to the third stream, Figure~\ref{fig:features}, given the neural networks capability to learn relevant features to describe their input.
+Furthermore, the RGB frame itself was fed to the third stream, given the neural networks capability to learn relevant features to describe their input.
 
@@
 The sliding window has a size of $L$ frames and gathers 2$L$ components ($L$ horizontal ($d_t^x$) + $L$ vertical ($d_t^y$) optical flow component vector fields) creating a stack $O$ = \{$d_t^x$, $d_t^y$, $d_{t+1}^x$, $d_{t+1}^y$, ..., $d_{t+L}^x$, $d_{t+L}^y$ \}.
-The total number of stacks is given by $N$-$L$+$1$, where $N$ is the number of frames in a video, Figure~\ref{fig:stacks, fig:features}.
+The total number of stacks is given by $N$-$L$+$1$, where $N$ is the number of frames in a video, Figure~\ref{fig:stacks}.
 \paragraph{Saliency Map} is composed of pixels varying from 0 to 1, and was fed as a gray-scale image to the network, Figure~\ref{fig:features}.
@@
 
-\begin{table*}[t]
+\begin{table}[]
 \centering
@@
 \hline
- &                              & Sensitivity (\%)  & Specificity (\%)  & Accuracy (\%)     & \\ \hline
- & Multi-stream (OF+RGB+Sal)    & \textbf{100}      & \textbf{98.77}    & \textbf{98.84}    & \\
- & Single-stream (OF)           & \textbf{100}      & 97.42             & 97.57             & \\
- & Single-stream (RGB)          & \textbf{100}      & 96.35             & 96.56             & \\
- & Single-stream (Sal)          & 93.67             & 93.39             & 93.40             & \\ \hline
+ &  & Sens. (\%) & Spec. (\%) & Acc. (\%) &  \\ \hline
+ & OF + RGB + Sal & \textbf{100} & \textbf{98.77} & \textbf{98.84} &  \\
+ & Optical Flow & \textbf{100} & 97.42 & 97.57 &  \\
+ & RGB & \textbf{100} & 96.35 & 96.56 &  \\
+ & Saliency & 93.67 & 93.39 & 93.40 &  \\ \hline
 \end{tabular}
-\end{table*}
+\end{table}
 
@@
 \hline
- &                      & Sensitivity (\%)  & Specificity (\%)  & Accuracy (\%)     &  \\ \hline
- & Multi (OF+RGB+Sal)   & \textbf{99.43}    & \textbf{99.55}    & \textbf{99.51}    &  \\
- & Single (OF)          & 99.07             & 99.12             & 99.11             &  \\
- & Single (RGB)         & 98.85             & 98.41             & 98.55             &  \\
- & Single (Sal)         & 88.39             & 92.40             & 91.25             & \\ \hline
+ &  & Sens. (\%) & Spec. (\%) & Acc. (\%) &  \\ \hline
+ & OF + RGB + Sal & \textbf{99.43} & \textbf{99.55} & \textbf{99.51} &  \\
+ & Optical Flow & 99.07             & 99.12             & 99.11             &  \\
+ & RGB & 98.85             & 98.41             & 98.55             &  \\
+ & Saliency & 88.39             & 92.40             & 91.25             & \\ \hline
 \end{tabular}
-\end{table*}
+\end{table}
 
@@
 \section{Conclusion and Future Work}
+\label{sec:conclusion}
 

### 2019-07-17 paper.tex
Updates from Overleaf

@@
 
-% \section{Background}
-% \label{background}
+\section{Background}
+\label{background}
 
-% In this section, we describe a few relevant concepts applied in the proposed method.
+In this section, we describe a few relevant concepts employed in Section~\ref{sec:method}.
 
-% \subsection{Optical Flow}
-% \label{sec:opticalflow}
+\subsection{Optical Flow}
+\label{sec:opticalflow}
 
-% Optical flow is a hand-crafted feature that conveys movement information between the frames of a video, either by object movement or camera shift, Figure~\ref{fig:opticalflow}.
-Its ability to describe movement enables this feature to support the deep network towards detecting falls.
+Optical flow is a hand-crafted feature that conveys movement information between two frames of a video, either by object or camera movement, Figure~\ref{fig:opticalflow}.
+Its ability to describe movement enables this feature to support the temporal aspect of a fall event in a deep network.
 
-% The extraction process considers a video frame as $I$ and $I(x, y, t)$ a pixel in this frame.
-Another frame collected $dt$ time later, and the distance that the same pixel moved $(dx, dy)$, described in Equation~\ref{eq:of-dist}.
+The extraction process considers a video frame as $I$ and $I(x, y, t)$ a pixel in this frame.
+Another frame collected $dt$ time later, and the distance that the same pixel moved $(dx, dy)$ is described in Equation~\ref{eq:of-dist}.
 
-% Optical flow Equation~\ref{eq:of} is formed after applying a Taylor series approximation of right-hand side and dividing by $dt$, $f_t$ is the gradient given time, $f_x$, $f_y$, $u$, and $v$ are given in Equation~\ref{eq:of-grad}.
+Optical flow's Equation~\ref{eq:of} is formed after applying a Taylor series approximation of right-hand side and dividing by $dt$, $f_t$ is the gradient given time, $f_x$, $f_y$, $u$, and $v$ are given in Equation~\ref{eq:of-grad}.
 Values of $u$ and $v$ can be achieved by different methods, such as the classical Lucas-Kanade~\cite{jain2018abnormal} or the one used in this work: Gunnar-Farneb{\"a}ck~\cite{lowhur2015dense}.
 
-% \begin{equation}
-% \label{eq:of-dist}
-% I(x, y, t)=I(x+dx, y+dy, t+dt)
-% \end{equation}
-% \begin{equation}
-% \label{eq:of}
-% f_xu + f_yv + f_t=0
-% \end{equation}
-% \begin{equation}
-% \label{eq:of-grad}
-% f_x = \frac{\partial f}{\partial x}; \quad f_y = \frac{\partial f}{\partial y}u = \frac{\partial x}{\partial t}; \quad v = \frac{\partial y}{\partial t}
-% \end{equation}
+\begin{equation}
+\label{eq:of-dist}
+I(x, y, t)=I(x+dx, y+dy, t+dt)
+\end{equation}
+\begin{equation}
+\label{eq:of}
+f_xu + f_yv + f_t=0
+\end{equation}
+\begin{equation}
+\label{eq:of-grad}
+f_x = \frac{\partial f}{\partial x}; \quad f_y = \frac{\partial f}{\partial y}u = \frac{\partial x}{\partial t}; \quad v = \frac{\partial y}{\partial t}
+\end{equation}
 
-% \subsection{Saliency Map}
-% \label{sec:saliency}
+\subsection{Saliency Map}
+\label{sec:saliency}
 
-% Saliency was envisioned as a visualizing technique to understand the learning process behind a deep network.
-It can be extracted in many ways, one of those is the practice of feeding a image $I$ to the network and its class label $c$, freeze the weights on the network and compute the gradients of $c$ with respect to the pixels of $I$.
+Saliency maps were envisioned as a visualizing technique to understand the learning process behind a deep network.
+It can be extracted in many ways, one of those being the practice of feeding an image $I$ and its class label $c$ to the network, then, freezing the weights on the network and compute the gradients of $c$ with respect to the pixels of $I$.
 Consider $S_c(I)$ to be the class score function for an image $I$ and, for this simple explanation, that it is a simple linear function, $S_c(I) = w_c^{T} + b_c$.
@@
 
-% The saliency map was chosen as a stream for its spatial relation to the frame, as the raw RGB frames are prone to interference, for instance from brightness variation, we believe the saliency is capable to overcome these variables.
+The saliency map was chosen as a stream for its spatial relation to the frame, as the raw RGB frames are prone to interference, for instance from brightness variation, we believe the saliency is capable to overcome these variables.
 This work's saliency extractor is implemented after the paper of Sundararajan et al.~\cite{sundararajan2017axiomatic}.
@@
 An ensemble of VGG-16s were employed and evaluated to classify fall and not fall in video sequences, as seen in Figure~\ref{fig:overview} and further detailed bellow.
+
+\begin{figure}[htbp]
+\centerline{\includegraphics[width=\linewidth]{figures/overview.png}}
+\caption{Methodology overview.}
+\label{fig:overview}
+\end{figure}
 
@@
 
+\begin{figure}[htbp]
+\centerline{\includegraphics[width=0.9\linewidth]{figures/pre14.png}}
+\caption{Deep layers being trained by ImagetNet and UCF101.}
+\label{fig:pre14}
+\end{figure}
+
 The 14 initial layer's weights were then frozen, and the last two fully connected layers were separately fine-tuned, with dropout regularization, over the extracted hand-crafted features of the URFD~\cite{kepski2014human} and FDD~\cite{charfi2013optimised} datasets.
 The last fine-tuning was performed three times, one for each of the extracted hand-crafted features, Figure~\ref{fig:pos14}.
+
+\begin{figure}[htbp]
+\centerline{\includegraphics[width=0.4\linewidth]{figures/pos14.png}}
+\caption{Fully connected layers training.}
+\label{fig:pos14}
+\end{figure}
 

### 2019-07-17 paper.tex
Updates from Overleaf

@@
 Consider $S_c(I)$ to be the class score function for an image $I$ and, for this simple explanation, that it is a simple linear function, $S_c(I) = w_c^{T} + b_c$.
-With $w$ being the weights of the network and $b$ the bias, it is possible to see that the magnitude of elements of $w$ affects the importance of the corresponding pixels in $I$ for class $c$.
+With $w$ being the weights of the network and $b$ the bias, it is possible to notice that the magnitude of elements of $w$ affects the importance of the corresponding pixels in $I$ with class $c$.
 
-The saliency map was chosen as a stream for its spatial relation to the frame, as the raw RGB frames are prone to interference, for instance from brightness variation, we believe the saliency is capable to overcome these variables.
-This work's saliency extractor is implemented after the paper of Sundararajan et al.~\cite{sundararajan2017axiomatic}.
+The saliency map was chosen as a stream for its spatial relation to the frame, as the raw RGB frames are prone to environment interference, and its performance in the works of Yang et al.~\cite{yang2019.} and Sigal et al.~\cite{sigal
+Sundararajan's et al.~\cite{sundararajan2017axiomatic} saliency method is used in this work.
 

### 2019-07-17 paper.tex
Text revised by me

@@
 
-% ~\cite{yang2019.} % saliency
-% ~\cite{mastorakis2018.} % simulated db
-
-% ~\cite{sigal2018interpretable} % salinecy
-
 \section{Background}
@@
 
-The saliency map was chosen as a stream for its spatial relation to the frame, as the raw RGB frames are prone to environment interference, and its performance in the works of Yang et al.~\cite{yang2019.} and Sigal et al.~\cite{sigal
+The saliency map was chosen as a stream for its spatial relation to the frame, as the raw RGB frames are prone to environment interference, and its performance in the works of Yang et al.~\cite{yang2019enhanced} and Sigal et al.~\cite{sigal2018interpretable}.
 Sundararajan's et al.~\cite{sundararajan2017axiomatic} saliency method is used in this work.
@@
 
-An ensemble of VGG-16s were employed and evaluated to classify fall and not fall in video sequences, as seen in Figure~\ref{fig:overview} and further detailed bellow.
+An ensemble of VGG-16s were employed and evaluated to classify between fall and not fall in video sequences, as seen in Figure~\ref{fig:overview} and further detailed bellow.
 
@@
 
-The selected datasets, further detailed in Section~\ref{sec:experiments}, possesses a relatively small amount of human fall samples in their videos, which would limit the CNNs learning capabilities to detect a fall event.
+The selected datasets, further detailed in Section~\ref{sec:experiments}, possesses relatively few human fall samples in their videos, which would limit the CNNs learning capabilities to detect fall events.
 Hence, the importance of transfer learning.
@@
 The reasoning being that the network would initially learn low level features from the ImageNet classes, and focus these features on human activities with the UCF101 videos, Figure~\ref{fig:pre14}.
+This process was executed by N\'u\~nez-Marcos et al.~\cite{nunez2017vision}, who shared the pre-trained weights files.
 
@@
 
-The 14 initial layer's weights were then frozen, and the last two fully connected layers were separately fine-tuned, with dropout regularization, over the extracted hand-crafted features of the URFD~\cite{kepski2014human} and FDD~\cite{charfi2013optimised} datasets.
-The last fine-tuning was performed three times, one for each of the extracted hand-crafted features, Figure~\ref{fig:pos14}.
+The 14 initial layer's weights were then frozen, and the last two fully connected layers were fine-tuned, with dropout regularization.
+This last fine-tuning was performed three times, one for each of the extracted hand-crafted features, Figure~\ref{fig:pos14}.
 
@@
 
-Wang et al.~\cite{wang2015towards} reported that networks employing multi-stream classifiers outperformed their single-streamed peers.
-Inspired on this finding, a SVM classifier fed with the outputs of each stream, between 0 and 1, generates a ($x$, $y$, $z$) vector.
-This vector is then fed to a second SVM that classifies between fall and not fall, Figure~\ref{fig:pos14}.
+Wang et al.~\cite{wang2015towards} reported that, networks employing multi-stream classifiers outperformed their single-streamed peers.
+Inspired on this finding, a SVM classifier fed with the outputs of each stream, vectors between 0 and 1, generates a ($x$, $y$, $z$) vector.
+This vector is then fed to a second SVM that classifies between fall and not fall, Figure~\ref{fig:overview}.
 
@@
 Two selected features were fed to the streams explained in Subsection~\ref{sec:classification}:(i) Optical Flow and (ii) Saliency Map.
-Furthermore, the RGB frame itself was fed to the third stream, given the neural networks capability to learn relevant features to describe their input.
+Furthermore, given the neural networks capability to learn relevant features to describe their input, the RGB frame itself was fed to the third stream.
 
-\paragraph{Optical Flow} represents the temporal relation between frames, and to fully gather this property it was used as a stack of optical flows on top of a sliding window of frames.
+\paragraph{Optical Flow} represents the temporal relation between frames, and to fully gather this property it was used as a stack of optical flows on top of a sliding window of frames, as suggested by N\'u\~nez-Marcos et al.~\cite{nunez2017vision}.
 The sliding window has a size of $L$ frames and gathers 2$L$ components ($L$ horizontal ($d_t^x$) + $L$ vertical ($d_t^y$) optical flow component vector fields) creating a stack $O$ = \{$d_t^x$, $d_t^y$, $d_{t+1}^x$, $d_{t+1}^y$, ..., $d_{t+L}^x$, $d_{t+L}^y$ \}.
-The total number of stacks is given by $N$-$L$+$1$, where $N$ is the number of frames in a video, Figure~\ref{fig:stacks}.
-\paragraph{Saliency Map} is composed of pixels varying from 0 to 1, and was fed as a gray-scale image to the network, Figure~\ref{fig:features}.
+The total number of stacks is given by $N$-$L$+$1$, where $N$ is the number of frames in a video.
+\paragraph{Saliency Map} is composed of pixels varying from 0 to 1, and was fed as a gray-scale image to the network.
 
@@
 
-\paragraph{URFD dataset} contains 70 videos: (i) 30 videos of falls; and (ii) 40 videos of daily living activities, recorded from a top-down and side view perspective by two Microsoft Kinect cameras.
-Each frame is labeled in three categories, whether the person is lying on the ground, not lying on the ground or in an intermediate pose.
+\paragraph{URFD dataset} contains 70 videos: (i) 30 videos of falls; and (ii) 40 videos of daily living activities, recorded from a top-down and front view perspective by two Microsoft Kinect cameras.
+Each frame is labeled in three categories, if the person is lying on the ground, not lying on the ground, and in an intermediate pose.
 \paragraph{FDD dataset} is composed of 191 videos of which 107 are falls, recorded from a surveillance camera perspective by a single RGB camera. With every frame annotated between fall and not fall.
@@
 We used a learning rate of $10^{-4}$, 500 epochs, 5-fold cross-validation, minibatches of $2^{10}$, and Adam optimization.
-We also experimented with different class weights, however, with further tuning of the hyper-parameters we were able to keep both classes on the same weight.
+We also experimented with differents classes weights, however, with further tuning of the hyper-parameters we were able to keep both classes on the same weight.
 The ensemble was performed by the double-SVM approach explained in Section~\ref{sec:classification}.
@@
 The higher single-stream accuracy was derived from the optical flow stream, at 97.57\%, and the multi-stream was still able to outperform it, at 98.84\%.
-Table~\ref{tab:urfd-our-their} compares our result with other works in the literature, whilst not all works measured their sensitivity and specificity, all of them reported their accuracy.
-Our method's accuracy and specificity performed better than theirs, and kept the same 100\% sensitivity.
+Table~\ref{tab:urfd-our-their} compares our result with other works in the literature, whilst not all works measured their sensitivity
+and specificity, all of them reported their accuracy.
+Our method's accuracy and specificity performed better than most and kept the same 100\% sensitivity.
+Lu et al.~\cite{lu2018deep} was the only work to perform better than ours, and we believe the reason for such is the temporal importance to detect a fall event, and their usage of LSTM would better cater this relationship.
 
@@
 This paper proposes to detect human fall events, based on the employment of a multi-stream convolutional neural network.
-Each stream was served an extracted feature, them being: (i) optical flow, (ii) saliency map, and (iii) the RGB frame itself, the ensemble was a double SVM approach.
-The proposed method was tested on URFD and FDD datasets, and our solution outperformed the related literature, indicating that multi-stream approaches and the selected features can be useful to detect human fall events.
+Each stream was served an extracted feature, them being: (i) optical flow, (ii) saliency map, and (iii) the RGB frame itself, the ensemble performed was a double SVM approach.
+The proposed method was tested on URFD and FDD datasets, and our solution outperformed the related literature in most cases, indicating that multi-stream approaches and the selected features can be useful to detect human fall events.
 
@@
 
-% Harrou et al.~\cite{harrou2017vision} procurou sensitivity
-
-Observing the results in Table~\ref{tab:urfd-our-their} and~\ref{tab:fdd-our-their}, it is possible to notice a saturation of these datasets, and as reported by et al.~\cite{chernbumroong2012elderly} systems trained on artificial environments did not perform as well on real-life scenarios.
-Therefore, the importance of future work to come up with a more extensive dataset that better resembles the actual application setup.
-Methods wise, as explained above, the exploration of cheaper features and deep networks that could generate comparable results, should also be focused on.
+Observing the results in Table~\ref{tab:urfd-our-their} and~\ref{tab:fdd-our-their}, it is possible to notice a saturation of these datasets, and as also reported by et al.~\cite{chernbumroong2012elderly}, systems trained on artificial environments did not perform as well on real-life scenarios.
+Therefore, the importance of future work to come up with a more extensive dataset that better resembles the actual application setup, Mastorakis et al.~\cite{mastorakis2018fall} published a simulated dataset of fall events.
+Method wise, as explained above, the exploration of cheaper features and deep networks that could generate comparable results, should also be focused on.
 

### 2019-07-17 paper.tex
Updates from Overleaf

@@
 \begin{abstract}
-This document is a model and instructions for \LaTeX.
-This and the IEEEtran.cls file define the components of your paper [title, text, heads, etc.]. *CRITICAL: Do Not Use Symbols, Special Characters, Footnotes, 
-or Math in Paper Title or Abstract.
+With falls being, at the same time more susceptible in advanced ages and the second most common cause of accidental death to elders, detecting falls became a necessary research topic to an aging population~\cite{who2007report}.
+To this effect, we proposed and evaluated the employment of a multi-stream approach to detect fall events.
+Three features (optical flow, saliency map, and RGB data) fed to each stream of a VGG-16 and classified by an SVM of whether there was or not a fall event.
+We experimented on two datasets URFD and FDD, achieving respectively 98.84\% and 99.51\% accuracy, outperforming the majority of reviewed solutions.
 \end{abstract}
@@
 With deteriorating health in advanced ages, even a minor fall can trigger a chain reaction of serious psychological and physical injuries to the elder population.
-Hence, the motivation for ambient assistant living solutions to both avoid falling from occurring and reducing the interval between a fall and help arrival.
-Many studies have been conducted to detect falls as soon as they happen, and can be split into two main categories.
+Hence, the motivation for ambient assistant living solutions to both avoids falling from occurring and reducing the interval between a fall and help arrival.
+The studies conducted to detect falls as soon as they happen can be split into two main categories.
 Hardware reliant solutions, such as accelerometers and IMUs.
 Which are met with frustration from the subjects, mainly towards forgetting to use the device, despite their fall detection performance.
-And vision-based solutions, which allied to machine learning techniques have shown promising results and, furthermore, not relying on the subject's setup to operate.
+And vision-based solutions, which allied to machine learning techniques have shown promising results and, furthermore, not relying on the subject's set up to operate.
 
-Throughout the fall detection literature, techniques varies from threshold activation based, such as, Sase et al.~\cite{sase2018human} detecting regions of interest after a background subtraction, and a threshold activation function if the region of interest was bellow a third of the subject height in the frame.
-Bhandari et al.~\cite{bhandari2017novel} determined regions of interest via Shi-Tomasi, tracked them using Lucas-Kanade, and set a threshold on the region of interest's speed and motion.
+Throughout the fall detection literature, techniques vary from threshold activation based, such as Sase et al.~\cite{sase2018human} detecting regions of interest after background subtraction, and a threshold activation function if the region of interest was under a third of the subject height in the frame.
+Bhandari et al.~\cite{bhandari2017novel} determined regions of interest via Shi-Tomasi, tracked them using Lucas-Kanade and set a threshold on the region of interest's speed and motion.
 And Albawendi et al.~\cite{albawendi2018video} who used a threshold activation on silhouette shape.
 Another commonly used classification technique is support vector machine (SVM), used by Harrou et al.~\cite{harrou2017vision} that fed a feature extractor with the subject segmented from the frame.
-The extractor output would then be compared with a multivariate exponentially-weighted moving average (MEWMA), and classified by a SVM.
+They compared extractor output with a multivariate exponentially-weighted moving average (MEWMA) and classified by an SVM.
 Panahi et al.~\cite{panahi2018human} subtracted the background from depth images, fitted an ellipse in the subject's shape, and classified it with SVM.
-Abobakr et al.~\cite{abobakr2017skeleton} also subtracted the background from depth images, applied a random decision forest to estimate the subject's posture, and a SVM to classify it.
+Abobakr et al.~\cite{abobakr2017skeleton} also subtracted the background from depth images, applied a random decision forest to estimate the subject's posture, and an SVM to classify it.
 Regarding the subject's privacy, both Edgcomb et al.~\cite{edgcomb2012automated} and Lin et al.~\cite{lin2013fall} investigated privacy-prone features, such as blurring, silhouetting, and covering the body with shapes.
-Deep neural approaches were explored by Lu et al.~\cite{lu2018deep} who employed a 3D convolutional neural network (CNN) followed by a long short-term memory (LSTM).
+Lu et al.~\cite{lu2018deep} employed a 3D convolutional neural network (CNN) followed by a long short-term memory (LSTM).
 Huang et al.~\cite{huang2018video} extracted the human pose with OpenPose and classified it with a VGG-16 architecture.
 N\'u\~nez-Marcos et al.~\cite{nunez2017vision} extracted the dense optical flow (OF) and also served it to a VGG-16.
-And Anishchenko et al.~\cite{anishchenko2018machine} employed a modified AlexNet as classifier.
-A few different approaches were also reported, such as, K-nearest neighbor classifiers by Sehairi et al.~\cite{sehairi2018elderly} and Kwolek et al.~\cite{kwolek2015improving}.
-Hidden markov model by Zerrouki et al.~\cite{zerrouki2018combined} and Qian et al.~\cite{qian2017recognizing}.
+And Anishchenko et al.~\cite{anishchenko2018machine} employed a modified AlexNet as a classifier.
+A few different approaches were also reported, such as K-nearest neighbor classifiers by Sehairi et al.~\cite{sehairi2018elderly} and Kwolek et al.~\cite{kwolek2015improving}.
+Hidden Markov model by Zerrouki et al.~\cite{zerrouki2018combined} and Qian et al.~\cite{qian2017recognizing}.
 Particle filtering by Yu et al.~\cite{yu2009fall}.
-And gaussian models by Yu et al.~\cite{yu2010robust} and Rougier et al.~\cite{rougier2011robust}.
-Furthermore Xu et al.~\cite{xu2018new} produced a survey on fall detections systems.
+And Gaussian models by Yu et al.~\cite{yu2010robust} and Rougier et al.~\cite{rougier2011robust}.
+Furthermore, Xu et al.~\cite{xu2018new} produced a survey on fall detections systems.
 
-This work's main contribution is the development and evaluation of hand-crafted features to be used in a multi-stream learning model.
+This work's main contribution is the development and evaluation of hand-crafted features in a multi-stream learning model.
 To this end, we compare the effectiveness of three features extracted from videos frames: (i) optical flow, (ii) saliency map, and (iii) RGB features.
@@
 
-This paper is organized as follows.
+We organized this paper as follows.
 In Section~\ref{sec:method} we detail the proposed three-stream methodology.
-In Section~\ref{sec:experiments} the performed experiments and their results are compared to other works in the literature.
+In Section~\ref{sec:experiments} we performed experiments and compared their results to other works in the literature.
 Moreover, in Section~\ref{sec:conclusion} we elaborate on some points and future work suggestions.
@@
 
-Optical flow is a hand-crafted feature that conveys movement information between two frames of a video, either by object or camera movement, Figure~\ref{fig:opticalflow}.
+Optical flow is a hand-crafted feature that conveys movement information between two frames of a video, either by object or camera movement.
 Its ability to describe movement enables this feature to support the temporal aspect of a fall event in a deep network.
@@
 
-Saliency maps were envisioned as a visualizing technique to understand the learning process behind a deep network.
-It can be extracted in many ways, one of those being the practice of feeding an image $I$ and its class label $c$ to the network, then, freezing the weights on the network and compute the gradients of $c$ with respect to the pixels of $I$.
+Envisioned as a visualizing technique to understand the learning process behind a deep network.
+Its extraction can occur in many ways, one of those being the practice of feeding an image $I$ and its class label $c$ to the network, then, freezing the weights on the network and compute the gradients of $c$ to the pixels of $I$.
 Consider $S_c(I)$ to be the class score function for an image $I$ and, for this simple explanation, that it is a simple linear function, $S_c(I) = w_c^{T} + b_c$.
@@
 
-The saliency map was chosen as a stream for its spatial relation to the frame, as the raw RGB frames are prone to environment interference, and its performance in the works of Yang et al.~\cite{yang2019enhanced} and Sigal et al.~\cite{sigal2018interpretable}.
-Sundararajan's et al.~\cite{sundararajan2017axiomatic} saliency method is used in this work.
+The choice of saliency map as a stream is due to its spatial relation to the frame, as the raw RGB frames are prone to environmental interference, and its performance in the works of Zuo et al.~\cite{zuo2019enhanced} and Meng et al.~\cite{Meng2018interpretable}.
+We applied Sundararajan's et al.~\cite{sundararajan2017axiomatic} saliency method in this work.
 
@@
 
-An ensemble of VGG-16s were employed and evaluated to classify between fall and not fall in video sequences, as seen in Figure~\ref{fig:overview} and further detailed bellow.
+As further detailed below, to classify between fall and not fall in video sequences we used an ensemble of VGG-16s and evaluated them,  Figure~\ref{fig:overview} shows an overview of the method.
 
@@
 
-% In this work we intended to employ and evaluate a CNN architecture capable of detecting the presence or not of falls in videos, thus approaching the problem as a binary classification.
-To this end, we select the CNN architecture VGG16, since it is well known, and yields satisfactory results.
-Furthermore, based on the results of Wang et al.~\cite{wang2015towards}, in which a multi-streamed CNN outperformed single-stream ones, a ensembled was also exerted to learn the influence of three selected streams, each stream fed with a hand-crafted feature, them being: (i) optical flow, (ii) rgb, and (iii) saliency map.
-
 \subsection{Transfer Learning}
 
-The selected datasets, further detailed in Section~\ref{sec:experiments}, possesses relatively few human fall samples in their videos, which would limit the CNNs learning capabilities to detect fall events.
+The selected datasets, further detailed in Section~\ref{sec:experiments}, possess relatively few human fall samples in their videos, which would limit the CNNs learning capabilities to detect fall events.
 Hence, the importance of transfer learning.
@@
 The first 14 layers of the VGG-16 architecture were trained on the ImageNet~\cite{imagenet_cvpr09} dataset, and later on, these same layers were fine-tuned over the UCF101~\cite{soomro2012ucf101} dataset.
-The reasoning being that the network would initially learn low level features from the ImageNet classes, and focus these features on human activities with the UCF101 videos, Figure~\ref{fig:pre14}.
-This process was executed by N\'u\~nez-Marcos et al.~\cite{nunez2017vision}, who shared the pre-trained weights files.
+The reasoning being that the network would initially learn low-level features from the ImageNet classes, and focus these features on human activities with the UCF101 videos, Figure~\ref{fig:pre14}.
+N\'u\~nez-Marcos et al.~\cite{nunez2017vision} executed this step and released their weights files publicly.
 
@@
 
-The 14 initial layer's weights were then frozen, and the last two fully connected layers were fine-tuned, with dropout regularization.
+We froze the 14 initial layer's weights, and fine-tuned the last two fully connected layers were fine-tuned, with dropout regularization.
 This last fine-tuning was performed three times, one for each of the extracted hand-crafted features, Figure~\ref{fig:pos14}.
@@
 Each frame is labeled in three categories, if the person is lying on the ground, not lying on the ground, and in an intermediate pose.
-\paragraph{FDD dataset} is composed of 191 videos of which 107 are falls, recorded from a surveillance camera perspective by a single RGB camera. With every frame annotated between fall and not fall.
+\paragraph{FDD dataset} is composed of 191 videos of which 143 are falls, recorded from a surveillance camera perspective by a single RGB camera. With every frame annotated between fall and not fall.
 
@@
 
-\begin{table*}[t]
+\begin{table*}[]
 \centering

### 2019-07-18 paper.tex
Updates from Overleaf

@@
 \begin{abstract}
-With falls being, at the same time more susceptible in advanced ages and the second most common cause of accidental death to elders, detecting falls became a necessary research topic to an aging population~\cite{who2007report}.
+With falls being at the same time more susceptible in advanced ages and the second most common cause of accidental death to elders, detecting falls became a necessary research topic to an aging population~\cite{who2007report}.
 To this effect, we proposed and evaluated the employment of a multi-stream approach to detect fall events.
@@
 
-We froze the 14 initial layer's weights, and fine-tuned the last two fully connected layers were fine-tuned, with dropout regularization.
-This last fine-tuning was performed three times, one for each of the extracted hand-crafted features, Figure~\ref{fig:pos14}.
+We froze the 14 initial layer's weights and fine-tuned the last two fully connected layers were fine-tuned, with dropout regularization.
+Each stream executed this last fine-tuning step, totaling three executions, Figure~\ref{fig:pos14}.
 
@@
 
-Wang et al.~\cite{wang2015towards} reported that, networks employing multi-stream classifiers outperformed their single-streamed peers.
-Inspired on this finding, a SVM classifier fed with the outputs of each stream, vectors between 0 and 1, generates a ($x$, $y$, $z$) vector.
-This vector is then fed to a second SVM that classifies between fall and not fall, Figure~\ref{fig:overview}.
+Wang et al.~\cite{wang2015towards} reported that networks employing multi-stream classifiers outperformed their single-streamed peers.
+Inspired on this finding, an SVM classifier fed with the outputs of each stream, vectors between 0 and 1, generates a ($x$, $y$, $z$) vector.
+A second SVM uses this vector to classify between fall and not fall, Figure~\ref{fig:overview}.
 
@@
 
-Two selected features were fed to the streams explained in Subsection~\ref{sec:classification}:(i) Optical Flow and (ii) Saliency Map.
-Furthermore, given the neural networks capability to learn relevant features to describe their input, the RGB frame itself was fed to the third stream.
+The features Optical Flow and Saliency map were fed to the streams we explained in Subsection~\ref{sec:classification}, and furthermore, given the neural networks capability to learn relevant features to describe their input, the RGB frame itself was fed to the third stream.
 
@@
 The sliding window has a size of $L$ frames and gathers 2$L$ components ($L$ horizontal ($d_t^x$) + $L$ vertical ($d_t^y$) optical flow component vector fields) creating a stack $O$ = \{$d_t^x$, $d_t^y$, $d_{t+1}^x$, $d_{t+1}^y$, ..., $d_{t+L}^x$, $d_{t+L}^y$ \}.
-The total number of stacks is given by $N$-$L$+$1$, where $N$ is the number of frames in a video.
-\paragraph{Saliency Map} is composed of pixels varying from 0 to 1, and was fed as a gray-scale image to the network.
+The total number of stacks is given by $N$-$L$+$1$, where $N$ is the number of frames in a video, Figure~\ref{fig:of} shows and extracted example.
+\paragraph{Saliency Map} is composed of pixels varying from 0 to 1, and was fed as a gray-scale image to the network, Figure~\ref{fig:sal} shows and extracted example.
+
+\begin{figure}[htbp]
+\centerline{\includegraphics[width=\linewidth]{figures/of.png}}
+\caption{A frame and its extracted optical flow.}
+\label{fig:of}
+\end{figure}
+
+\begin{figure}[htbp]
+\centerline{\includegraphics[width=\linewidth]{figures/sal.png}}
+\caption{A frame and its extracted saliency map.}
+\label{fig:sal}
+\end{figure}
 
@@
 For the sake of comparison with other works we evaluated our method by three metrics: (i) Sensitivity reflecting the true positive rate, (ii) Specificity also known as the true negative rate, and (iii) Accuracy representing the overall performance of the method.
-We used a learning rate of $10^{-4}$, 500 epochs, 5-fold cross-validation, minibatches of $2^{10}$, and Adam optimization.
-We also experimented with differents classes weights, however, with further tuning of the hyper-parameters we were able to keep both classes on the same weight.
-The ensemble was performed by the double-SVM approach explained in Section~\ref{sec:classification}.
+We used a learning rate of $10^{-4}$, 500 epochs, 5-fold cross-validation, mini-batches of $2^{10}$, and Adam optimization.
+We also experimented with different classes weights, however, further tuning of the hyper-parameters we were able to keep both classes on the same weight.
+As explained in Section~\ref{sec:classification}, a double SVM is used to ensemble the outputs.
 
@@
 In Table~\ref{tab:urfd-ensem} we compare each single-stream feature with their multi-stream counterpart.
-The higher single-stream accuracy was derived from the optical flow stream, at 97.57\%, and the multi-stream was still able to outperform it, at 98.84\%.
-Table~\ref{tab:urfd-our-their} compares our result with other works in the literature, whilst not all works measured their sensitivity
-and specificity, all of them reported their accuracy.
+The optical flow single-stream acquired the highest accuracy, at 97.57\%, and the multi-stream was still able to outperform it, at 98.84\%.
+Table~\ref{tab:urfd-our-their} compares our result with other works in the literature, whilst not all works measured their sensitivity and specificity, all of them reported their accuracy.
 Our method's accuracy and specificity performed better than most and kept the same 100\% sensitivity.
@@
 And was 0.05\% worse then Charfi's et al.~\cite{charfi2013optimised} specificity.
-Our results also confirmed the findings of Wang et al.~\cite{wang2015towards}, since each feature stream did not perform great on their own, but when applyed together they contributed to state of the art results towards fall detection.
+Our results also confirmed the findings of Wang et al.~\cite{wang2015towards} since each feature stream did not perform great on their own, but when applied together they contributed to state of the art results towards fall detection.
 
@@
 This paper proposes to detect human fall events, based on the employment of a multi-stream convolutional neural network.
-Each stream was served an extracted feature, them being: (i) optical flow, (ii) saliency map, and (iii) the RGB frame itself, the ensemble performed was a double SVM approach.
-The proposed method was tested on URFD and FDD datasets, and our solution outperformed the related literature in most cases, indicating that multi-stream approaches and the selected features can be useful to detect human fall events.
+Each stream was served an extracted feature, them being: (i) optical flow, (ii) saliency map, and (iii) the RGB frame itself, the double SVM performed the ensemble approach.
+e tested the proposed method on URFD and FDD datasets, and our solution outperformed the related literature in most cases, indicating that multi-stream approaches and the selected features can be useful to detect human fall events.
 
 It is worth discussing the selected features and some literature results.
-As et al.~\cite{chernbumroong2012elderly} noted that privacy concerns might arise on video-based approaches, the selected features are able to conceal one's identity.
-Despite these feature's performance, both optical flow and saliency map are timely and computational intensive to extract, which would halt their implementation in a real-time system.
+As et al.~\cite{chernbumroong2012elderly} noted that privacy concerns might arise on video-based approaches, the selected features can conceal one's identity.
+Despite these feature's performance, both optical flow and saliency map are timely and computationally intensive to extract, which would halt their implementation in a real-time system.
 Considering this work's goal in exploring features to the fall detection problem, it is relevant to weight their extraction process against their results.

### 2019-09-12 paper.tex
Updates from Overleaf

@@
 \documentclass[conference]{IEEEtran}
+
 \IEEEoverridecommandlockouts
@@
 \usepackage{textcomp}
+\usepackage{booktabs}
+\usepackage{flushend}
 \usepackage{xcolor}
@@
     T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
+
 \begin{document}
 
-\title{Paper Title*\\
-\thanks{Identify applicable funding agency here. If none, delete this.}
-}
+\sloppy
+\tolerance = 999
 
-\author{\IEEEauthorblockN{1\textsuperscript{st} Given Name Surname}
-\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
-\textit{name of organization (of Aff.)}\\
-City, Country \\
-email address}
-\and
-\IEEEauthorblockN{2\textsuperscript{nd} Given Name Surname}
-\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
-\textit{name of organization (of Aff.)}\\
-City, Country \\
-email address}
-\and
-\IEEEauthorblockN{3\textsuperscript{rd} Given Name Surname}
-\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
-\textit{name of organization (of Aff.)}\\
-City, Country \\
-email address}
-\and
-\IEEEauthorblockN{4\textsuperscript{th} Given Name Surname}
-\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
-\textit{name of organization (of Aff.)}\\
-City, Country \\
-email address}
-\and
-\IEEEauthorblockN{5\textsuperscript{th} Given Name Surname}
-\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
-\textit{name of organization (of Aff.)}\\
-City, Country \\
-email address}
-\and
-\IEEEauthorblockN{6\textsuperscript{th} Given Name Surname}
-\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
-\textit{name of organization (of Aff.)}\\
-City, Country \\
-email address}
-}
+\title{Fall Detection in Video Sequences \\ Based on a Three-Stream Convolutional \\ Neural Network}
+
+\author{\vspace*{0.0cm}}
+
+%\author{\IEEEauthorblockN{1\textsuperscript{st} Guilherme Vieira Leite}
+%\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
+%\textit{name of organization (of Aff.)}\\
+%City, Country \\
+%email address}
+%\and
+%\IEEEauthorblockN{2\textsuperscript{nd} Gabriel Pellegrino da Silva}
+%\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
+%\textit{name of organization (of Aff.)}\\
+%City, Country \\
+%email address}
+%\and
+%\IEEEauthorblockN{2\textsuperscript{nd} Helio Pedrini}
+%\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
+%\textit{name of organization (of Aff.)}\\
+%City, Country \\
+%email address}
+%}
 
@@
 \begin{abstract}
-With falls being at the same time more susceptible in advanced ages and the second most common cause of accidental death to elders, detecting falls became a necessary research topic to an aging population~\cite{who2007report}.
-To this effect, we proposed and evaluated the employment of a multi-stream approach to detect fall events.
+With falls being at the same time more susceptible in advanced ages and the second most common cause of accidental death to elders, detecting falls became a crucial research topic to an aging population~\cite{who2007report}.
+To this effect, we propose and evaluate the employment of a multi-stream approach to detect fall events.
 Three features (optical flow, saliency map, and RGB data) fed to each stream of a VGG-16 and classified by an SVM of whether there was or not a fall event.
-We experimented on two datasets URFD and FDD, achieving respectively 98.84\% and 99.51\% accuracy, outperforming the majority of reviewed solutions.
+Experiments are conducted on two datasets, URFD and FDD, achieving accuracy rates of 98.84\% and 99.51\%, respectively, which outperforms the majority of the reviewed solutions.
 \end{abstract}
@@
 \begin{IEEEkeywords}
-Multi-stream, optical flow, saliency, video, deep learning
+Fall detection, multi-stream neural networks, optical flow, saliency, video, deep learning
 \end{IEEEkeywords}
@@
 Hence, the motivation for ambient assistant living solutions to both avoids falling from occurring and reducing the interval between a fall and help arrival.
-The studies conducted to detect falls as soon as they happen can be split into two main categories.
-Hardware reliant solutions, such as accelerometers and IMUs.
-Which are met with frustration from the subjects, mainly towards forgetting to use the device, despite their fall detection performance.
-And vision-based solutions, which allied to machine learning techniques have shown promising results and, furthermore, not relying on the subject's set up to operate.
+
+The studies that detect falls as soon as they happen can be split into two main categories: hardware reliant solutions and vision based ones.
+The first one, which uses devices such as accelerometers and IMUs, has a satisfactory performance but are met with frustration from the subjects, mainly towards forgetting to use the device.
+Vision-based solutions, which allied to machine learning techniques, have shown promising results and, furthermore, do not rely on the subject wearing it.
 
 Throughout the fall detection literature, techniques vary from threshold activation based, such as Sase et al.~\cite{sase2018human} detecting regions of interest after background subtraction, and a threshold activation function if the region of interest was under a third of the subject height in the frame.
-Bhandari et al.~\cite{bhandari2017novel} determined regions of interest via Shi-Tomasi, tracked them using Lucas-Kanade and set a threshold on the region of interest's speed and motion.
-And Albawendi et al.~\cite{albawendi2018video} who used a threshold activation on silhouette shape.
-Another commonly used classification technique is support vector machine (SVM), used by Harrou et al.~\cite{harrou2017vision} that fed a feature extractor with the subject segmented from the frame.
+Bhandari et al.~\cite{bhandari2017novel} determined regions of interest via Shi-Tomasi, tracked them using Lucas-Kanade and set a threshold on the region of interest's speed and motion and also Albawendi et al.~\cite{albawendi2018video} who used a threshold activation on a silhouette shape.
+Another commonly used classification technique is the support vector machine (SVM), used by Harrou et al.~\cite{harrou2017vision}, that fed a feature extractor with the subject segmented from the frame.
 They compared extractor output with a multivariate exponentially-weighted moving average (MEWMA) and classified by an SVM.
@@
 Regarding the subject's privacy, both Edgcomb et al.~\cite{edgcomb2012automated} and Lin et al.~\cite{lin2013fall} investigated privacy-prone features, such as blurring, silhouetting, and covering the body with shapes.
-Lu et al.~\cite{lu2018deep} employed a 3D convolutional neural network (CNN) followed by a long short-term memory (LSTM).
+Lu et al.~\cite{lu2019deep} employed a 3D convolutional neural network (CNN) followed by a long short-term memory (LSTM).
 Huang et al.~\cite{huang2018video} extracted the human pose with OpenPose and classified it with a VGG-16 architecture.
 N\'u\~nez-Marcos et al.~\cite{nunez2017vision} extracted the dense optical flow (OF) and also served it to a VGG-16.
-And Anishchenko et al.~\cite{anishchenko2018machine} employed a modified AlexNet as a classifier.
+Anishchenko et al.~\cite{anishchenko2018machine} employed a modified AlexNet as a classifier.
 A few different approaches were also reported, such as K-nearest neighbor classifiers by Sehairi et al.~\cite{sehairi2018elderly} and Kwolek et al.~\cite{kwolek2015improving}.
 Hidden Markov model by Zerrouki et al.~\cite{zerrouki2018combined} and Qian et al.~\cite{qian2017recognizing}.
-Particle filtering by Yu et al.~\cite{yu2009fall}.
-And Gaussian models by Yu et al.~\cite{yu2010robust} and Rougier et al.~\cite{rougier2011robust}.
+Particle filtering by Yu et al.~\cite{yu2009fall}, Gaussian models by Yu et al.~\cite{yu2010robust} and Rougier et al.~\cite{rougier2011robust}.
 Furthermore, Xu et al.~\cite{xu2018new} produced a survey on fall detections systems.
 
-This work's main contribution is the development and evaluation of hand-crafted features in a multi-stream learning model.
-To this end, we compare the effectiveness of three features extracted from videos frames: (i) optical flow, (ii) saliency map, and (iii) RGB features.
-These features a fed to a three-stream VGG-16 architecture, and their results compared with the literature.
+The main contribution of this work is the development and evaluation of handcrafted features in a multi-stream learning model.
+We compare the effectiveness of three features extracted from videos frames: (i) optical flow, (ii) saliency map, and (iii) RGB data.
+These features are fed to a three-stream VGG-16 architecture, and their results compared with the literature.
 
 We organized this paper as follows.
-In Section~\ref{sec:method} we detail the proposed three-stream methodology.
-In Section~\ref{sec:experiments} we performed experiments and compared their results to other works in the literature.
-Moreover, in Section~\ref{sec:conclusion} we elaborate on some points and future work suggestions.
+In Section~\ref{sec:method}, we detail the proposed three-stream methodology for fall detection.
+In Section~\ref{sec:experiments}, we performed experiments and compared their results to other approaches available in the literature.
+Finally, in Section~\ref{sec:conclusion}, we conclude the work and suggest directions for future work.
 
@@
 
-In this section, we describe a few relevant concepts employed in Section~\ref{sec:method}.
+In this section, we describe some relevant concepts related to the topic under investigations and employed in Section~\ref{sec:method}.
 
@@
 
-Optical flow is a hand-crafted feature that conveys movement information between two frames of a video, either by object or camera movement.
+Optical flow is a handcrafted feature that conveys movement information between two frames of a video, either by object or camera movement.
 Its ability to describe movement enables this feature to support the temporal aspect of a fall event in a deep network.
+
+\begin{figure*}[!htb]
+\centerline{\includegraphics[width=0.55\linewidth]{figures/overview.png}}
+\caption{Main components of the proposed fall detection method.}
+\label{fig:overview}
+\end{figure*}
 
@@
 Another frame collected $dt$ time later, and the distance that the same pixel moved $(dx, dy)$ is described in Equation~\ref{eq:of-dist}.
-
-Optical flow's Equation~\ref{eq:of} is formed after applying a Taylor series approximation of right-hand side and dividing by $dt$, $f_t$ is the gradient given time, $f_x$, $f_y$, $u$, and $v$ are given in Equation~\ref{eq:of-grad}.
-Values of $u$ and $v$ can be achieved by different methods, such as the classical Lucas-Kanade~\cite{jain2018abnormal} or the one used in this work: Gunnar-Farneb{\"a}ck~\cite{lowhur2015dense}.
-
 \begin{equation}
@@
 \end{equation}
+
+Equation~\ref{eq:of} is formed after applying a Taylor series approximation of right-hand side and dividing by $dt$, $f_t$ is the gradient given time, $f_x$, $f_y$, $u$, and $v$ are given in Equation~\ref{eq:of-grad}.
+Values of $u$ and $v$ can be achieved by different methods, such as the classical Lucas-Kanade~\cite{jain2018abnormal} or the one used in this work: Gunnar-Farneb{\"a}ck~\cite{lowhur2015dense}.
 \begin{equation}
@@
 
-Envisioned as a visualizing technique to understand the learning process behind a deep network.
+Saliency map is envisioned as a visualizing technique to understand the learning process behind a deep network.
 Its extraction can occur in many ways, one of those being the practice of feeding an image $I$ and its class label $c$ to the network, then, freezing the weights on the network and compute the gradients of $c$ to the pixels of $I$.
@@
 
-The choice of saliency map as a stream is due to its spatial relation to the frame, as the raw RGB frames are prone to environmental interference, and its performance in the works of Zuo et al.~\cite{zuo2019enhanced} and Meng et al.~\cite{Meng2018interpretable}.
-We applied Sundararajan's et al.~\cite{sundararajan2017axiomatic} saliency method in this work.
+The choice of saliency map as a stream is due to its spatial relation to the frame, as the raw RGB frames are prone to environmental interference, and its performance in the works developed by Zuo et al.~\cite{zuo2019enhanced} and Meng et al.~\cite{Meng2018interpretable}.
+In our work, we applied the saliency method described by Sundararajan et al.~\cite{sundararajan2017axiomatic}.
 
-\section{Method}
+\section{Fall Detection Method}
 \label{sec:method}
 
-As further detailed below, to classify between fall and not fall in video sequences we used an ensemble of VGG-16s and evaluated them,  Figure~\ref{fig:overview} shows an overview of the method.
-
-\begin{figure}[htbp]
-\centerline{\includegraphics[width=\linewidth]{figures/overview.png}}
-\caption{Methodology overview.}
-\label{fig:overview}
-\end{figure}
+As further detailed in the following subsections, we used an ensemble of VGG-16s to classify between fall and not fall in video sequences.
+Figure~\ref{fig:overview} illustrates an overview of the proposed method.
 
@@
 
-The first 14 layers of the VGG-16 architecture were trained on the ImageNet~\cite{imagenet_cvpr09} dataset, and later on, these same layers were fine-tuned over the UCF101~\cite{soomro2012ucf101} dataset.
+The first 14 layers of the VGG-16 architecture were trained on the ImageNet~\cite{imagenet_cvpr09} dataset and, later on, these same layers were fine-tuned over the UCF101~\cite{soomro2012ucf101} dataset.
 The reasoning being that the network would initially learn low-level features from the ImageNet classes, and focus these features on human activities with the UCF101 videos, Figure~\ref{fig:pre14}.
-N\'u\~nez-Marcos et al.~\cite{nunez2017vision} executed this step and released their weights files publicly.
+N\'u\~nez-Marcos et al.~\cite{nunez2017vision} executed this step and released their weight files publicly.
 
-\begin{figure}[htbp]
-\centerline{\includegraphics[width=0.9\linewidth]{figures/pre14.png}}
-\caption{Deep layers being trained by ImagetNet and UCF101.}
+\begin{figure}[!htb]
+\centerline{\includegraphics[width=0.96\linewidth]{figures/pre14.png}}
+\caption{Deep layers being trained on ImageNet and UCF101 datasets.}
 \label{fig:pre14}
@@
 We froze the 14 initial layer's weights and fine-tuned the last two fully connected layers were fine-tuned, with dropout regularization.
-Each stream executed this last fine-tuning step, totaling three executions, Figure~\ref{fig:pos14}.
+Each stream executed this last fine-tuning step, totaling three executions (Figure~\ref{fig:pos14}).
 
-\begin{figure}[htbp]
-\centerline{\includegraphics[width=0.4\linewidth]{figures/pos14.png}}
-\caption{Fully connected layers training.}
+\begin{figure}[!htb]
+\centerline{\includegraphics[width=0.43\linewidth]{figures/pos14.png}}
+\caption{Fully connected layer training.}
 \label{fig:pos14}
@@
 Inspired on this finding, an SVM classifier fed with the outputs of each stream, vectors between 0 and 1, generates a ($x$, $y$, $z$) vector.
-A second SVM uses this vector to classify between fall and not fall, Figure~\ref{fig:overview}.
+A second SVM uses this vector to classify between fall and not fall (Figure~\ref{fig:overview}).
 
@@
 
-The features Optical Flow and Saliency map were fed to the streams we explained in Subsection~\ref{sec:classification}, and furthermore, given the neural networks capability to learn relevant features to describe their input, the RGB frame itself was fed to the third stream.
+The optical flow and saliency map features were fed to the streams, explained in Subsection~\ref{sec:classification}.
+Furthermore, given the neural networks capability of learning relevant features to describe their input, the RGB frame itself was fed to the third stream.
 
-\paragraph{Optical Flow} represents the temporal relation between frames, and to fully gather this property it was used as a stack of optical flows on top of a sliding window of frames, as suggested by N\'u\~nez-Marcos et al.~\cite{nunez2017vision}.
+\paragraph{Optical Flow} represents the temporal relation between frames and to fully gather this property it was used as a stack of optical flows on top of a sliding window of frames, as suggested by N\'u\~nez-Marcos et al.~\cite{nunez2017vision}.
 The sliding window has a size of $L$ frames and gathers 2$L$ components ($L$ horizontal ($d_t^x$) + $L$ vertical ($d_t^y$) optical flow component vector fields) creating a stack $O$ = \{$d_t^x$, $d_t^y$, $d_{t+1}^x$, $d_{t+1}^y$, ..., $d_{t+L}^x$, $d_{t+L}^y$ \}.
-The total number of stacks is given by $N$-$L$+$1$, where $N$ is the number of frames in a video, Figure~\ref{fig:of} shows and extracted example.
-\paragraph{Saliency Map} is composed of pixels varying from 0 to 1, and was fed as a gray-scale image to the network, Figure~\ref{fig:sal} shows and extracted example.
+The total number of stacks is given by $N$-$L$+$1$, where $N$ is the number of frames in a video.
+Figure~\ref{fig:of} shows an extracted example.
 
-\begin{figure}[htbp]
+\begin{figure}[!htb]
 \centerline{\includegraphics[width=\linewidth]{figures/of.png}}
@@
 
-\begin{figure}[htbp]
+\paragraph{Saliency Map} is composed of pixels varying from 0 to 1, and was fed as a gray-scale image to the network. Figure~\ref{fig:sal} shows and extracted example.
+
+\begin{figure}[!htb]
 \centerline{\includegraphics[width=\linewidth]{figures/sal.png}}
@@
 
-Our experiments were performed on two publicly available datasets, \textit{URFD}~\cite{kepski2014human} and \textit{FDD}~\cite{charfi2013optimised}.
+Our experiments were performed on two publicly available datasets: URFD~\cite{kwolek2014human} and FDD~\cite{charfi2013optimised}.
 
-\paragraph{URFD dataset} contains 70 videos: (i) 30 videos of falls; and (ii) 40 videos of daily living activities, recorded from a top-down and front view perspective by two Microsoft Kinect cameras.
-Each frame is labeled in three categories, if the person is lying on the ground, not lying on the ground, and in an intermediate pose.
-\paragraph{FDD dataset} is composed of 191 videos of which 143 are falls, recorded from a surveillance camera perspective by a single RGB camera. With every frame annotated between fall and not fall.
+The URFD dataset contains 70 videos: (i) 30 videos of falls; and (ii) 40 videos of daily living activities, recorded from a top-down and front view perspective by two Microsoft Kinect cameras.
+Each frame is labeled in three categories: if the person is lying on the ground, not lying on the ground, and in an intermediate pose.
 
-For the sake of comparison with other works we evaluated our method by three metrics: (i) Sensitivity reflecting the true positive rate, (ii) Specificity also known as the true negative rate, and (iii) Accuracy representing the overall performance of the method.
+The FDD dataset is composed of 191 videos, of which 143 are falls, recorded from a surveillance camera perspective by a single RGB camera. With every frame annotated between fall and not fall.
+
+To enable a comparison with other works, we evaluated our method through three metrics: (i) sensitivity, which reflects the true positive rate; (ii) specificity, also known as the true negative rate; and (iii) accuracy, which represents the overall performance of the method.
+
 We used a learning rate of $10^{-4}$, 500 epochs, 5-fold cross-validation, mini-batches of $2^{10}$, and Adam optimization.
-We also experimented with different classes weights, however, further tuning of the hyper-parameters we were able to keep both classes on the same weight.
+We also experimented with different classes and weights, however, further tuning of the hyper-parameters we were able to keep both classes on the same weight.
 As explained in Section~\ref{sec:classification}, a double SVM is used to ensemble the outputs.
 
-Tables~\ref{tab:urfd-ensem} and~\ref{tab:urfd-our-their} shows the results obtained over the URFD dataset.
-In Table~\ref{tab:urfd-ensem} we compare each single-stream feature with their multi-stream counterpart.
+Tables~\ref{tab:urfd-ensem} and~\ref{tab:urfd-our-their} show the results obtained on the URFD dataset.
+In Table~\ref{tab:urfd-ensem}, we compare each single-stream feature with their multi-stream counterpart.
 The optical flow single-stream acquired the highest accuracy, at 97.57\%, and the multi-stream was still able to outperform it, at 98.84\%.
 Table~\ref{tab:urfd-our-their} compares our result with other works in the literature, whilst not all works measured their sensitivity and specificity, all of them reported their accuracy.
-Our method's accuracy and specificity performed better than most and kept the same 100\% sensitivity.
-Lu et al.~\cite{lu2018deep} was the only work to perform better than ours, and we believe the reason for such is the temporal importance to detect a fall event, and their usage of LSTM would better cater this relationship.
 
-\begin{table}[]
+The accuracy and specificity of our method performed better than most and kept the same 100\% sensitivity.
+The approach developed by Lu et al.~\cite{lu2019deep} was the only work that outperformed ours.
+We conjecture that the reason for such is the temporal importance to detect a fall event, and their usage of LSTM would better cater this relationship.
+
+\begin{table*}[!htb]
+\renewcommand{\tabcolsep}{2.5mm}
+\renewcommand{\arraystretch}{1.15}
 \centering
-\caption{URFD single-stream \textit{vs} multi-stream, decreasing accuracy.}
+\caption{Results on URFD dataset for single-stream \textit{vs} multi-stream (descending order of accuracy).}
 \label{tab:urfd-ensem}
-\begin{tabular}{llcccl}
-\hline
- &  & Sens. (\%) & Spec. (\%) & Acc. (\%) &  \\ \hline
- & OF + RGB + Sal & \textbf{100} & \textbf{98.77} & \textbf{98.84} &  \\
- & Optical Flow & \textbf{100} & 97.42 & 97.57 &  \\
- & RGB & \textbf{100} & 96.35 & 96.56 &  \\
- & Saliency & 93.67 & 93.39 & 93.40 &  \\ \hline
-\end{tabular}
-\end{table}
-
-\begin{table*}[]
-\centering
-\caption{URFD our method \textit{vs} literature, decreasing accuracy.}
-\label{tab:urfd-our-their}
-\begin{tabular}{llcccl}
-\hline
- &                                                      & Sensitivity (\%)  & Specificity (\%)  & Accuracy (\%)     & \\ \hline
- & Lu et al.~\cite{lu2018deep}                          & -                 & -                 & \textbf{99.27}    & \\
- & Ours                                                 & \textbf{100}      & \textbf{98.77}    & 98.84             & \\
- & Panahi et al.~\cite{panahi2018human}                 & 97.05             & 97.02             & 97.14             & \\
- & Zerrouki and Houacine~\cite{zerrouki2018combined}    & -                 & -                 & 96.88             & \\
- & Harrou et al.~\cite{harrou2017vision}                & -                 & -                 & 96.66             & \\
- & Abobakr et al.~\cite{abobakr2017skeleton}            & \textbf{100}      & 0.91              & 96.00             & \\
- & Bhandari et al.~\cite{bhandari2017novel}             & 96.66             & -                 & 95.71             & \\
- & Kwolek and Kepski~\cite{kwolek2015improving}         & \textbf{100}      & 92.50             & 95.71             & \\
- & N\'u\~nez-Marcos et al.~\cite{nunez2017vision}       & \textbf{100}      & 92.00             & 95.00             & \\
- & Sase et al.~\cite{sase2018human}                     & 81.00             & -                 & 90.00             & \\ \hline
+\begin{tabular}{lccc}
+\toprule
+ & Sensitivity (\%) & Specificity (\%) & Accuracy (\%) \\
+ \midrule
+ OF + RGB + Saliency & \textbf{100} & \textbf{98.77} & \textbf{98.84} \\
+ Optical Flow        & \textbf{100} & 97.42          & 97.57          \\
+ RGB                 & \textbf{100} & 96.35          & 96.56          \\
+ Saliency            & 93.67        & 93.39          & 93.40          \\
+ \bottomrule
 \end{tabular}
@@
 
-Tables~\ref{tab:fdd-ensem} and~\ref{tab:fdd-our-their} reports the results extracted from the FDD dataset.
+\begin{table*}[!htb]
+\renewcommand{\tabcolsep}{2.5mm}
+\renewcommand{\arraystretch}{1.15}
+\centering
+\caption{Comparison of the results on URFD datasets (descending order of accuracy).}
+\label{tab:urfd-our-their}
+\begin{tabular}{lccc}
+ \toprule
+                                                      & Sensitivity (\%)  & Specificity (\%)  & Accuracy (\%)  \\
+ \midrule
+ Lu et al.~\cite{lu2019deep}                          & -                 & -                 & \textbf{99.27} \\
+ Ours                                                 & \textbf{100}      & \textbf{98.77}    & 98.84          \\
+ Carneiro et al.~\cite{Carneiro2019}                  & \textbf{100}      & 98.61             & 98.77          \\
+ Panahi et al.~\cite{panahi2018human}                 & 97.05             & 97.02             & 97.14          \\
+ Zerrouki and Houacine~\cite{zerrouki2018combined}    & -                 & -                 & 96.88          \\
+ Harrou et al.~\cite{harrou2017vision}                & -                 & -                 & 96.66          \\
+ Abobakr et al.~\cite{abobakr2017skeleton}            & \textbf{100}      & 0.91              & 96.00          \\
+ Bhandari et al.~\cite{bhandari2017novel}             & 96.66             & -                 & 95.71          \\
+ Kwolek and Kepski~\cite{kwolek2015improving}         & \textbf{100}      & 92.50             & 95.71          \\
+ N\'u\~nez-Marcos et al.~\cite{nunez2017vision}       & \textbf{100}      & 92.00             & 95.00          \\
+ Sase et al.~\cite{sase2018human}                     & 81.00             & -                 & 90.00          \\
+ \bottomrule
+\end{tabular}
+\end{table*}
+
+Tables~\ref{tab:fdd-ensem} and~\ref{tab:fdd-our-their} report the results extracted from the FDD dataset.
 Homologous to the URFD report, Table~\ref{tab:fdd-ensem} compares each single-stream with the multi-stream approach.
 The multi-stream achieved 99.51\% accuracy, and the highest single-stream score was again the optical flow, with 99.11\%.
-When comparing our results with the literature, in Table~\ref{tab:fdd-our-their}, our's outperformed every other one, regarding accuracy and sensitivity.
-And was 0.05\% worse then Charfi's et al.~\cite{charfi2013optimised} specificity.
-Our results also confirmed the findings of Wang et al.~\cite{wang2015towards} since each feature stream did not perform great on their own, but when applied together they contributed to state of the art results towards fall detection.
+When comparing our results against the literature, in Table~\ref{tab:fdd-our-their}, ours outperformed every other one, regarding accuracy and sensitivity.
+It was 0.05\% worse than Charfi et al.'s~\cite{charfi2013optimised} specificity.
+Our results also confirmed the findings of Wang et al.~\cite{wang2015towards} since each feature stream did not perform great on their own, however, when applied together, they contributed to the state-of-the-art results towards fall detection.
 
-\begin{table}[]
+\begin{table*}[!htb]
+\renewcommand{\tabcolsep}{2.5mm}
+\renewcommand{\arraystretch}{1.15}
 \centering
-\caption{FDD single-stream \textit{vs} multi-stream, decreasing accuracy.}
+\caption{Results on FDD dataset for single-stream \textit{vs} multi-stream (descending order of accuracy).}
 \label{tab:fdd-ensem}
-\begin{tabular}{llcccl}
-\hline
- &  & Sens. (\%) & Spec. (\%) & Acc. (\%) &  \\ \hline
- & OF + RGB + Sal & \textbf{99.43} & \textbf{99.55} & \textbf{99.51} &  \\
- & Optical Flow & 99.07             & 99.12             & 99.11             &  \\
- & RGB & 98.85             & 98.41             & 98.55             &  \\
- & Saliency & 88.39             & 92.40             & 91.25             & \\ \hline
+\begin{tabular}{lccc}
+\toprule
+ & Sensitivity (\%) & Specificity (\%) & Accuracy (\%) \\
+ \midrule
+ OF + RGB + Saliency & \textbf{99.43} & \textbf{99.55} & \textbf{99.51} \\
+ Optical Flow        & 99.07          & 99.12          & 99.11          \\
+ RGB                 & 98.85          & 98.41          & 98.55          \\
+ Saliency            & 88.39          & 92.40          & 91.25          \\
+ \bottomrule
 \end{tabular}
-\end{table}
+\end{table*}
 
-\begin{table*}[]
+\begin{table*}[!htb]
+\renewcommand{\tabcolsep}{2.5mm}
+\renewcommand{\arraystretch}{1.15}
 \centering
-\caption{FDD our method \textit{vs} literature, decreasing accuracy.}
+\caption{Comparison of the results on FDD dataset (descending order of accuracy).}
 \label{tab:fdd-our-their}
-\begin{tabular}{llcccl}
-\hline
- &                                                      & Sensitivity (\%)  & Specificity (\%)  & Accuracy (\%)     & \\ \hline
- & Ours                                                 & \textbf{99.43}    & 99.55             & \textbf{99.51}    & \\
- & Lu et al.~\cite{lu2018deep}                          & -                 & -                 & 99.36             & \\
- & Sehairi et al.~\cite{sehairi2018elderly}             & -                 & -                 & 98.91             & \\
- & Zerrouki and Houacine~\cite{zerrouki2018combined}    & -                 & -                 & 97.02             & \\
- & Harrou et al.~\cite{harrou2017vision}                & -                 & -                 & 97.02             & \\
- & Charfi et al.~\cite{charfi2012definition}            & 98.0              & \textbf{99.60}    & -                 & \\
- & N\'u\~nez-Marcos et al.~\cite{nunez2017vision}       & 99.0              & 97.00             & 97.00             & \\ \hline
+\begin{tabular}{lccc}
+\toprule
+ & Sensitivity (\%)  & Specificity (\%)  & Accuracy (\%) \\
+ \midrule
+ Ours                                                 & 99.43             & 99.55             & \textbf{99.51} \\
+ Lu et al.~\cite{lu2019deep}                          & -                 & -                 & 99.36          \\
+ Sehairi et al.~\cite{sehairi2018elderly}             & -                 & -                 & 98.91          \\
+ Carneiro et al.~\cite{Carneiro2019}                  & \textbf{99.9}     & 98.32             & 98.43          \\
+ Zerrouki and Houacine~\cite{zerrouki2018combined}    & -                 & -                 & 97.02          \\
+ Harrou et al.~\cite{harrou2017vision}                & -                 & -                 & 97.02          \\
+ Charfi et al.~\cite{charfi2012definition}            & 98.0              & \textbf{99.60}    & -              \\
+ N\'u\~nez-Marcos et al.~\cite{nunez2017vision}       & 99.0              & 97.00             & 97.00          \\
+\bottomrule
 \end{tabular}
@@
 
-This paper proposes to detect human fall events, based on the employment of a multi-stream convolutional neural network.
-Each stream was served an extracted feature, them being: (i) optical flow, (ii) saliency map, and (iii) the RGB frame itself, the double SVM performed the ensemble approach.
-e tested the proposed method on URFD and FDD datasets, and our solution outperformed the related literature in most cases, indicating that multi-stream approaches and the selected features can be useful to detect human fall events.
+In this paper, we proposed a method to detect human fall events, based on the employment of a multi-stream convolutional neural network.
+Each stream was served an extracted feature, as follows: (i) optical flow, (ii) saliency map, and (iii) the RGB frame itself.
+The double SVM performed the ensemble approach.
+The proposed method was evaluated on the RFD and FDD datasets.
+Our solution outperformed the related literature in most cases, indicating that multi-stream approaches and the selected features can be useful to detect human fall events.
 
 It is worth discussing the selected features and some literature results.
-As et al.~\cite{chernbumroong2012elderly} noted that privacy concerns might arise on video-based approaches, the selected features can conceal one's identity.
-Despite these feature's performance, both optical flow and saliency map are timely and computationally intensive to extract, which would halt their implementation in a real-time system.
-Considering this work's goal in exploring features to the fall detection problem, it is relevant to weight their extraction process against their results.
-And regarding other works in the literature, some seemed to dismiss the importance of the sensitivity metric, which quantifies the avoidance of false negatives.
-A World Health Organization report~\cite{who2007report}, enlightens the severity of an elderly fall, thus the importance of a high sensitivity metric.
+As et al.~\cite{chernbumroong2012elderly} noticed that privacy concerns might arise on video-based approaches, the selected features can conceal one's identity.
+Despite their feature performance, both optical flow and saliency map are timely and computationally intensive to extract, which would halt their implementation in a real-time system.
 
-Observing the results in Table~\ref{tab:urfd-our-their} and~\ref{tab:fdd-our-their}, it is possible to notice a saturation of these datasets, and as also reported by et al.~\cite{chernbumroong2012elderly}, systems trained on artificial environments did not perform as well on real-life scenarios.
-Therefore, the importance of future work to come up with a more extensive dataset that better resembles the actual application setup, Mastorakis et al.~\cite{mastorakis2018fall} published a simulated dataset of fall events.
-Method wise, as explained above, the exploration of cheaper features and deep networks that could generate comparable results, should also be focused on.
+Considering the goal of this work in exploring features to the fall detection problem, it is relevant to weight their extraction process against their results.
+Regarding other works in the literature, some seemed to dismiss the importance of the sensitivity metric, which quantifies the avoidance of false negatives.
+A World Health Organization report~\cite{who2007report} enlightens the severity of an elderly fall, thus the importance of a high sensitivity metric.
 
-\section*{Acknowledgment}
+From the results reported in Tables~\ref{tab:urfd-our-their} and~\ref{tab:fdd-our-their}, it is possible to observe a saturation of these datasets, and as also reported by Chernbumroong et al.~\cite{chernbumroong2012elderly}, systems trained on artificial environments did not perform as well on real-life scenarios.
+Therefore, since it is important to come up with a more extensive dataset that better resembles the actual application setup, Mastorakis et al.~\cite{mastorakis2018fall} published a simulated dataset of fall events.
+Cheaper features and deep networks for generating comparable results could also be explored.
 
-%\begin{thebibliography}{00}
-%\end{thebibliography}
+\section*{Acknowledgments}
+
+Omitted for blind review.
 

### 2019-09-12 main.tex
Updates from Overleaf

--- 2019-07-17 paper.tex
@@
 
-\title{Paper Title*\\
-\thanks{Identify applicable funding agency here. If none, delete this.}
-}
+\title{MO443 - Assignment I}
 
-\author{\IEEEauthorblockN{1\textsuperscript{st} Given Name Surname}
-\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
-\textit{name of organization (of Aff.)}\\
-City, Country \\
-email address}
-\and
-\IEEEauthorblockN{2\textsuperscript{nd} Given Name Surname}
-\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
-\textit{name of organization (of Aff.)}\\
-City, Country \\
-email address}
-\and
-\IEEEauthorblockN{3\textsuperscript{rd} Given Name Surname}
-\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
-\textit{name of organization (of Aff.)}\\
-City, Country \\
-email address}
-\and
-\IEEEauthorblockN{4\textsuperscript{th} Given Name Surname}
-\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
-\textit{name of organization (of Aff.)}\\
-City, Country \\
-email address}
-\and
-\IEEEauthorblockN{5\textsuperscript{th} Given Name Surname}
-\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
-\textit{name of organization (of Aff.)}\\
-City, Country \\
-email address}
-\and
-\IEEEauthorblockN{6\textsuperscript{th} Given Name Surname}
-\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
-\textit{name of organization (of Aff.)}\\
-City, Country \\
-email address}
-}
+\author{210404 -- Guilherme Vieira Leite}
 
@@
 
-\begin{abstract}
-With falls being, at the same time more susceptible in advanced ages and the second most common cause of accidental death to elders, detecting falls became a necessary research topic to an aging population~\cite{who2007report}.
-To this effect, we proposed and evaluated the employment of a multi-stream approach to detect fall events.
-Three features (optical flow, saliency map, and RGB data) fed to each stream of a VGG-16 and classified by an SVM of whether there was or not a fall event.
-We experimented on two datasets URFD and FDD, achieving respectively 98.84\% and 99.51\% accuracy, outperforming the majority of reviewed solutions.
-\end{abstract}
-
-\begin{IEEEkeywords}
-Multi-stream, optical flow, saliency, video, deep learning
-\end{IEEEkeywords}
-
 \section{Introduction}
 
-With deteriorating health in advanced ages, even a minor fall can trigger a chain reaction of serious psychological and physical injuries to the elder population.
-Hence, the motivation for ambient assistant living solutions to both avoids falling from occurring and reducing the interval between a fall and help arrival.
-The studies conducted to detect falls as soon as they happen can be split into two main categories.
-Hardware reliant solutions, such as accelerometers and IMUs.
-Which are met with frustration from the subjects, mainly towards forgetting to use the device, despite their fall detection performance.
-And vision-based solutions, which allied to machine learning techniques have shown promising results and, furthermore, not relying on the subject's set up to operate.
+In this work we explore some variants of the dithering technique and their effect on images. The implemented variant of dithering is the error
 
-Throughout the fall detection literature, techniques vary from threshold activation based, such as Sase et al.~\cite{sase2018human} detecting regions of interest after background subtraction, and a threshold activation function if the region of interest was under a third of the subject height in the frame.
-Bhandari et al.~\cite{bhandari2017novel} determined regions of interest via Shi-Tomasi, tracked them using Lucas-Kanade and set a threshold on the region of interest's speed and motion.
-And Albawendi et al.~\cite{albawendi2018video} who used a threshold activation on silhouette shape.
-Another commonly used classification technique is support vector machine (SVM), used by Harrou et al.~\cite{harrou2017vision} that fed a feature extractor with the subject segmented from the frame.
-They compared extractor output with a multivariate exponentially-weighted moving average (MEWMA) and classified by an SVM.
-Panahi et al.~\cite{panahi2018human} subtracted the background from depth images, fitted an ellipse in the subject's shape, and classified it with SVM.
-Abobakr et al.~\cite{abobakr2017skeleton} also subtracted the background from depth images, applied a random decision forest to estimate the subject's posture, and an SVM to classify it.
-Regarding the subject's privacy, both Edgcomb et al.~\cite{edgcomb2012automated} and Lin et al.~\cite{lin2013fall} investigated privacy-prone features, such as blurring, silhouetting, and covering the body with shapes.
-Lu et al.~\cite{lu2018deep} employed a 3D convolutional neural network (CNN) followed by a long short-term memory (LSTM).
-Huang et al.~\cite{huang2018video} extracted the human pose with OpenPose and classified it with a VGG-16 architecture.
-N\'u\~nez-Marcos et al.~\cite{nunez2017vision} extracted the dense optical flow (OF) and also served it to a VGG-16.
-And Anishchenko et al.~\cite{anishchenko2018machine} employed a modified AlexNet as a classifier.
-A few different approaches were also reported, such as K-nearest neighbor classifiers by Sehairi et al.~\cite{sehairi2018elderly} and Kwolek et al.~\cite{kwolek2015improving}.
-Hidden Markov model by Zerrouki et al.~\cite{zerrouki2018combined} and Qian et al.~\cite{qian2017recognizing}.
-Particle filtering by Yu et al.~\cite{yu2009fall}.
-And Gaussian models by Yu et al.~\cite{yu2010robust} and Rougier et al.~\cite{rougier2011robust}.
-Furthermore, Xu et al.~\cite{xu2018new} produced a survey on fall detections systems.
+\section{Dithering Methods}
 
-This work's main contribution is the development and evaluation of hand-crafted features in a multi-stream learning model.
-To this end, we compare the effectiveness of three features extracted from videos frames: (i) optical flow, (ii) saliency map, and (iii) RGB features.
-These features a fed to a three-stream VGG-16 architecture, and their results compared with the literature.
+The many implemented techniques differentiate by their mask and the way they are applied to the image.
 
-We organized this paper as follows.
-In Section~\ref{sec:method} we detail the proposed three-stream methodology.
-In Section~\ref{sec:experiments} we performed experiments and compared their results to other works in the literature.
-Moreover, in Section~\ref{sec:conclusion} we elaborate on some points and future work suggestions.
+\subsection{left2right}
+\subsection{right2left}
+\subsection{zigzag}
 
-\section{Background}
-\label{background}
-
-In this section, we describe a few relevant concepts employed in Section~\ref{sec:method}.
-
-\subsection{Optical Flow}
-\label{sec:opticalflow}
-
-Optical flow is a hand-crafted feature that conveys movement information between two frames of a video, either by object or camera movement.
-Its ability to describe movement enables this feature to support the temporal aspect of a fall event in a deep network.
-
-The extraction process considers a video frame as $I$ and $I(x, y, t)$ a pixel in this frame.
-Another frame collected $dt$ time later, and the distance that the same pixel moved $(dx, dy)$ is described in Equation~\ref{eq:of-dist}.
-
-Optical flow's Equation~\ref{eq:of} is formed after applying a Taylor series approximation of right-hand side and dividing by $dt$, $f_t$ is the gradient given time, $f_x$, $f_y$, $u$, and $v$ are given in Equation~\ref{eq:of-grad}.
-Values of $u$ and $v$ can be achieved by different methods, such as the classical Lucas-Kanade~\cite{jain2018abnormal} or the one used in this work: Gunnar-Farneb{\"a}ck~\cite{lowhur2015dense}.
-
-\begin{equation}
-\label{eq:of-dist}
-I(x, y, t)=I(x+dx, y+dy, t+dt)
-\end{equation}
-\begin{equation}
-\label{eq:of}
-f_xu + f_yv + f_t=0
-\end{equation}
-\begin{equation}
-\label{eq:of-grad}
-f_x = \frac{\partial f}{\partial x}; \quad f_y = \frac{\partial f}{\partial y}u = \frac{\partial x}{\partial t}; \quad v = \frac{\partial y}{\partial t}
-\end{equation}
-
-\subsection{Saliency Map}
-\label{sec:saliency}
-
-Envisioned as a visualizing technique to understand the learning process behind a deep network.
-Its extraction can occur in many ways, one of those being the practice of feeding an image $I$ and its class label $c$ to the network, then, freezing the weights on the network and compute the gradients of $c$ to the pixels of $I$.
-Consider $S_c(I)$ to be the class score function for an image $I$ and, for this simple explanation, that it is a simple linear function, $S_c(I) = w_c^{T} + b_c$.
-With $w$ being the weights of the network and $b$ the bias, it is possible to notice that the magnitude of elements of $w$ affects the importance of the corresponding pixels in $I$ with class $c$.
-
-The choice of saliency map as a stream is due to its spatial relation to the frame, as the raw RGB frames are prone to environmental interference, and its performance in the works of Zuo et al.~\cite{zuo2019enhanced} and Meng et al.~\cite{Meng2018interpretable}.
-We applied Sundararajan's et al.~\cite{sundararajan2017axiomatic} saliency method in this work.
-
-\section{Method}
-\label{sec:method}
-
-As further detailed below, to classify between fall and not fall in video sequences we used an ensemble of VGG-16s and evaluated them,  Figure~\ref{fig:overview} shows an overview of the method.
+\section{Results}
 
 \begin{figure}[htbp]
-\centerline{\includegraphics[width=\linewidth]{figures/overview.png}}
-\caption{Methodology overview.}
-\label{fig:overview}
+\centerline{\includegraphics{figures/left2right/flo_color_juquinha.png}}
+\caption{Example of a figure caption.}
+\label{fig}
 \end{figure}
 
-\subsection{Transfer Learning}
-
-The selected datasets, further detailed in Section~\ref{sec:experiments}, possess relatively few human fall samples in their videos, which would limit the CNNs learning capabilities to detect fall events.
-Hence, the importance of transfer learning.
-
-The first 14 layers of the VGG-16 architecture were trained on the ImageNet~\cite{imagenet_cvpr09} dataset, and later on, these same layers were fine-tuned over the UCF101~\cite{soomro2012ucf101} dataset.
-The reasoning being that the network would initially learn low-level features from the ImageNet classes, and focus these features on human activities with the UCF101 videos, Figure~\ref{fig:pre14}.
-N\'u\~nez-Marcos et al.~\cite{nunez2017vision} executed this step and released their weights files publicly.
-
-\begin{figure}[htbp]
-\centerline{\includegraphics[width=0.9\linewidth]{figures/pre14.png}}
-\caption{Deep layers being trained by ImagetNet and UCF101.}
-\label{fig:pre14}
-\end{figure}
-
-We froze the 14 initial layer's weights, and fine-tuned the last two fully connected layers were fine-tuned, with dropout regularization.
-This last fine-tuning was performed three times, one for each of the extracted hand-crafted features, Figure~\ref{fig:pos14}.
-
-\begin{figure}[htbp]
-\centerline{\includegraphics[width=0.4\linewidth]{figures/pos14.png}}
-\caption{Fully connected layers training.}
-\label{fig:pos14}
-\end{figure}
-
-\subsection{Classification}
-\label{sec:classification}
-
-Wang et al.~\cite{wang2015towards} reported that, networks employing multi-stream classifiers outperformed their single-streamed peers.
-Inspired on this finding, a SVM classifier fed with the outputs of each stream, vectors between 0 and 1, generates a ($x$, $y$, $z$) vector.
-This vector is then fed to a second SVM that classifies between fall and not fall, Figure~\ref{fig:overview}.
-
-\subsection{Streams Input}
-
-Two selected features were fed to the streams explained in Subsection~\ref{sec:classification}:(i) Optical Flow and (ii) Saliency Map.
-Furthermore, given the neural networks capability to learn relevant features to describe their input, the RGB frame itself was fed to the third stream.
-
-\paragraph{Optical Flow} represents the temporal relation between frames, and to fully gather this property it was used as a stack of optical flows on top of a sliding window of frames, as suggested by N\'u\~nez-Marcos et al.~\cite{nunez2017vision}.
-The sliding window has a size of $L$ frames and gathers 2$L$ components ($L$ horizontal ($d_t^x$) + $L$ vertical ($d_t^y$) optical flow component vector fields) creating a stack $O$ = \{$d_t^x$, $d_t^y$, $d_{t+1}^x$, $d_{t+1}^y$, ..., $d_{t+L}^x$, $d_{t+L}^y$ \}.
-The total number of stacks is given by $N$-$L$+$1$, where $N$ is the number of frames in a video.
-\paragraph{Saliency Map} is composed of pixels varying from 0 to 1, and was fed as a gray-scale image to the network.
-
-\section{Experiments}
-\label{sec:experiments}
-
-Our experiments were performed on two publicly available datasets, \textit{URFD}~\cite{kepski2014human} and \textit{FDD}~\cite{charfi2013optimised}.
-
-\paragraph{URFD dataset} contains 70 videos: (i) 30 videos of falls; and (ii) 40 videos of daily living activities, recorded from a top-down and front view perspective by two Microsoft Kinect cameras.
-Each frame is labeled in three categories, if the person is lying on the ground, not lying on the ground, and in an intermediate pose.
-\paragraph{FDD dataset} is composed of 191 videos of which 143 are falls, recorded from a surveillance camera perspective by a single RGB camera. With every frame annotated between fall and not fall.
-
-For the sake of comparison with other works we evaluated our method by three metrics: (i) Sensitivity reflecting the true positive rate, (ii) Specificity also known as the true negative rate, and (iii) Accuracy representing the overall performance of the method.
-We used a learning rate of $10^{-4}$, 500 epochs, 5-fold cross-validation, minibatches of $2^{10}$, and Adam optimization.
-We also experimented with differents classes weights, however, with further tuning of the hyper-parameters we were able to keep both classes on the same weight.
-The ensemble was performed by the double-SVM approach explained in Section~\ref{sec:classification}.
-
-Tables~\ref{tab:urfd-ensem} and~\ref{tab:urfd-our-their} shows the results obtained over the URFD dataset.
-In Table~\ref{tab:urfd-ensem} we compare each single-stream feature with their multi-stream counterpart.
-The higher single-stream accuracy was derived from the optical flow stream, at 97.57\%, and the multi-stream was still able to outperform it, at 98.84\%.
-Table~\ref{tab:urfd-our-their} compares our result with other works in the literature, whilst not all works measured their sensitivity
-and specificity, all of them reported their accuracy.
-Our method's accuracy and specificity performed better than most and kept the same 100\% sensitivity.
-Lu et al.~\cite{lu2018deep} was the only work to perform better than ours, and we believe the reason for such is the temporal importance to detect a fall event, and their usage of LSTM would better cater this relationship.
-
-\begin{table}[]
-\centering
-\caption{URFD single-stream \textit{vs} multi-stream, decreasing accuracy.}
-\label{tab:urfd-ensem}
-\begin{tabular}{llcccl}
-\hline
- &  & Sens. (\%) & Spec. (\%) & Acc. (\%) &  \\ \hline
- & OF + RGB + Sal & \textbf{100} & \textbf{98.77} & \textbf{98.84} &  \\
- & Optical Flow & \textbf{100} & 97.42 & 97.57 &  \\
- & RGB & \textbf{100} & 96.35 & 96.56 &  \\
- & Saliency & 93.67 & 93.39 & 93.40 &  \\ \hline
-\end{tabular}
-\end{table}
-
-\begin{table*}[]
-\centering
-\caption{URFD our method \textit{vs} literature, decreasing accuracy.}
-\label{tab:urfd-our-their}
-\begin{tabular}{llcccl}
-\hline
- &                                                      & Sensitivity (\%)  & Specificity (\%)  & Accuracy (\%)     & \\ \hline
- & Lu et al.~\cite{lu2018deep}                          & -                 & -                 & \textbf{99.27}    & \\
- & Ours                                                 & \textbf{100}      & \textbf{98.77}    & 98.84             & \\
- & Panahi et al.~\cite{panahi2018human}                 & 97.05             & 97.02             & 97.14             & \\
- & Zerrouki and Houacine~\cite{zerrouki2018combined}    & -                 & -                 & 96.88             & \\
- & Harrou et al.~\cite{harrou2017vision}                & -                 & -                 & 96.66             & \\
- & Abobakr et al.~\cite{abobakr2017skeleton}            & \textbf{100}      & 0.91              & 96.00             & \\
- & Bhandari et al.~\cite{bhandari2017novel}             & 96.66             & -                 & 95.71             & \\
- & Kwolek and Kepski~\cite{kwolek2015improving}         & \textbf{100}      & 92.50             & 95.71             & \\
- & N\'u\~nez-Marcos et al.~\cite{nunez2017vision}       & \textbf{100}      & 92.00             & 95.00             & \\
- & Sase et al.~\cite{sase2018human}                     & 81.00             & -                 & 90.00             & \\ \hline
-\end{tabular}
-\end{table*}
-
-Tables~\ref{tab:fdd-ensem} and~\ref{tab:fdd-our-their} reports the results extracted from the FDD dataset.
-Homologous to the URFD report, Table~\ref{tab:fdd-ensem} compares each single-stream with the multi-stream approach.
-The multi-stream achieved 99.51\% accuracy, and the highest single-stream score was again the optical flow, with 99.11\%.
-When comparing our results with the literature, in Table~\ref{tab:fdd-our-their}, our's outperformed every other one, regarding accuracy and sensitivity.
-And was 0.05\% worse then Charfi's et al.~\cite{charfi2013optimised} specificity.
-Our results also confirmed the findings of Wang et al.~\cite{wang2015towards}, since each feature stream did not perform great on their own, but when applyed together they contributed to state of the art results towards fall detection.
-
-\begin{table}[]
-\centering
-\caption{FDD single-stream \textit{vs} multi-stream, decreasing accuracy.}
-\label{tab:fdd-ensem}
-\begin{tabular}{llcccl}
-\hline
- &  & Sens. (\%) & Spec. (\%) & Acc. (\%) &  \\ \hline
- & OF + RGB + Sal & \textbf{99.43} & \textbf{99.55} & \textbf{99.51} &  \\
- & Optical Flow & 99.07             & 99.12             & 99.11             &  \\
- & RGB & 98.85             & 98.41             & 98.55             &  \\
- & Saliency & 88.39             & 92.40             & 91.25             & \\ \hline
-\end{tabular}
-\end{table}
-
-\begin{table*}[]
-\centering
-\caption{FDD our method \textit{vs} literature, decreasing accuracy.}
-\label{tab:fdd-our-their}
-\begin{tabular}{llcccl}
-\hline
- &                                                      & Sensitivity (\%)  & Specificity (\%)  & Accuracy (\%)     & \\ \hline
- & Ours                                                 & \textbf{99.43}    & 99.55             & \textbf{99.51}    & \\
- & Lu et al.~\cite{lu2018deep}                          & -                 & -                 & 99.36             & \\
- & Sehairi et al.~\cite{sehairi2018elderly}             & -                 & -                 & 98.91             & \\
- & Zerrouki and Houacine~\cite{zerrouki2018combined}    & -                 & -                 & 97.02             & \\
- & Harrou et al.~\cite{harrou2017vision}                & -                 & -                 & 97.02             & \\
- & Charfi et al.~\cite{charfi2012definition}            & 98.0              & \textbf{99.60}    & -                 & \\
- & N\'u\~nez-Marcos et al.~\cite{nunez2017vision}       & 99.0              & 97.00             & 97.00             & \\ \hline
-\end{tabular}
-\end{table*}
-
-\section{Conclusion and Future Work}
-\label{sec:conclusion}
-
-This paper proposes to detect human fall events, based on the employment of a multi-stream convolutional neural network.
-Each stream was served an extracted feature, them being: (i) optical flow, (ii) saliency map, and (iii) the RGB frame itself, the ensemble performed was a double SVM approach.
-The proposed method was tested on URFD and FDD datasets, and our solution outperformed the related literature in most cases, indicating that multi-stream approaches and the selected features can be useful to detect human fall events.
-
-It is worth discussing the selected features and some literature results.
-As et al.~\cite{chernbumroong2012elderly} noted that privacy concerns might arise on video-based approaches, the selected features are able to conceal one's identity.
-Despite these feature's performance, both optical flow and saliency map are timely and computational intensive to extract, which would halt their implementation in a real-time system.
-Considering this work's goal in exploring features to the fall detection problem, it is relevant to weight their extraction process against their results.
-And regarding other works in the literature, some seemed to dismiss the importance of the sensitivity metric, which quantifies the avoidance of false negatives.
-A World Health Organization report~\cite{who2007report}, enlightens the severity of an elderly fall, thus the importance of a high sensitivity metric.
-
-Observing the results in Table~\ref{tab:urfd-our-their} and~\ref{tab:fdd-our-their}, it is possible to notice a saturation of these datasets, and as also reported by et al.~\cite{chernbumroong2012elderly}, systems trained on artificial environments did not perform as well on real-life scenarios.
-Therefore, the importance of future work to come up with a more extensive dataset that better resembles the actual application setup, Mastorakis et al.~\cite{mastorakis2018fall} published a simulated dataset of fall events.
-Method wise, as explained above, the exploration of cheaper features and deep networks that could generate comparable results, should also be focused on.
-
-\section*{Acknowledgment}
-
-%\begin{thebibliography}{00}
-%\end{thebibliography}
-
-\bibliographystyle{IEEEtran}
-\bibliography{paper}
+\subsection{Error function}
 

### 2019-09-12 main.tex
Updates from Overleaf

@@
 \usepackage{xcolor}
+\usepackage{subfig}
+\usepackage{float}
+
 \def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
@@
 \section{Dithering Methods}
+\label{sec:method}
 
-The many implemented techniques differentiate by their mask and the way they are applied to the image.
+The implemented dithering methods in this work differentiates between each other by a couple of factors: (i) whether they are grayscaled or colored, and (ii) the error diffusion matrix.
 
-\subsection{left2right}
-\subsection{right2left}
-\subsection{zigzag}
+\paragraph{Color space} Dithering in the grayscale color space is performed as in the algorithm discussed in class, in a few words: the pixel is binarized, it's error is calculated and multiplied by the mask value relative to that pixel.
+To transfer this process to the RGB color space, we treated each of its three bands as if they were separate grayscale images, that were later combined together to create a dithered colored image.
+
+\paragraph{Filter matrix} Each pixel is dithered by a error metric in relation to its neighbourhood, this neighbourhood is defined by the filter matrix, how large it is and which pixels are considered in the metric.
+In this work we tested on six pre-defined error diffusion matrices: Floyd and Steinberg, Stevenson and Arce, Burkes, Sierra, Stucki, and Jarvis, Judice, and Ninke, seen in Section~\ref{sec:appendix1}.
+
+\section{Experiments}
+
+Throughout our experiments we aimed to explore the effects of dithering, while varying the color space, the error diffusion matrix and the order in which the error was diffused.
+We also exchanged the output's quality by lower processing time, shrinking all input images to around 128x128, but the algorithm is still able to process larger images.
+
+We performed dithering on {\color{red}nine} images, some provided by the professor and some particularly obtained.
+The images were chosen to exhaust the algorithm and explore its weaknesses and strengths, specially the colored dithering.
+Figure~\ref{fig:input} presents a few samples of the chosen images.
+
+\begin{figure}[H]
+	\centering
+	\subfloat{
+		{
+			\includegraphics[scale=0.7]{figures/input/baboon}
+		}
+		\label{fig:baboon}
+	}
+	\quad
+	\subfloat{
+		{
+			\includegraphics[scale=0.7]{figures/input/david}
+		}
+		\label{fig:david}
+	}
+	\quad
+	\subfloat{
+		{
+			\includegraphics[scale=0.7]{figures/input/juquinha}
+		}
+		\label{fig:juquinha}
+	}
+	\quad
+	\subfloat{
+		{
+			\includegraphics[scale=0.7]{figures/input/bee}
+		}
+		\label{fig:bee}
+	}
+	\quad
+	\subfloat{
+		{
+			\includegraphics[scale=0.7]{figures/input/peppers}
+		}
+		\label{fig:peppers}
+	}
+	\quad
+	\subfloat{
+		{
+			\includegraphics[scale=0.7]{figures/input/peppers}
+		}
+		\label{fig:peppers}
+	}
+	\caption{A sample of the images used in the experiments.}
+	\label{fig:input}
+\end{figure}
+
+We also experimented with three traversal methods, looping through the image from (i) left to right, top to bottom, (ii) right to left, bottom to top, and (iii) top to bottom, but every even row was looped left to right and every odd row was looped from right to left, seen in Figure~\ref{fig:traversal}.
+To traverse the images in these varying methods a few precautions had to be taken, since the chosen filters generates a particular effect, in which any pixel already dithered will be ignored to future error diffusion.
+We need to accommodate this effect on any traversal that differs from left to right, top to bottom, and we did so by tweaking with the filter's matrix to match the expected result, one example on Floyd and Steinberg can be seen in Table~\ref{tab:flo_inverse}.
+
+\begin{figure}[H]
+	\centering
+	\subfloat{
+		{
+			\includegraphics[scale=0.5]{figures/l2r}
+		}
+		\label{fig:l2r}
+	}
+	\quad
+	\subfloat{
+		{
+			\includegraphics[scale=0.5]{figures/r2l}
+		}
+		\label{fig:r2l}
+	}
+	\quad
+	\subfloat{
+		{
+			\includegraphics[scale=0.5]{figures/zz}
+		}
+		\label{fig:zz}
+	}
+	\caption{Traversal directions experimented on.}
+	\label{fig:traversal}
+\end{figure}
+
+\begin{table}[H]
+\centering
+\renewcommand{\arraystretch}{1.5}
+\begin{tabular}{c|c|c}
+1/16 & 5/16             & 3/16 \\ \hline
+7/16 & \textit{f(x, y)} &     
+\end{tabular}
+\caption{Floyd and Steinberg's diffusion error matrix when traversing from right to left, bottom to right.}
+\label{tab:flo_inverse}
+\end{table}
 
 \section{Results}
+\label{sec:results}
 
-\begin{figure}[htbp]
-\centerline{\includegraphics{figures/left2right/flo_color_juquinha.png}}
-\caption{Example of a figure caption.}
-\label{fig}
+In this section we present and discuss the results obtained from the methods discussed in Section~\ref{sec:method}.
+To better explore the different aspects of a dithering process we focus our discussion on three subsections bellow.
+
+\subsection{Color space}
+
+In this experiment we performed a colored dithering and a grayscaled one. We also used Floyd and Steinberg's erro diffusion
+
+\begin{figure}[H]
+	\centering
+	\subfloat{
+		{
+			\includegraphics[scale=0.7]{figures/left2right/flo_color_baboon}
+		}
+		\label{fig:baboon_color}
+	}
+	\quad
+	\subfloat{
+		{
+			\includegraphics[scale=0.7]{figures/left2right/flo_gray_baboon}
+		}
+		\label{fig:baboon_gray}
+	}
+	\caption{Traversal directions experimented on.}
+	\label{fig:baboon_colorspace}
 \end{figure}
+
+\subsection{Dithering matrices}
+
+\subsection{Traversal directions}
 
@@
 
+\section{Appendix I}
+\label{sec:appendix1}
+
+\begin{table}[!h]
+\centering
+\renewcommand{\arraystretch}{1.5}
+\begin{tabular}{c|c|c}
+     & \textit{f(x, y)} & 7/16 \\ \hline
+3/16 & 5/16             & 1/16
+\end{tabular}
+\caption{Floyd and Steinberg's diffusion error matrix.}
+\label{tab:flo}
+\end{table}
+
+\begin{table}[!h]
+\centering
+\renewcommand{\arraystretch}{1.5}
+\begin{tabular}{c|c|c|c|c|c|c}
+ & \textit{} &  & \textit{f(x, y)} &  & 32/200 &  \\ \hline
+12/200 &  & 26/200 &  & 30/200 &  & 16/200 \\ \hline
+ & 12/200 &  & 26/200 &  & 12/200 &  \\ \hline
+5/200 &  & 12/200 &  & 12/200 &  & 5/200
+\end{tabular}
+\caption{Stevenson and Arce's diffusion error matrix.}
+\label{tab:ste}
+\end{table}
+
+\begin{table}[!h]
+\centering
+\renewcommand{\arraystretch}{1.5}
+\begin{tabular}{c|c|c|c|c}
+ &  & \textit{f(x, y)} & 8/32 & 4/32 \\ \hline
+2/32 & 4/32 & 8/32 & 4/32 & 2/32
+\end{tabular}
+\caption{Burkes' diffusion error matrix.}
+\label{tab:bur}
+\end{table}
+
+\begin{table}[!h]
+\centering
+\renewcommand{\arraystretch}{1.5}
+\begin{tabular}{c|c|c|c|c}
+ &  & \textit{f(x, y)} & 5/32 & 3/32 \\ \hline
+2/32 & 4/32 & 5/32 & 4/32 & 2/32 \\ \hline
+ & 2/32 & 3/32 & 2/32 & 
+\end{tabular}
+\caption{Sierra's diffusion error matrix.}
+\label{tab:sie}
+\end{table}
+
+\begin{table}[!h]
+\centering
+\renewcommand{\arraystretch}{1.5}
+\begin{tabular}{l|l|l|l|l}
+ &  & \textit{f(x, y)} & 8/42 & 4/42 \\ \hline
+2/42 & 4/42 & 8/42 & 4/42 & 2/42 \\ \hline
+1/42 & 2/42 & 4/42 & 2/42 & 1/42
+\end{tabular}
+\caption{Stucki's diffusion error matrix.}
+\label{tab:stu}
+\end{table}
+
+\begin{table}[!h]
+\centering
+\renewcommand{\arraystretch}{1.5}
+\begin{tabular}{l|l|l|l|l}
+ &  & \textit{f(x, y)} & 7/48 & 5/48 \\ \hline
+3/48 & 5/48 & 7/48 & 5/48 & 3/48 \\ \hline
+1/48 & 3/48 & 5/48 & 3/48 & 1/48
+\end{tabular}
+\caption{Jarvis, Judice, and Ninke's diffusion error matrix.}
+\label{tab:jar}
+\end{table}
+
 \end{document}

### 2019-09-12 main.tex
Updates from Overleaf

@@
 	{
-			\includegraphics[scale=0.7]{figures/input/baboon}
+		\includegraphics[scale=0.7]{figures/input/bee}
 	}
-		\label{fig:baboon}
+	\label{fig:peppers}
 }
-	\quad
 \subfloat{
 	{
-			\includegraphics[scale=0.7]{figures/input/david}
+		\includegraphics[scale=0.7]{figures/input/bee}
 	}
-		\label{fig:david}
-	}
-	\quad
-	\subfloat{
-		{
-			\includegraphics[scale=0.7]{figures/input/juquinha}
-		}
-		\label{fig:juquinha}
+	\label{fig:peppers}
 }
@@
 	}
-		\label{fig:bee}
+	\label{fig:peppers}
 }
-	\quad
 \subfloat{
 	{
-			\includegraphics[scale=0.7]{figures/input/peppers}
+		\includegraphics[scale=0.7]{figures/input/bee}
 	}
@@
 	{
-			\includegraphics[scale=0.7]{figures/input/peppers}
+		\includegraphics[scale=0.7]{figures/input/bee}
+	}
+	\label{fig:peppers}
+}
+\subfloat{
+	{
+		\includegraphics[scale=0.7]{figures/input/bee}
 	}
@@
 
-In this experiment we performed a colored dithering and a grayscaled one. We also used Floyd and Steinberg's erro diffusion
+In this experiment we performed a colored dithering and a grayscaled one.
+Although we are not exploring the effects of error diffusion and traversal direction, we also used Floyd and Steinberg's erro diffusion and traversed the image from left to right, top to bottom.
+Figure~\ref{fig:baboon_colorspace} shows the resulting dithering, in it we can observe that overall features of the image are kept, it is still possible to identify the baboon in frame, as it is the intention of dithering.
+But on a closer inspection it is also possible to notice a drop in quality of both images, also an expected effect, for instance the lower lip of the baboon has been filled with noise and mixes with the fur.
 
@@
 	}
-	\caption{Traversal directions experimented on.}
+	\caption{Color and Grayscale dithering on Baboon.}
 	\label{fig:baboon_colorspace}
@@
 
+\begin{figure}[H]
+	\centering
+	\subfloat{
+		{
+			\includegraphics[scale=0.7]{figures/left2right/flo_color_juquinha}
+		}
+		\label{fig:flo_color_juquinha}
+	}
+	\subfloat{
+		{
+			\includegraphics[scale=0.7]{figures/left2right/ste_color_juquinha}
+		}
+		\label{fig:ste_color_juquinha}
+	}
+    \quad
+	\subfloat{
+		{
+			\includegraphics[scale=0.7]{figures/left2right/bur_color_juquinha}
+		}
+		\label{fig:bur_color_juquinha}
+	}
+	\subfloat{
+		{
+			\includegraphics[scale=0.7]{figures/left2right/sie_color_juquinha}
+		}
+		\label{fig:sie_color_juquinha}
+	}\quad
+	\subfloat{
+		{
+			\includegraphics[scale=0.7]{figures/left2right/stu_color_juquinha}
+		}
+		\label{fig:stu_color_juquinha}
+	}
+	\subfloat{
+		{
+			\includegraphics[scale=0.7]{figures/left2right/jar_color_juquinha}
+		}
+		\label{fig:jar_color_juquinha}
+	}
+	\caption{Color Error Diffusion on Cat.}
+	\label{fig:color_error_diffusion}
+\end{figure}
+
+\begin{figure}[H]
+	\centering
+	\subfloat{
+		{
+			\includegraphics[scale=0.7]{figures/left2right/flo_gray_juquinha}
+		}
+		\label{fig:flo_gray_juquinha}
+	}
+	\subfloat{
+		{
+			\includegraphics[scale=0.7]{figures/left2right/ste_gray_juquinha}
+		}
+		\label{fig:ste_cgray_juquinha}
+	}
+    \quad
+	\subfloat{
+		{
+			\includegraphics[scale=0.7]{figures/left2right/bur_gray_juquinha}
+		}
+		\label{fig:bur_gray_juquinha}
+	}
+	\subfloat{
+		{
+			\includegraphics[scale=0.7]{figures/left2right/sie_gray_juquinha}
+		}
+		\label{fig:sie_gray_juquinha}
+	}
+	\quad
+	\subfloat{
+		{
+			\includegraphics[scale=0.7]{figures/left2right/stu_gray_juquinha}
+		}
+		\label{fig:stu_gray_juquinha}
+	}
+
+	\subfloat{
+		{
+			\includegraphics[scale=0.7]{figures/left2right/jar_gray_juquinha}
+		}
+		\label{fig:jar_gray_juquinha}
+	}
+	\caption{Grayscale error diffusion on Cat.}
+	\label{fig:gray_error_diffusion}
+\end{figure}
+
 \subsection{Traversal directions}
+
+\begin{figure}[H]
+	\centering
+	\subfloat{
+		{
+			\includegraphics[scale=0.7]{figures/left2right/flo_color_bee}
+		}
+		\label{fig:l2r_flo_color_bee}
+	}
+	\subfloat{
+		{
+			\includegraphics[scale=0.7]{figures/right2left/flo_color_bee}
+		}
+		\label{fig:r2l_flo_color_bee}
+	}
+	\quad
+	\subfloat{
+		{
+			\includegraphics[scale=0.7]{figures/zigzag/flo_color_bee}
+		}
+		\label{fig:zz_flo_color_bee}
+	}
+	\caption{Color traversal direction on Girl.}
+	\label{fig:color_traversal_l2r}
+\end{figure}
+
+\begin{figure}[H]
+	\centering
+	\subfloat{
+		{
+			\includegraphics[scale=0.7]{figures/left2right/flo_gray_bee}
+		}
+		\label{fig:l2r_flo_gray_bee}
+	}
+	\subfloat{
+		{
+			\includegraphics[scale=0.7]{figures/right2left/flo_gray_bee}
+		}
+		\label{fig:r2l_flo_gray_bee}
+	}
+	\quad
+	\subfloat{
+		{
+			\includegraphics[scale=0.7]{figures/zigzag/flo_gray_bee}
+		}
+		\label{fig:zz_flo_gray_bee}
+	}
+	\caption{Grayscale traversal direction on Girl.}
+	\label{fig:gray_traversal_l2r}
+\end{figure}
 

### 2019-10-07 main.tex
Updates from Overleaf
T2

--- 2019-09-12 main.tex
@@
 
-\title{MO443 - Assignment I}
+\title{MO443 - Assignment II}
 
@@
 \section{Introduction}
-
-In this work we explore some variants of the dithering technique and their effect on images. The implemented variant of dithering is the error
-
-\section{Dithering Methods}
-
-The many implemented techniques differentiate by their mask and the way they are applied to the image.
-
-\subsection{left2right}
-\subsection{right2left}
-\subsection{zigzag}
-
+Segmentation is a vast field of research in computer vision, for its especially known applications in various industries, either to help count objects or highlighting regions of interest.
+In this work, we explore a few segmentations obtained by thresholds alone.
+More specifically we explore the strengths and weaknesses of the global threshold and a few local thresholds.
+This work is organized in the following manner: Section~\ref{sec:method} explains our methods, Section~\ref{sec:result} shows the obtained results, their parameters, and their histograms, and Section~\ref{sec:conclusion} reflects on our results and discuss a few next steps to explore in threshold segmentation.
+\section{Methods}
+\label{sec:method}
+In this section, we explain each of the methods used to perform the segmentation.
+Our methods were split between global and local ones and their results are illustrated in Section~\ref{sec:result}.\par
+Our first and simplest method was the global threshold, in which value $T$ was chosen and every pixel was segmented according to $T$.
+This method has a predetermined belief that the foreground and background of the image are well distributed in the histogram and can be split by a single $T$ value.\par
+In contrast to the global threshold, and to account for more life scenarios, we also explored local thresholds, in which each pixel has a different $T$ value according to the local neighborhood, of $n$ size, and the chosen method.
+The chosen methods and their formulas are the following, with $z(x, y)$ being the region around $pixel(x, y)$: Bernsen Eq.~\ref{eq:bernsen}, Niblack Eq.~\ref{eq:niblack},Sauvola Eq.~\ref{eq:sauvola}, Phansalskar Eq.~\ref{eq:phansalskar}, Contrast Eq.~\ref{eq:contrast}, Mean Eq.~\ref{eq:mean}, and Median Eq.~\ref{eq:median}.
+\begin{equation}
+\label{eq:bernsen}
+    T(x, y) = \frac{z_{min}(x, y) + z_{max}(x, y)}{2}
+\end{equation}
+\begin{equation}
+\label{eq:niblack}
+    T(x, y) = \mu(x, y) + k \sigma(x, y)
+\end{equation}
+\begin{equation}
+\label{eq:sauvola}
+    T(x, y) = \mu(x, y) \left[ 1 + k \left(\frac{\sigma(x, y)}{r} - 1\right)\right]
+\end{equation}
+\begin{equation}
+\label{eq:phansalskar}
+    T(x, y) = \mu(x, y) \left[ 1 + p e^{-q\mu(x, y)} + k \left( \frac{\sigma(x, y)}{r} - 1 \right) \right]
+\end{equation}
+\begin{equation}
+\label{eq:contrast}
+    T(x, y) =
+    \begin{cases}
+    0,& \texit{if} (x, y)\ closer\ to\ max(z(x, y))\\
+    255,& \texit{if} (x, y)\ closer\ to\ min(z(x, y))
+    \end{cases}
+\end{equation}
+\begin{equation}
+\label{eq:mean}
+    T(x, y) = \mu(z(x, y))
+\end{equation}
+\begin{equation}
+\label{eq:median}
+    T(x, y) = median(z(x, y))
+\end{equation}
 \section{Results}
-
+\label{sec:result}
+In this section, we present the obtained results upon implementing the methods from Section~\ref{sec:method}.
+Firstly we show the results of the global threshold followed by the many variations of local thresholds and their histograms.
+Our input images are shown in Figure~\ref{fig:input}.
 \begin{figure}[htbp]
-\centerline{\includegraphics{figures/left2right/flo_color_juquinha.png}}
-\caption{Example of a figure caption.}
-\label{fig}
+\centering
+\subfloat[Baboon]{
+	{
+		\includegraphics[scale=0.35]{figures/input/baboon}
+	}
+}
+\subfloat[Fiducial]{
+	{
+		\includegraphics[scale=0.35]{figures/input/fiducial}
+	}
+}
+\quad
+\subfloat[Monarch]{
+	{
+		\includegraphics[scale=0.35]{figures/input/monarch}
+	}
+}
+\subfloat[Peppers]{
+	{
+		\includegraphics[scale=0.35]{figures/input/peppers}
+	}
+}
+\quad
+\subfloat[Retina]{
+	{
+		\includegraphics[scale=0.35]{figures/input/retina}
+	}
+}
+\subfloat[Sonnet]{
+	{
+		\includegraphics[scale=0.35]{figures/input/sonnet}
+	}
+}
+\caption{A sample of the images used in the experiments.}
+\label{fig:input}
 \end{figure}
-
-\subsection{Error function}
-
+\subsection{Global}
+To explore the effects of a global threshold in an image we explored three distinct $T$ values, $T = 50$, $T = 128$, and $T = 200$, shown in Figure~\ref{fig:global_fiducial}.
+These values were chosen arbitrarily in a manner to explore global threshold's features.
+\begin{figure}[htbp]
+	\centering
+	\subfloat[$T = 50$]{
+		{
+			\includegraphics[scale=0.7]{figures/global/global_50_fiducial.png}
+		}
+		\label{fig:global_50_fiducial}
+	}
+	\subfloat[$T = 128$]{
+		{
+			\includegraphics[scale=0.7]{figures/global/global_128_fiducial.png}
+		}
+		\label{fig:global_128_fiducial}
+	}\quad
+	\subfloat[$T = 200$]{
+		{
+			\includegraphics[scale=0.7]{figures/global/global_200_fiducial.png}
+		}
+		\label{fig:global_200_fiducial}
+	}
+	\caption{Different $T$s on Fiducial image.}
+	\label{fig:global_fiducial}
+\end{figure}
+In Figure~\ref{fig:global_fiducial} it is possible to notice that a single $T$ value is not enough to distinguish between foreground and background.
+Figure~\ref{fig:global_50_fiducial} shows a large portion of the foreground, but there is a white spot occluding some of it, this white spot can be seen with different values of $T$, but again it will occlude other parts of the foreground.
+In general, we obtained a bad performance from lower and higher values of $T$.\par
+In Figure~\ref{fig:low_t} it is possible to notice how few features survive the thresholding with a low $T$ value, the worst case being Figure~\ref{fig:low_t_wedge}, which is completely white.
+\begin{figure}[htbp]
+	\centering
+	\subfloat[Baboon]{
+		{
+			\includegraphics[scale=0.7]{figures/global/global_50_baboon.png}
+		}
+		\label{fig:low_t_baboon}
+	}
+	\subfloat[Monarch]{
+		{
+			\includegraphics[scale=0.7]{figures/global/global_50_monarch.png}
+		}
+		\label{fig:low_t_monarch}
+	}\quad
+	\subfloat[Retina]{
+		{
+			\includegraphics[scale=0.7]{figures/global/global_50_retina.png}
+		}
+		\label{fig:low_t_retina}
+	}
+	\subfloat[Wedge]{
+		{
+			\includegraphics[scale=0.7]{figures/global/global_50_wedge.png}
+		}
+		\label{fig:low_t_wedge}
+	}
+	\caption{Low global $T$ on different images.}
+	\label{fig:low_t}
+\end{figure}
+Figure~\ref{fig:high_t} shows the same effect happening with a high $T$ values.
+We assume this happened because of a somewhat \textit{good} histogram distribution, with dark and light parts in the same image, favoring a more median threshold.
+\begin{figure}[htbp]
+	\centering
+	\subfloat[Baboon]{
+		{
+			\includegraphics[scale=0.7]{figures/global/global_200_baboon.png}
+		}
+		\label{fig:high_t_baboon}
+	}
+	\subfloat[Monarch]{
+		{
+			\includegraphics[scale=0.7]{figures/global/global_200_monarch.png}
+		}
+		\label{fig:high_t_monarch}
+	}\quad
+	\subfloat[Retina]{
+		{
+			\includegraphics[scale=0.7]{figures/global/global_200_retina.png}
+		}
+		\label{fig:high_t_retina}
+	}
+	\subfloat[Wedge]{
+		{
+			\includegraphics[scale=0.7]{figures/global/global_200_wedge.png}
+		}
+		\label{fig:high_t_wedge}
+	}
+	\caption{High global $T$ on different images.}
+	\label{fig:high_t}
+\end{figure}
+The threshold of $T = 128$ was responsible for the best results in our experiments, seen in Figure~\ref{fig:median_t}.
+In special the Baboon and Monarch in Figures~\ref{fig:median_t_baboon} and~\ref{fig:median_t_monarch}.
+\begin{figure}[htbp]
+	\centering
+	\subfloat[Baboon]{
+		{
+			\includegraphics[scale=0.7]{figures/global/global_128_baboon.png}
+		}
+		\label{fig:median_t_baboon}
+	}
+	\subfloat[Monarch]{
+		{
+			\includegraphics[scale=0.7]{figures/global/global_128_monarch.png}
+		}
+		\label{fig:median_t_monarch}
+	}\quad
+	\subfloat[Retina]{
+		{
+			\includegraphics[scale=0.7]{figures/global/global_128_retina.png}
+		}
+		\label{fig:median_t_retina}
+	}
+	\subfloat[Wedge]{
+		{
+			\includegraphics[scale=0.7]{figures/global/global_128_wedge.png}
+		}
+		\label{fig:median_t_wedge}
+	}
+	\caption{Global $T = 128$ on different images.}
+	\label{fig:median_t}
+\end{figure}
+\subsection{Local}
+We also explored and compared the effects of the seven local thresholds presented in Section~\ref{sec:method}. Their histograms are shown separately in Subsection~\ref{sec:hist}.
+\paragraph*{Bernsen} Figure~\ref{fig:bernsen_n} shows the different aspects of the area considered upon determining the threshold for each pixel.
+A larger area cleared a lot of the background noise but also corroded some of the borders on the right side of Figure~\ref{fig:bernsen_11_wedge}.
+\begin{figure}[htbp]
+	\centering
+	\subfloat[3x3]{
+		{
+			\includegraphics[scale=0.7]{figures/local/bernsen/local_ber_3_wedge.png}
+		}
+		\label{fig:bernsen_3_wedge}
+	}
+	\subfloat[7x7]{
+		{
+			\includegraphics[scale=0.7]{figures/local/bernsen/local_ber_7_wedge.png}
+		}
+		\label{fig:bernsen_7_wedge}
+	}\quad
+	\subfloat[11x11]{
+		{
+			\includegraphics[scale=0.7]{figures/local/bernsen/local_ber_11_wedge.png}
+		}
+		\label{fig:bernsen_11_wedge}
+	}
+	\caption{Bernsen with different neighbourhoods $n$ on Wedge image.}
+	\label{fig:bernsen_n}
+\end{figure}
+It is also interesting to compare the Bernsen local threshold with the global one.
+Figure~\ref{fig:global_vs_local} shows the Wedge image, previously badly segmented via global threshold, and now presents some distinguishable features.
+\begin{figure}[htbp]
+	\centering
+	\subfloat[Global]{
+		{
+			\includegraphics[scale=0.7]{figures/global/global_128_wedge.png}
+		}
+		\label{fig:global_vs_local_global}
+	}
+	\subfloat[Local]{
+		{
+			\includegraphics[scale=0.7]{figures/local/bernsen/local_ber_3_wedge.png}
+		}
+		\label{fig:global_vs_local_local}
+	}
+	\caption{Global vs Local threshold on Wedge image.}
+	\label{fig:global_vs_local}
+\end{figure}
+\paragraph*{The Niblack} method varies with the neighborhood area $n$, and by the same $k$ factor as Bernsen.
+Figure~\ref{fig:niblack_n} shows how the $n$ area affects the segmentation, although the three $n$ values segmented the optical nerve, only $n = 11$ showed a clear segmentation of the spot in the center of the image.
+Upon varying the $k$ value in Figure~\ref{fig:niblack_k} it is noticeable how $k$ affects the border by completely vanishing the image, if the value gets too high, generating a better or worse segmentation.
+\begin{figure}[htbp]
+	\centering
+	\subfloat[3x3]{
+		{
+			\includegraphics[scale=0.7]{figures/local/niblack/local_nib_3_retina.png}
+		}
+		\label{fig:niblack_3_retina}
+	}
+	\subfloat[7x7]{
+		{
+			\includegraphics[scale=0.7]{figures/local/niblack/local_nib_7_retina.png}
+		}
+		\label{fig:niblack_7_retina}
+	}\quad
+	\subfloat[11x11]{
+		{
+			\includegraphics[scale=0.7]{figures/local/niblack/local_nib_11_retina.png}
+		}
+		\label{fig:niblack_11_retina}
+	}
+	\caption{Niblack with different neighbourhoods $n$ on Retina image.}
+	\label{fig:niblack_n}
+\end{figure}
+\begin{figure}[htbp]
+	\centering
+	\subfloat[$k = 0.5$]{
+		{
+			\includegraphics[scale=0.7]{figures/local/niblack/local_nib_11_retina.png}
+		}
+		\label{fig:niblack_k_0_5_retina}
+	}
+	\subfloat[$k = 1.0$]{
+		{
+			\includegraphics[scale=0.7]{figures/local/niblack/local_nib_11_retina_1_0.png}
+		}
+		\label{fig:niblack_k_1_0_retina}
+	}\quad
+	\subfloat[$k = 5.0$]{
+		{
+			\includegraphics[scale=0.7]{figures/local/niblack/local_nib_11_retina_5_0.png}
+		}
+		\label{fig:niblack_k_5_0_retina}
+	}
+	\caption{Niblack with different $k$s on Retina image.}
+	\label{fig:niblack_k}
+\end{figure}
+\paragraph*{The Sauvola and Pietaksinen} methods vary with three parameters, its neighborhood area ($n$), the same border factor from Niblack ($k$), and the maximum standard deviation of the image ($r$).
+In our experiment, we varied the values of $n$ and $k$ but kept $r = 128$ since all images only varied from 0 to 255 shades of gray.
+\begin{figure}[htbp]
+	\centering
+	\subfloat[3x3]{
+		{
+			\includegraphics[scale=0.7]{figures/local/sauvola/local_sau_3_monarch.png}
+		}
+		\label{fig:sauvola_3_monarch}
+	}
+	\subfloat[7x7]{
+		{
+			\includegraphics[scale=0.7]{figures/local/sauvola/local_sau_7_monarch.png}
+		}
+		\label{fig:sauvola_7_monarch}
+	}\quad
+	\subfloat[11x11]{
+		{
+			\includegraphics[scale=0.7]{figures/local/sauvola/local_sau_11_monarch.png}
+		}
+		\label{fig:sauvola_11_monarch}
+	}
+	\caption{Sauvola with different $n$s on Monarch image.}
+	\label{fig:sauvola_n}
+\end{figure}
+Figure~\ref{fig:sauvola_n} shows the segmentation while varying $n$, in which the best result obtained was using $n = 11$.
+In Figure~\ref{fig:sauvola_k} we varied $k$ values, and although the recommended value for $k$ is of 0.5, the best segmentation was obtained with $k = 1.0$, seen in Figure~\ref{fig:sauvola_k_1.0_monarch}.
+\begin{figure}[htbp]
+	\centering
+	\subfloat[$k = 0.5$]{
+		{
+			\includegraphics[scale=0.7]{figures/local/sauvola/local_sau_11_monarch.png}
+		}
+		\label{fig:sauvola_k_0.5_monarch}
+	}
+	\subfloat[$k = 1.0$]{
+		{
+			\includegraphics[scale=0.7]{figures/local/sauvola/local_sau_11_monarch_1_0.png}
+		}
+		\label{fig:sauvola_k_1.0_monarch}
+	}\quad
+	\subfloat[$k = 5.0$]{
+		{
+			\includegraphics[scale=0.7]{figures/local/sauvola/local_sau_11_monarch_5_0.png}
+		}
+		\label{fig:sauvola_k_5.0_monarch}
+	}
+	\caption{Sauvola with different $k$s on Monarch image.}
+	\label{fig:sauvola_k}
+\end{figure}
+\paragraph*{The Phansalskar, More and Sabale} method has four parameters, the neighborhood area ($n$), $k$ inherited from the previous methods, and $r$ with a different meaning, and added two new parameters: $p$ and $q$.
+We faced an error with this method in which the images were only outputting as white images, we tried to normalize the input pixels between 0 and 1, but it did not fix the error in Figure~\ref{fig:phansalskar_n}, which shows our results with varying $n$ and freezing the other parameters to their recommended value: $k = 0.25$, $r = 0.5$, $p = 2$, and $q = 10$.
+\begin{figure}[htbp]
+	\centering
+	\subfloat[3x3]{
+		{
+			\includegraphics[scale=0.7]{figures/local/phansalskar/local_pha_3_sonnet.png}
+		}
+		\label{fig:phansalskar_3}
+	}
+	\subfloat[7x7]{
+		{
+			\includegraphics[scale=0.7]{figures/local/phansalskar/local_pha_7_sonnet.png}
+		}
+		\label{fig:phansalskar_7}
+	}\quad
+	\subfloat[11x11]{
+		{
+			\includegraphics[scale=0.7]{figures/local/phansalskar/local_pha_11_sonnet.png}
+		}
+		\label{fig:phansalskar_11}
+	}
+	\caption{Phansalskar with different $k$s on Sonnet image.}
+	\label{fig:phansalskar_n}
+\end{figure}
+\paragraph*{Contrast} This method varies only by the size of the neighborhood $n$ area.
+The majority of the contrast results did not produce distinguishable images, as in Figure~\ref{fig:contrast_bad_peppers} with no clear features of the objects.
+In one instance this method produced a better result on image Sonnet, seen in Figure~\ref{fig:contrast_sonnet}, but still only for small neighborhood areas.
+\begin{figure}[htbp]
+	\centering
+	\subfloat[3x3]{
+		{
+			\includegraphics[scale=0.7]{figures/local/contrast/local_con_3_peppers.png}
+		}
+		\label{fig:contrast_bad_3_peppers}
+	}
+	\subfloat[7x7]{
+		{
+			\includegraphics[scale=0.7]{figures/local/contrast/local_con_7_peppers.png}
+		}
+		\label{fig:contrast_bad_7_peppers}
+	}\quad
+	\subfloat[11x11]{
+		{
+			\includegraphics[scale=0.7]{figures/local/contrast/local_con_11_peppers.png}
+		}
+		\label{fig:contrast_bad_11_peppers}
+	}
+	\caption{Bad contrast with different neighbourhoods $n$ on Peppers image.}
+	\label{fig:contrast_bad_peppers}
+\end{figure}
+\begin{figure}[htbp]
+	\centering
+	\subfloat[3x3]{
+		{
+			\includegraphics[scale=0.7]{figures/local/contrast/local_con_3_sonnet.png}
+		}
+		\label{fig:contrast_3_sonnet}
+	}
+	\subfloat[7x7]{
+		{
+			\includegraphics[scale=0.7]{figures/local/contrast/local_con_7_sonnet.png}
+		}
+		\label{fig:contrast_7_sonnet}
+	}\quad
+	\subfloat[11x11]{
+		{
+			\includegraphics[scale=0.7]{figures/local/contrast/local_con_11_sonnet.png}
+		}
+		\label{fig:contrast_11_sonnet}
+	}
+	\caption{Contrast with different neighbourhoods $n$ on Sonnet image.}
+	\label{fig:contrast_sonnet}
+\end{figure}
+\paragraph*{Mean} This method varies only by the size of the neighborhood $n$ area.
+In Figure~\ref{fig:mean_baboon} it is possible to notice some features of the baboon throughout the different $n$ values, with the smaller windows producing the worst result.
+Another interesting fact to notice is the noise generated at the borders of the image, it is caused by the padding done via adding $0$s to the image and influencing in the mean calculation.
+\begin{figure}[htbp]
+	\centering
+	\subfloat[3x3]{
+		{
+			\includegraphics[scale=0.7]{figures/local/mean/local_mea_3_baboon.png}
+		}
+		\label{fig:mean_3_baboon}
+	}
+	\subfloat[7x7]{
+		{
+			\includegraphics[scale=0.7]{figures/local/mean/local_mea_7_baboon.png}
+		}
+		\label{fig:mean_7_baboon}
+	}\quad
+	\subfloat[11x11]{
+		{
+			\includegraphics[scale=0.7]{figures/local/mean/local_mea_7_baboon.png}
+		}
+		\label{fig:mean_11_baboon}
+	}
+	\caption{Mean with different neighbourhoods $n$ on Baboon image.}
+	\label{fig:mean_baboon}
+\end{figure}
+\paragraph*{Median} This method varies only by the size of the neighborhood $n$ area.
+Figure~\ref{fig:median_monarch} shows the benefits of a larger area, with more distinguishable features, but still an overall cluttered image.
+\begin{figure}[htbp]
+	\centering
+	\subfloat[3x3]{
+		{
+			\includegraphics[scale=0.7]{figures/local/median/local_med_3_monarch.png}
+		}
+		\label{fig:median_3_monarch}
+	}
+	\subfloat[7x7]{
+		{
+			\includegraphics[scale=0.7]{figures/local/median/local_med_7_monarch.png}
+		}
+		\label{fig:median_7_monarch}
+	}\quad
+	\subfloat[11x11]{
+		{
+			\includegraphics[scale=0.7]{figures/local/median/local_med_11_monarch.png}
+		}
+		\label{fig:median_11_monarch}
+	}
+	\caption{Median with different neighbourhoods $n$ on Monarch image.}
+	\label{fig:median_monarch}
+\end{figure}
+\subsection{Histograms}
+\label{sec:hist}
+We generated the histograms in Figure~\ref{fig:hist} for each of method reported above on image Monarch, with $n = 3$ and $k = 0.5$.
+\section{Conclusion}
+\label{sec:conclusion}
+In this work, we explored and compared some aspects of global and local thresholding.
+We went through some well known local methods: (i) Bernsen, (ii) Niblack, (iii) Sauvola, (iv) Phansalskar, (v) Contrast, (vi) Mean, and (vii) Median; and compared some variations of their parameters.
+Overall the local thresholds were better than the global ones, but they all required some grid search for each application, for instance, the Phansalskar was proposed to be used in biological cells segmentation, and so their recommended parameters are specifically for that use case.
+Regarding computing time both approaches were fast to execute on a CPU, although, global was faster the difference was minimal.
+Some few details could be explored in future works such as an extensive grid search for the parameters, and the use of wrap-around padding to avoid dark borders.
+\begin{figure*}[htbp]
+	\centering
+	\subfloat[Bernsen]{
+		{
+			\includegraphics[scale=0.35]{figures/hist/local_hist_ber_3_monarch.png}
+		}
+		\label{fig:hist_ber}
+	}
+	\subfloat[Niblack]{
+		{
+			\includegraphics[scale=0.35]{figures/hist/local_hist_nib_3_monarch.png}
+		}
+		\label{fig:hist_nib}
+	}\quad
+	\subfloat[Sauvola]{
+		{
+			\includegraphics[scale=0.35]{figures/hist/local_hist_sau_3_monarch.png}
+		}
+		\label{fig:hist_sau}
+	}
+	\subfloat[Phansalskar]{
+		{
+			\includegraphics[scale=0.35]{figures/hist/local_hist_pha_3_monarch.png}
+		}
+		\label{fig:hist_sau}
+	}\quad
+	\subfloat[Contrast]{
+		{
+			\includegraphics[scale=0.35]{figures/hist/local_hist_con_3_monarch.png}
+		}
+		\label{fig:hist_con}
+	}
+	\subfloat[Mean]{
+		{
+			\includegraphics[scale=0.35]{figures/hist/local_hist_mea_3_monarch.png}
+		}
+		\label{fig:hist_mea}
+	}\quad
+	\subfloat[Median]{
+		{
+			\includegraphics[scale=0.35]{figures/hist/local_hist_med_3_monarch.png}
+		}
+		\label{fig:hist_med}
+	}
+	\caption{Histogram for $n = 3$ on all images.}
+	\label{fig:hist}
+\end{figure*}
 \end{document}

### 2019-10-07 old.tex
T2

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{subfig}
\usepackage{float}

\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

\title{MO443 - Assignment II}

\author{210404 -- Guilherme Vieira Leite}

\maketitle

\section{Introduction}
Dithering, or half-tone, is widely used to reduce the amount of data that travels through a medium, as in television signal being transmitted through airwaves to newspaper printing in only black and white. In this work, we explore the implementation of some dithering variants with error diffusion and their effects on the input image.\par
This work is structured as such: Section~\ref{sec:method} explains our method, and which aspects of dithering we will explore in the following section, and our input images. Our results are presented in Section~\ref{sec:results}, in which we compare the methods against each other and discuss their results. Section~\ref{sec:conclusion} concludes this work with some consideration regarding our findings, and a future work direction to follow. Finally Section~\ref{sec:appendix1} acts as an Appendix to our matrices that were better stored separately from the main body.
\section{Dithering Methods}
\label{sec:method}
The implemented dithering methods in this work differentiates between each other by a couple of factors: (i) whether they are grayscaled or colored, and (ii) the error diffusion matrix.
\paragraph{Color space} Dithering in the grayscale color space is performed as in the algorithm discussed in class, in a few words: the pixel is binarized, its error is calculated and multiplied by the mask value relative to that pixel. To transfer this process to the RGB color space, we treated each of its three bands as if they were separate grayscale images, that were later combined to create a dithered colored image.
\paragraph{Filter matrix} Each pixel is dithered by an error metric to its neighborhood, this neighborhood is defined by the filter matrix, how large it is and which pixels are considered in the metric. In this work, we tested on six pre-defined error diffusion matrices: Floyd and Steinberg, Stevenson and Arce, Burkes, Sierra, Stucki, and Jarvis, Judice, and Ninke, seen in Section~\ref{sec:appendix1}.
\section{Experiments}
Throughout our experiments, we aimed to explore the effects of dithering, while varying the color space, the error diffusion matrix and the order in which the error was diffused. We also exchanged the output's quality by lower processing time, shrinking all input images to around 128x128, but the algorithm is still able to process larger images.\par
We performed dithering on nine images, some provided by the professor and some particularly obtained. The images were chosen to exhaust the algorithm and explore their weaknesses and strengths, especially the colored dithering. Figure~\ref{fig:input} presents a few samples of the chosen images.
\begin{figure}[htbp]
\centering
\subfloat{
	{
		\includegraphics[scale=0.35]{figures/input/baboon}
	}
	\label{fig:baboon}
}
\subfloat{
	{
		\includegraphics[scale=0.35]{figures/input/fiducial}
	}
	\label{fig:bee}
}
\quad
\subfloat{
	{
		\includegraphics[scale=0.35]{figures/input/monarch}
	}
	\label{fig:juquinha}
}
\subfloat{
	{
		\includegraphics[scale=0.35]{figures/input/peppers}
	}
	\label{fig:peppers}
}
\quad
\subfloat{
	{
		\includegraphics[scale=0.35]{figures/input/retina}
	}
	\label{fig:sky}
}
\subfloat{
	{
		\includegraphics[scale=0.35]{figures/input/sonnet}
	}
	\label{fig:tattoo}
}
\caption{A sample of the images used in the experiments.}
\label{fig:input}
\end{figure}\par

\begin{figure}[htbp]
\centering
\subfloat{
	{
		\includegraphics[scale=0.7]{figures/global/global_128_baboon.png}
	}
	\label{fig:baboon}
}
\subfloat{
	{
		\includegraphics[scale=0.7]{figures/global/global_128_fiducial.png}
	}
	\label{fig:bee}
}
\quad
\subfloat{
	{
		\includegraphics[scale=0.7]{figures/global/global_128_monarch.png}
	}
	\label{fig:juquinha}
}
\subfloat{
	{
		\includegraphics[scale=0.7]{figures/global/global_128_peppers.png}
	}
	\label{fig:peppers}
}
\quad
\subfloat{
	{
		\includegraphics[scale=0.7]{figures/global/global_128_retina.png}
	}
	\label{fig:sky}
}
\subfloat{
	{
		\includegraphics[scale=0.7]{figures/global/global_128_sonnet.png}
	}
	\label{fig:tattoo}
}
\caption{A sample of the images used in the experiments.}
\label{fig:input}
\end{figure}\par

We also experimented with three traversal methods, looping through the image from (i) left to right, top to bottom, (ii) right to left, bottom to top, and (iii) top to bottom, but every even row was looped left to right and every odd row was looped from right to left, seen in Figure~\ref{fig:traversal}. To traverse the images in these varying methods a few precautions had to be taken since the chosen filters generate a particular effect, in which any pixel already dithered will be ignored to future error diffusion. We need to accommodate this effect on any traversal that differs from left to right, top to bottom, and we did so by tweaking with the filter's matrix to match the expected result, one example on Floyd and Steinberg can be seen in Table~\ref{tab:flo_inverse}.
\begin{figure}[htbp]
	\centering
	\subfloat{
		{
			\includegraphics[scale=0.5]{figures/l2r}
		}
		\label{fig:l2r}
	}
	\quad
	\subfloat{
		{
			\includegraphics[scale=0.5]{figures/r2l}
		}
		\label{fig:r2l}
	}
	\quad
	\subfloat{
		{
			\includegraphics[scale=0.5]{figures/zz}
		}
		\label{fig:zz}
	}
	\caption{Traversal directions experimented on.}
	\label{fig:traversal}
\end{figure}
\begin{table}[!h]
\centering
\renewcommand{\arraystretch}{1.5}
\begin{tabular}{c|c|c}
1/16 & 5/16             & 3/16 \\ \hline
7/16 & \textit{f(x, y)} &     
\end{tabular}
\caption{Floyd and Steinberg's diffusion error matrix when traversing from right to left, bottom to right.}
\label{tab:flo_inverse}
\end{table}
\section{Results}
\label{sec:results}
In this section, we present and discuss the results obtained from the methods discussed in Section~\ref{sec:method}. To better explore the different aspects of a dithering process we focus our discussion on three subsections bellow.
\subsection{Color space}
In this experiment, we performed a colored dithering and a grayscaled one. Although we are not exploring the effects of error diffusion and traversal direction, we also used Floyd and Steinberg's error diffusion and traversed the image from left to right, top to bottom. Figure~\ref{fig:baboon_colorspace} shows the resulting dithering, in it we can observe that overall features of the image are kept, it is still possible to identify the baboon in Figure~\ref{fig:baboon_color}, as it is the intention of dithering. But on a closer inspection it is also possible to notice a drop in quality of both images, also an expected effect, for instance, the lower lip of the baboon has been filled with noise and mixes with the fur, another side effect of dithering is the loss of small details, as seen in Figure~\ref{fig:sky_color} the skylines at the distance are almost indiscernible.
\begin{figure}[htbp]
	\centering
	\subfloat[Color baboon]{
		{
			\includegraphics[scale=0.7]{figures/left2right/flo_color_baboon}
		}
		\label{fig:baboon_color}
	}
	\subfloat[Gray baboon]{
		{
			\includegraphics[scale=0.7]{figures/left2right/flo_gray_baboon}
		}
		\label{fig:baboon_gray}
	}
	\quad
	\subfloat[Color sky]{
		{
			\includegraphics[scale=0.7]{figures/left2right/flo_color_sky}
		}
		\label{fig:sky_color}
	}
	\subfloat[Gray sky]{
		{
			\includegraphics[scale=0.7]{figures/left2right/flo_gray_sky}
		}
		\label{fig:sky_gray}
	}
	\caption{Color and Grayscale dithering.}
	\label{fig:baboon_colorspace}
\end{figure}
\subsection{Dithering matrices}
\label{ssec:matrix}
In this experiment, we investigated the effects of a pixel's neighborhood in dithering. We generated the same dithered image for each of the six masks presented in Section~\ref{sec:method}, both in color and grayscale, Figures~\ref{fig:color_error_diffusion} and~\ref{fig:gray_error_diffusion}, and as in the previous experiment, we fixed the traverse direction from left to right, top to bottom.
\begin{figure}[htbp]
	\centering
	\subfloat[Floyd \& Steinnberg]{
		{
			\includegraphics[scale=0.7]{figures/left2right/flo_color_tattoo}
		}
		\label{fig:flo_color_tattoo}
	}
	\subfloat[Stevenson \& Arce]{
		{
			\includegraphics[scale=0.7]{figures/left2right/ste_color_tattoo}
		}
		\label{fig:ste_color_tattoo}
	}
    \quad
	\subfloat[Burkes]{
		{
			\includegraphics[scale=0.7]{figures/left2right/bur_color_tattoo}
		}
		\label{fig:bur_color_tattoo}
	}
	\subfloat[Sierra]{
		{
			\includegraphics[scale=0.7]{figures/left2right/sie_color_tattoo}
		}
		\label{fig:sie_color_tattoo}
	}\quad
	\subfloat[Stucki]{
		{
			\includegraphics[scale=0.7]{figures/left2right/stu_color_tattoo}
		}
		\label{fig:stu_color_tattoo}
	}
	\subfloat[Jarvis, Judice, \& Ninke]{
		{
			\includegraphics[scale=0.7]{figures/left2right/jar_color_tattoo}
		}
		\label{fig:jar_color_tattoo}
	}
	\caption{Color error diffusion on Tattoo.}
	\label{fig:color_error_diffusion}
\end{figure}\par
The results with colored images are shown in Figure~\ref{fig:color_error_diffusion}, and it is possible to notice that the biggest difference resides between Fig~\ref{fig:ste_color_tattoo} and the rest. In Stevenson and Arce's method, a lot of the noise was increased, creating thicker borders but also disrupting the color of the skin with pink and green pixels. It is also interesting to notice that the methods of Sierra Fig.~\ref{fig:sie_color_tattoo}, Stucki Fig.~\ref{fig:stu_color_tattoo}, and Jarvis et al. Fig.~\ref{fig:jar_color_tattoo} improved the borders of the original image, Figure~\ref{fig:tattoo}, especially in the bee black and yellow stripes which were blurred.
\begin{figure}[htbp]
	\centering
	\subfloat[Floyd \& Steinnberg]{
		{
			\includegraphics[scale=0.7]{figures/left2right/flo_gray_tattoo}
		}
		\label{fig:flo_gray_tattoo}
	}
	\subfloat[Stevenson \& Arce]{
		{
			\includegraphics[scale=0.7]{figures/left2right/ste_gray_tattoo}
		}
		\label{fig:ste_cgray_tattoo}
	}
    \quad
	\subfloat[Burkes]{
		{
			\includegraphics[scale=0.7]{figures/left2right/bur_gray_tattoo}
		}
		\label{fig:bur_gray_tattoo}
	}
	\subfloat[Sierra]{
		{
			\includegraphics[scale=0.7]{figures/left2right/sie_gray_tattoo}
		}
		\label{fig:sie_gray_tattoo}
	}
	\quad
	\subfloat[Stucki]{
		{
			\includegraphics[scale=0.7]{figures/left2right/stu_gray_tattoo}
		}
		\label{fig:stu_gray_tattoo}
	}
	\subfloat[Jarvis, Judice, \& Ninke]{
		{
			\includegraphics[scale=0.7]{figures/left2right/jar_gray_tattoo}
		}
		\label{fig:jar_gray_tattoo}
	}
	\caption{Grayscale error diffusion on Tattoo.}
	\label{fig:gray_error_diffusion}
\end{figure}\par
There are not many differences between the color and grayscale masks applications, but in Figure~\ref{fig:gray_error_diffusion} it is even easier to spot the noise effect caused by Stevenson and Arce's mask. Most of the bee's wings also vanished in the background, but that is a side effect of the grayscale transform process and not the application of the masks.
\subsection{Traversal directions}
In this experiment we test three traversal directions and discuss their effect on the output image, the experiment was performed on Figure~\ref{fig:bee}, using Floyd and Steinberg's mask, its colored result is shown in Figure~\ref{fig:color_traversal} and the grayscaled output in Figure~\ref{fig:gray_traversal}.
\begin{figure}[htbp]
	\centering
	\subfloat[Left to right]{
		{
			\includegraphics[scale=0.8]{figures/left2right/flo_color_bee}
		}
		\label{fig:l2r_flo_color_bee}
	}
	\quad
	\subfloat[Right to left]{
		{
			\includegraphics[scale=0.8]{figures/right2left/flo_color_bee}
		}
		\label{fig:r2l_flo_color_bee}
	}
	\subfloat[Zig zag]{
		{
			\includegraphics[scale=0.8]{figures/zigzag/flo_color_bee}
		}
		\label{fig:zz_flo_color_bee}
	}
	\caption{Color traversal direction on Girl.}
	\label{fig:color_traversal}
\end{figure}
In Figure~\ref{fig:l2r_flo_color_bee} we traversed the image from left to right, top to bottom, and in Figure~\ref{fig:r2l_flo_color_bee} from right to left, bottom to top. These outputs differ from one another on subtle ways, for example the girl's lips in Figure~\ref{fig:l2r_flo_color_bee} looks serious, as in the original Figure~\ref{fig:bee}, but in Figure~\ref{fig:r2l_flo_color_bee} they were extended and form a subtle smile, other than this detail we can notice a few differences in the white background at the top where it forms a wavy pattern in Figure~\ref{fig:l2r_flo_color_bee} and diagonal patterns in Figure~\ref{fig:r2l_flo_color_bee}. The third approach or the zig zag traversal, show in Figure~\ref{fig:zz_flo_color_bee}, disrupted the image by introducing a great amount of noise, and similarly to Figure~\ref{fig:l2r_flo_color_bee} a wavy pattern at the top.
\begin{figure}[htbp]
	\centering
	\subfloat[Left to right]{
		{
			\includegraphics[scale=0.8]{figures/left2right/flo_gray_bee}
		}
		\label{fig:l2r_flo_gray_bee}
	}
	\quad
	\subfloat[Right to left]{
		{
			\includegraphics[scale=0.8]{figures/right2left/flo_gray_bee}
		}
		\label{fig:r2l_flo_gray_bee}
	}
	\subfloat[Zig zag]{
		{
			\includegraphics[scale=0.8]{figures/zigzag/flo_gray_bee}
		}
		\label{fig:zz_flo_gray_bee}
	}
	\caption{Grayscale traversal direction on Girl.}
	\label{fig:gray_traversal}
\end{figure}
The grayscale images shown in Figure~\ref{fig:gray_traversal} illustrates similar problems as the ones from Section~\ref{ssec:matrix}, the images gets more blurry due to color loss and the noise seen in Figure~\ref{fig:zz_flo_color_bee} is also seen in Figure~\ref{fig:zz_flo_gray_bee}.
\subsection{Error function}
In this section we want to discuss an experiment that we performed \textit{accidentally} by committing a mistake in the error function calculation. Upon performing the error calculation we overflowed its maximum value, which turned roughly every other pixel into a black one. The output can be seen in Figure~\ref{fig:error}, it is similar to the desired result, except a lot darker due to the abundance of black pixels.
\begin{figure}[htbp]
	\centering
	\subfloat[Desired]{
		{
			\includegraphics[scale=0.8]{figures/left2right/flo_color_juquinha}
		}
		\label{fig:juquinha2}
	}
	\subfloat[Error]{
		{
			\includegraphics[scale=0.2]{figures/error}
		}
		\label{fig:error1}
	}
	\caption{Mistake in error function generated a darker image.}
	\label{fig:error}
\end{figure}
\section{Conclusions}
This work proposed to explore a few aspects of dithering with error diffusion, we went through the differences regarding the color space, the neighborhood relevance, and the direction to loop the input. Overall only a few masks produced an inferior result than expected, and in our experiments, the \textit{zig zag} traversal performed as worst among its alternatives. As future work, the exploration of a diagonal traversal should be considered.
\pagebreak
\section{Appendix I}
\label{sec:appendix1}

\begin{table}[!h]
\centering
\renewcommand{\arraystretch}{1.5}
\begin{tabular}{c|c|c}
     & \textit{f(x, y)} & 7/16 \\ \hline
3/16 & 5/16             & 1/16
\end{tabular}
\caption{Floyd and Steinberg's diffusion error matrix.}
\label{tab:flo}
\end{table}

\begin{table}[!h]
\centering
\renewcommand{\arraystretch}{1.5}
\begin{tabular}{c|c|c|c|c|c|c}
 & \textit{} &  & \textit{f(x, y)} &  & 32/200 &  \\ \hline
12/200 &  & 26/200 &  & 30/200 &  & 16/200 \\ \hline
 & 12/200 &  & 26/200 &  & 12/200 &  \\ \hline
5/200 &  & 12/200 &  & 12/200 &  & 5/200
\end{tabular}
\caption{Stevenson and Arce's diffusion error matrix.}
\label{tab:ste}
\end{table}

\begin{table}[!h]
\centering
\renewcommand{\arraystretch}{1.5}
\begin{tabular}{c|c|c|c|c}
 &  & \textit{f(x, y)} & 8/32 & 4/32 \\ \hline
2/32 & 4/32 & 8/32 & 4/32 & 2/32
\end{tabular}
\caption{Burkes' diffusion error matrix.}
\label{tab:bur}
\end{table}

\begin{table}[!h]
\centering
\renewcommand{\arraystretch}{1.5}
\begin{tabular}{c|c|c|c|c}
 &  & \textit{f(x, y)} & 5/32 & 3/32 \\ \hline
2/32 & 4/32 & 5/32 & 4/32 & 2/32 \\ \hline
 & 2/32 & 3/32 & 2/32 & 
\end{tabular}
\caption{Sierra's diffusion error matrix.}
\label{tab:sie}
\end{table}

\begin{table}[!h]
\centering
\renewcommand{\arraystretch}{1.5}
\begin{tabular}{l|l|l|l|l}
 &  & \textit{f(x, y)} & 8/42 & 4/42 \\ \hline
2/42 & 4/42 & 8/42 & 4/42 & 2/42 \\ \hline
1/42 & 2/42 & 4/42 & 2/42 & 1/42
\end{tabular}
\caption{Stucki's diffusion error matrix.}
\label{tab:stu}
\end{table}

\begin{table}[!h]
\centering
\renewcommand{\arraystretch}{1.5}
\begin{tabular}{l|l|l|l|l}
 &  & \textit{f(x, y)} & 7/48 & 5/48 \\ \hline
3/48 & 5/48 & 7/48 & 5/48 & 3/48 \\ \hline
1/48 & 3/48 & 5/48 & 3/48 & 1/48
\end{tabular}
\caption{Jarvis, Judice, and Ninke's diffusion error matrix.}
\label{tab:jar}
\end{table}

\end{document}

### 2019-10-07 2019_ICMLA/paper.tex
ICMLA 2019 looking like Helio's, but still missing his tweaks

--- 2019-09-12 paper.tex
@@
 \documentclass[conference]{IEEEtran}
-
 \IEEEoverridecommandlockouts
@@
 \usepackage{textcomp}
-\usepackage{booktabs}
-\usepackage{flushend}
 \usepackage{xcolor}
@@
     T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
-
 \begin{document}
 
-\sloppy
-\tolerance = 999
+\title{Fall Detection in Video Sequences\\ Based on a Three-Stream Convolutional\\ Neural Network}
 
-\title{Fall Detection in Video Sequences \\ Based on a Three-Stream Convolutional \\ Neural Network}
-
-\author{\vspace*{0.0cm}}
-
-%\author{\IEEEauthorblockN{1\textsuperscript{st} Guilherme Vieira Leite}
-%\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
-%\textit{name of organization (of Aff.)}\\
-%City, Country \\
-%email address}
-%\and
-%\IEEEauthorblockN{2\textsuperscript{nd} Gabriel Pellegrino da Silva}
-%\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
-%\textit{name of organization (of Aff.)}\\
-%City, Country \\
-%email address}
-%\and
-%\IEEEauthorblockN{2\textsuperscript{nd} Helio Pedrini}
-%\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
-%\textit{name of organization (of Aff.)}\\
-%City, Country \\
-%email address}
-%}
+% \author{\IEEEauthorblockN{1\textsuperscript{st} Given Name Surname}
+% \IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
+% \textit{name of organization (of Aff.)}\\
+% City, Country \\
+% email address}}
 
@@
 \section{Introduction}
-
 With deteriorating health in advanced ages, even a minor fall can trigger a chain reaction of serious psychological and physical injuries to the elder population.
-Hence, the motivation for ambient assistant living solutions to both avoids falling from occurring and reducing the interval between a fall and help arrival.
-
+Hence, the motivation for ambient assistant living solutions to both avoids falling from occurring and reducing the interval between a fall and help arrival.\par
 The studies that detect falls as soon as they happen can be split into two main categories: hardware reliant solutions and vision based ones.
 The first one, which uses devices such as accelerometers and IMUs, has a satisfactory performance but are met with frustration from the subjects, mainly towards forgetting to use the device.
-Vision-based solutions, which allied to machine learning techniques, have shown promising results and, furthermore, do not rely on the subject wearing it.
-
+Vision-based solutions, which allied to machine learning techniques, have shown promising results and, furthermore, do not rely on the subject wearing it.\par
 Throughout the fall detection literature, techniques vary from threshold activation based, such as Sase et al.~\cite{sase2018human} detecting regions of interest after background subtraction, and a threshold activation function if the region of interest was under a third of the subject height in the frame.
@@
 Regarding the subject's privacy, both Edgcomb et al.~\cite{edgcomb2012automated} and Lin et al.~\cite{lin2013fall} investigated privacy-prone features, such as blurring, silhouetting, and covering the body with shapes.
-Lu et al.~\cite{lu2019deep} employed a 3D convolutional neural network (CNN) followed by a long short-term memory (LSTM).
+Lu et al.~\cite{lu2018deep} employed a 3D convolutional neural network (CNN) followed by a long short-term memory (LSTM).
 Huang et al.~\cite{huang2018video} extracted the human pose with OpenPose and classified it with a VGG-16 architecture.
-N\'u\~nez-Marcos et al.~\cite{nunez2017vision} extracted the dense optical flow (OF) and also served it to a VGG-16.
+Núñez-Marcos et al.~\cite{nunez2017vision} extracted the dense optical flow (OF) and also served it to a VGG-16.
 Anishchenko et al.~\cite{anishchenko2018machine} employed a modified AlexNet as a classifier.
@@
 Particle filtering by Yu et al.~\cite{yu2009fall}, Gaussian models by Yu et al.~\cite{yu2010robust} and Rougier et al.~\cite{rougier2011robust}.
-Furthermore, Xu et al.~\cite{xu2018new} produced a survey on fall detections systems.
-
+Furthermore, Xu et al.~\cite{xu2018new} produced a survey on fall detections systems.\par
 The main contribution of this work is the development and evaluation of handcrafted features in a multi-stream learning model.
 We compare the effectiveness of three features extracted from videos frames: (i) optical flow, (ii) saliency map, and (iii) RGB data.
-These features are fed to a three-stream VGG-16 architecture, and their results compared with the literature.
-
+These features are fed to a three-stream VGG-16 architecture, and their results compared with the literature.\par
 We organized this paper as follows.
@@
 
-Optical flow is a handcrafted feature that conveys movement information between two frames of a video, either by object or camera movement.
-Its ability to describe movement enables this feature to support the temporal aspect of a fall event in a deep network.
-
-\begin{figure*}[!htb]
-\centerline{\includegraphics[width=0.55\linewidth]{figures/overview.png}}
+\begin{figure*}[htbp]
+\centerline{\includegraphics[width=0.57\linewidth]{figures/overview.png}}
 \caption{Main components of the proposed fall detection method.}
@@
 \end{figure*}
-
+Optical flow is a handcrafted feature that conveys movement information between two frames of a video, either by object or camera movement.
+Its ability to describe movement enables this feature to support the temporal aspect of a fall event in a deep network.\par
 The extraction process considers a video frame as $I$ and $I(x, y, t)$ a pixel in this frame.
@@
 \end{equation}
-
-Equation~\ref{eq:of} is formed after applying a Taylor series approximation of right-hand side and dividing by $dt$, $f_t$ is the gradient given time, $f_x$, $f_y$, $u$, and $v$ are given in Equation~\ref{eq:of-grad}.
-Values of $u$ and $v$ can be achieved by different methods, such as the classical Lucas-Kanade~\cite{jain2018abnormal} or the one used in this work: Gunnar-Farneb{\"a}ck~\cite{lowhur2015dense}.
+Equation~\ref{eq:of} is formed after applying a Taylor series approximation of right-hand side and dividing by $dt$, $f_t$ is the gradient given time, $f_x$ , $f_y$ , $u$, and $v$ are given in Equation~\ref{eq:of-grad}.
+Values of $u$ and $v$ can be achieved by different methods, such as the classical Lucas-Kanade~\cite{jain2018abnormal} or the one used in this work: Gunnar-Farnebäck~\cite{lowhur2015dense}.
 \begin{equation}
@@
 Its extraction can occur in many ways, one of those being the practice of feeding an image $I$ and its class label $c$ to the network, then, freezing the weights on the network and compute the gradients of $c$ to the pixels of $I$.
-Consider $S_c(I)$ to be the class score function for an image $I$ and, for this simple explanation, that it is a simple linear function, $S_c(I) = w_c^{T} + b_c$.
-With $w$ being the weights of the network and $b$ the bias, it is possible to notice that the magnitude of elements of $w$ affects the importance of the corresponding pixels in $I$ with class $c$.
-
+Consider $S_c(I)$ to be the class score function for an image $I$ and, for this simple explanation, that it is a simple linear function, $S_c(I) = w_c^T + b_c$.
+With $w$ being the weights of the network and $b$ the bias, it is possible to notice that the magnitude of elements of $w$ affects the importance of the corresponding pixels in $I$ with class $c$.\par
 The choice of saliency map as a stream is due to its spatial relation to the frame, as the raw RGB frames are prone to environmental interference, and its performance in the works developed by Zuo et al.~\cite{zuo2019enhanced} and Meng et al.~\cite{Meng2018interpretable}.
@@
 The selected datasets, further detailed in Section~\ref{sec:experiments}, possess relatively few human fall samples in their videos, which would limit the CNNs learning capabilities to detect fall events.
-Hence, the importance of transfer learning.
-
+Hence, the importance of transfer learning.\par
 The first 14 layers of the VGG-16 architecture were trained on the ImageNet~\cite{imagenet_cvpr09} dataset and, later on, these same layers were fine-tuned over the UCF101~\cite{soomro2012ucf101} dataset.
 The reasoning being that the network would initially learn low-level features from the ImageNet classes, and focus these features on human activities with the UCF101 videos, Figure~\ref{fig:pre14}.
-N\'u\~nez-Marcos et al.~\cite{nunez2017vision} executed this step and released their weight files publicly.
-
-\begin{figure}[!htb]
-\centerline{\includegraphics[width=0.96\linewidth]{figures/pre14.png}}
-\caption{Deep layers being trained on ImageNet and UCF101 datasets.}
+Núñez-Marcos et al.~\cite{nunez2017vision} executed this step and released their weight files publicly.\par
+\begin{figure}[htbp]
+\centerline{\includegraphics[width=0.9\linewidth]{figures/pre14.png}}
+\caption{Deep layers being trained on ImagetNet and UCF101.}
 \label{fig:pre14}
 \end{figure}
-
-We froze the 14 initial layer's weights and fine-tuned the last two fully connected layers were fine-tuned, with dropout regularization.
-Each stream executed this last fine-tuning step, totaling three executions (Figure~\ref{fig:pos14}).
-
-\begin{figure}[!htb]
-\centerline{\includegraphics[width=0.43\linewidth]{figures/pos14.png}}
-\caption{Fully connected layer training.}
+We froze the 14 initial layer's weights and fine-tuned the
+last two fully connected layers were fine-tuned, with dropout
+regularization. Each stream executed this last fine-tuning step,
+totaling three executions (Figure~\ref{fig:pos14}).
+\begin{figure}[htbp]
+\centerline{\includegraphics[width=0.4\linewidth]{figures/pos14.png}}
+\caption{Fully connected layers training.}
 \label{fig:pos14}
@@
 Furthermore, given the neural networks capability of learning relevant features to describe their input, the RGB frame itself was fed to the third stream.
-
-\paragraph{Optical Flow} represents the temporal relation between frames and to fully gather this property it was used as a stack of optical flows on top of a sliding window of frames, as suggested by N\'u\~nez-Marcos et al.~\cite{nunez2017vision}.
+\paragraph{Optical Flow} represents the temporal relation between frames and to fully gather this property it was used as a stack of optical flows on top of a sliding window of frames, as suggested by Núñez-Marcos et al.~\cite{nunez2017vision}.
 The sliding window has a size of $L$ frames and gathers 2$L$ components ($L$ horizontal ($d_t^x$) + $L$ vertical ($d_t^y$) optical flow component vector fields) creating a stack $O$ = \{$d_t^x$, $d_t^y$, $d_{t+1}^x$, $d_{t+1}^y$, ..., $d_{t+L}^x$, $d_{t+L}^y$ \}.
@@
 Figure~\ref{fig:of} shows an extracted example.
-
-\begin{figure}[!htb]
+\begin{figure}[htbp]
 \centerline{\includegraphics[width=\linewidth]{figures/of.png}}
@@
 \end{figure}
-
 \paragraph{Saliency Map} is composed of pixels varying from 0 to 1, and was fed as a gray-scale image to the network. Figure~\ref{fig:sal} shows and extracted example.
-
-\begin{figure}[!htb]
+\begin{figure}[htbp]
 \centerline{\includegraphics[width=\linewidth]{figures/sal.png}}
@@
 
-Our experiments were performed on two publicly available datasets: URFD~\cite{kwolek2014human} and FDD~\cite{charfi2013optimised}.
-
+Our experiments were performed on two publicly available
+datasets: URFD~\cite{kepski2014human} and FDD~\cite{charfi2013optimised}.\par
 The URFD dataset contains 70 videos: (i) 30 videos of falls; and (ii) 40 videos of daily living activities, recorded from a top-down and front view perspective by two Microsoft Kinect cameras.
-Each frame is labeled in three categories: if the person is lying on the ground, not lying on the ground, and in an intermediate pose.
-
-The FDD dataset is composed of 191 videos, of which 143 are falls, recorded from a surveillance camera perspective by a single RGB camera. With every frame annotated between fall and not fall.
-
-To enable a comparison with other works, we evaluated our method through three metrics: (i) sensitivity, which reflects the true positive rate; (ii) specificity, also known as the true negative rate; and (iii) accuracy, which represents the overall performance of the method.
-
-We used a learning rate of $10^{-4}$, 500 epochs, 5-fold cross-validation, mini-batches of $2^{10}$, and Adam optimization.
+Each frame is labeled in three categories: if the person is lying on the ground, not lying on the ground, and in an intermediate pose.\par
+The FDD dataset is composed of 191 videos, of which 143 are falls, recorded from a surveillance camera perspective by a single RGB camera. With every frame annotated between fall and not fall.\par
+To enable a comparison with other works, we evaluated our method through three metrics: (i) sensitivity, which reflects the true positive rate; (ii) specificity, also known as the true negative rate; and (iii) accuracy, which represents the overall performance of the method.\par
+We used a learning rate of $10^{−4}$ , 500 epochs, 5-fold cross-validation, mini-batches of $2^{10}$ , and Adam optimization.
 We also experimented with different classes and weights, however, further tuning of the hyper-parameters we were able to keep both classes on the same weight.
-As explained in Section~\ref{sec:classification}, a double SVM is used to ensemble the outputs.
-
+As explained in Section~\ref{sec:classification}, a double SVM is used to ensemble the outputs.\par
 Tables~\ref{tab:urfd-ensem} and~\ref{tab:urfd-our-their} show the results obtained on the URFD dataset.
@@
 The optical flow single-stream acquired the highest accuracy, at 97.57\%, and the multi-stream was still able to outperform it, at 98.84\%.
-Table~\ref{tab:urfd-our-their} compares our result with other works in the literature, whilst not all works measured their sensitivity and specificity, all of them reported their accuracy.
-
+Table~\ref{tab:urfd-our-their} compares our result with other works in the literature, whilst not all works measured their sensitivity and specificity, all of them reported their accuracy.\par
 The accuracy and specificity of our method performed better than most and kept the same 100\% sensitivity.
-The approach developed by Lu et al.~\cite{lu2019deep} was the only work that outperformed ours.
-We conjecture that the reason for such is the temporal importance to detect a fall event, and their usage of LSTM would better cater this relationship.
-
-\begin{table*}[!htb]
-\renewcommand{\tabcolsep}{2.5mm}
-\renewcommand{\arraystretch}{1.15}
-\centering
-\caption{Results on URFD dataset for single-stream \textit{vs} multi-stream (descending order of accuracy).}
-\label{tab:urfd-ensem}
-\begin{tabular}{lccc}
-\toprule
- & Sensitivity (\%) & Specificity (\%) & Accuracy (\%) \\
- \midrule
- OF + RGB + Saliency & \textbf{100} & \textbf{98.77} & \textbf{98.84} \\
- Optical Flow        & \textbf{100} & 97.42          & 97.57          \\
- RGB                 & \textbf{100} & 96.35          & 96.56          \\
- Saliency            & 93.67        & 93.39          & 93.40          \\
- \bottomrule
-\end{tabular}
-\end{table*}
-
-\begin{table*}[!htb]
-\renewcommand{\tabcolsep}{2.5mm}
-\renewcommand{\arraystretch}{1.15}
-\centering
-\caption{Comparison of the results on URFD datasets (descending order of accuracy).}
-\label{tab:urfd-our-their}
-\begin{tabular}{lccc}
- \toprule
-                                                      & Sensitivity (\%)  & Specificity (\%)  & Accuracy (\%)  \\
- \midrule
- Lu et al.~\cite{lu2019deep}                          & -                 & -                 & \textbf{99.27} \\
- Ours                                                 & \textbf{100}      & \textbf{98.77}    & 98.84          \\
- Carneiro et al.~\cite{Carneiro2019}                  & \textbf{100}      & 98.61             & 98.77          \\
- Panahi et al.~\cite{panahi2018human}                 & 97.05             & 97.02             & 97.14          \\
- Zerrouki and Houacine~\cite{zerrouki2018combined}    & -                 & -                 & 96.88          \\
- Harrou et al.~\cite{harrou2017vision}                & -                 & -                 & 96.66          \\
- Abobakr et al.~\cite{abobakr2017skeleton}            & \textbf{100}      & 0.91              & 96.00          \\
- Bhandari et al.~\cite{bhandari2017novel}             & 96.66             & -                 & 95.71          \\
- Kwolek and Kepski~\cite{kwolek2015improving}         & \textbf{100}      & 92.50             & 95.71          \\
- N\'u\~nez-Marcos et al.~\cite{nunez2017vision}       & \textbf{100}      & 92.00             & 95.00          \\
- Sase et al.~\cite{sase2018human}                     & 81.00             & -                 & 90.00          \\
- \bottomrule
-\end{tabular}
-\end{table*}
-
+The approach developed by Lu et al.~\cite{lu2018deep} was the only work that outperformed ours.
+We conjecture that the reason for such is the temporal importance to detect a fall event, and their usage of LSTM would better cater this relationship.\par
 Tables~\ref{tab:fdd-ensem} and~\ref{tab:fdd-our-their} report the results extracted from the FDD dataset.
@@
 Our results also confirmed the findings of Wang et al.~\cite{wang2015towards} since each feature stream did not perform great on their own, however, when applied together, they contributed to the state-of-the-art results towards fall detection.
-
-\begin{table*}[!htb]
-\renewcommand{\tabcolsep}{2.5mm}
-\renewcommand{\arraystretch}{1.15}
+\begin{table*}[]
+\centering
+\caption{Results on URFD dataset for single-stream \textit{vs} multi-stream (descending order of accuracy).}
+\label{tab:urfd-ensem}
+\begin{tabular}{llcccl}
+\hline
+ &  & Sensitivity (\%) & Specificity (\%) & Accuracy (\%) &  \\ \hline
+ & OF + RGB + Sal & \textbf{100} & \textbf{98.77} & \textbf{98.84} &  \\
+ & Optical Flow & \textbf{100} & 97.42 & 97.57 &  \\
+ & RGB & \textbf{100} & 96.35 & 96.56 &  \\
+ & Saliency & 93.67 & 93.39 & 93.40 &  \\ \hline
+\end{tabular}
+\end{table*}
+\begin{table*}[]
+\centering
+\caption{Comparison of the results on URFD datasets (descending order of accuracy).}
+\label{tab:urfd-our-their}
+\begin{tabular}{llcccl}
+\hline
+ &                                                      & Sensitivity (\%)  & Specificity (\%)  & Accuracy (\%)     & \\ \hline
+ & Lu et al.~\cite{lu2018deep}                          & -                 & -                 & \textbf{99.27}    & \\
+ & Ours                                                 & \textbf{100}      & \textbf{98.77}    & 98.84             & \\
+ & Carneiro et al.~\cite{carneiro2019multi}                                                 & \textbf{100}      & \textbf{98.61}    & 98.77             & \\
+ & Panahi et al.~\cite{panahi2018human}                 & 97.05             & 97.02             & 97.14             & \\
+ & Zerrouki and Houacine~\cite{zerrouki2018combined}    & -                 & -                 & 96.88             & \\
+ & Harrou et al.~\cite{harrou2017vision}                & -                 & -                 & 96.66             & \\
+ & Abobakr et al.~\cite{abobakr2017skeleton}            & \textbf{100}      & 0.91              & 96.00             & \\
+ & Bhandari et al.~\cite{bhandari2017novel}             & 96.66             & -                 & 95.71             & \\
+ & Kwolek and Kepski~\cite{kwolek2015improving}         & \textbf{100}      & 92.50             & 95.71             & \\
+ & N\'u\~nez-Marcos et al.~\cite{nunez2017vision}       & \textbf{100}      & 92.00             & 95.00             & \\
+ & Sase et al.~\cite{sase2018human}                     & 81.00             & -                 & 90.00             & \\ \hline
+\end{tabular}
+\end{table*}
+\begin{table*}[]
 \centering
@@
 \label{tab:fdd-ensem}
-\begin{tabular}{lccc}
-\toprule
- & Sensitivity (\%) & Specificity (\%) & Accuracy (\%) \\
- \midrule
- OF + RGB + Saliency & \textbf{99.43} & \textbf{99.55} & \textbf{99.51} \\
- Optical Flow        & 99.07          & 99.12          & 99.11          \\
- RGB                 & 98.85          & 98.41          & 98.55          \\
- Saliency            & 88.39          & 92.40          & 91.25          \\
- \bottomrule
+\begin{tabular}{llcccl}
+\hline
+ &  & Sensitivity (\%) & Specificity (\%) & Accuracy (\%) &  \\ \hline
+ & OF + RGB + Sal & \textbf{99.43} & \textbf{99.55} & \textbf{99.51} &  \\
+ & Optical Flow & 99.07             & 99.12             & 99.11             &  \\
+ & RGB & 98.85             & 98.41             & 98.55             &  \\
+ & Saliency & 88.39             & 92.40             & 91.25             & \\ \hline
 \end{tabular}
 \end{table*}
-
-\begin{table*}[!htb]
-\renewcommand{\tabcolsep}{2.5mm}
-\renewcommand{\arraystretch}{1.15}
+\begin{table*}[]
 \centering
@@
 \label{tab:fdd-our-their}
-\begin{tabular}{lccc}
-\toprule
- & Sensitivity (\%)  & Specificity (\%)  & Accuracy (\%) \\
- \midrule
- Ours                                                 & 99.43             & 99.55             & \textbf{99.51} \\
- Lu et al.~\cite{lu2019deep}                          & -                 & -                 & 99.36          \\
- Sehairi et al.~\cite{sehairi2018elderly}             & -                 & -                 & 98.91          \\
- Carneiro et al.~\cite{Carneiro2019}                  & \textbf{99.9}     & 98.32             & 98.43          \\
- Zerrouki and Houacine~\cite{zerrouki2018combined}    & -                 & -                 & 97.02          \\
- Harrou et al.~\cite{harrou2017vision}                & -                 & -                 & 97.02          \\
- Charfi et al.~\cite{charfi2012definition}            & 98.0              & \textbf{99.60}    & -              \\
- N\'u\~nez-Marcos et al.~\cite{nunez2017vision}       & 99.0              & 97.00             & 97.00          \\
-\bottomrule
+\begin{tabular}{llcccl}
+\hline
+ &                                                      & Sensitivity (\%)  & Specificity (\%)  & Accuracy (\%)     & \\ \hline
+ & Ours                                                 & \textbf{99.43}    & 99.55             & \textbf{99.51}    & \\
+ & Lu et al.~\cite{lu2018deep}                          & -                 & -                 & 99.36             & \\
+ & Sehairi et al.~\cite{sehairi2018elderly}             & -                 & -                 & 98.91             & \\
+ & Carneiro et al.~\cite{carneiro2019multi}                                                 & \textbf{99.9}      & \textbf{98.32}    & 98.43             & \\
+ & Zerrouki and Houacine~\cite{zerrouki2018combined}    & -                 & -                 & 97.02             & \\
+ & Harrou et al.~\cite{harrou2017vision}                & -                 & -                 & 97.02             & \\
+ & Charfi et al.~\cite{charfi2012definition}            & 98.0              & \textbf{99.60}    & -                 & \\
+ & N\'u\~nez-Marcos et al.~\cite{nunez2017vision}       & 99.0              & 97.00             & 97.00             & \\ \hline
 \end{tabular}
@@
 The proposed method was evaluated on the RFD and FDD datasets.
-Our solution outperformed the related literature in most cases, indicating that multi-stream approaches and the selected features can be useful to detect human fall events.
-
+Our solution outperformed the related literature in most cases, indicating that multi-stream approaches and the selected features can be useful to detect human fall events.\par
 It is worth discussing the selected features and some literature results.
 As et al.~\cite{chernbumroong2012elderly} noticed that privacy concerns might arise on video-based approaches, the selected features can conceal one's identity.
-Despite their feature performance, both optical flow and saliency map are timely and computationally intensive to extract, which would halt their implementation in a real-time system.
-
+Despite their feature performance, both optical flow and saliency map are timely and computationally intensive to extract, which would halt their implementation in a real-time system.\par
 Considering the goal of this work in exploring features to the fall detection problem, it is relevant to weight their extraction process against their results.
 Regarding other works in the literature, some seemed to dismiss the importance of the sensitivity metric, which quantifies the avoidance of false negatives.
-A World Health Organization report~\cite{who2007report} enlightens the severity of an elderly fall, thus the importance of a high sensitivity metric.
-
+A World Health Organization report~\cite{who2007report} enlightens the severity of an elderly fall, thus the importance of a high sensitivity metric.\par
 From the results reported in Tables~\ref{tab:urfd-our-their} and~\ref{tab:fdd-our-their}, it is possible to observe a saturation of these datasets, and as also reported by Chernbumroong et al.~\cite{chernbumroong2012elderly}, systems trained on artificial environments did not perform as well on real-life scenarios.
@@
 
-\section*{Acknowledgments}
+\section*{Acknowledgment}
 
 Omitted for blind review.
+
+%\begin{thebibliography}{00}
+%\end{thebibliography}
 
@@
 \end{document}
+
+%  3. Comments to authors
+
+%     Fall Detection in Video Sequences Based on a Three-Stream Convolutional Neural Network
+
+%     This paper proposes and evaluates the multi-stream approach for fall detection applications.
+Fall detection is an important and challenging application.
+This paper applies the standard technique used in action recognition for fall detection and shows strong results in two datasets URFD and FDD.
+
+%     Pros:
+%     The proposed approach gives decent results in two fall detection dataset.
+
+%     The proposed multi-stream approach is technically sound, and I also appreciate the ablation study results.
+
+%     Cons:
+%     I think this paper does not address the cross-dataset problem.
+Ideally, it would be better to train the model on one or two scenarios but test on the other unseen situations.
+This evaluation helps to understand if the proposed approach can generalize well for practical use.
+
+%     The other problem with the proposed approach is the lack of an important technical justification.
+It seems that the saliency map is an interesting attemp.
+But I am wondering why there is no evaluation on the foreground subtraction, which appears to be more common than the saliency map.
+
+%     Regarding the technical choice, I think SVM with the pre-trained imagenet features is a bit out of the dated technique.
+The current action recognition technique often involves end-to-end training, which would be useful to evaluate.
+
+%     I concern the metrics used in this paper too.
+Why is the only accuracy used?
+Ideally, precision and recall would be useful.
+In other action recognition papers, precision@1 and precision@5 are often used too.
+
+% 3. Comments to authors
+
+%     The authors propose a multi-stream method (optical flow, saliency map, RGB data) to detect fall events.
+Firstly, optical flow, saliency map, RGB data are extracted to fed a VGG-16, respectively.
+Then an SVM is used to classify whether there was a fall event.
+They demonstrate the efficacy of the proposed model on two datasets.
+
+%     However, there are some questions.
+
+%     # Why use SVM instead of direct neural network to supervise learning.
+
+%     #Why use two SVMs, the features of three streams can be concatenated, and use an SVM to classify.
+
+%  3. Comments to authors
+
+%     In this paper, the authors proposed the use of a deep learning approach to detect fall events.
+In order to detect the falls, the authors came up with a set of handcrafted features and used in conjunction with VGG-16 architecture.
+A SVM is used as a final classification layer on top of the VGG-16 outputs.
+Finally, different sets of architectures are trained and compared in terms of performance.
+
+%     Good Points:
+
+%     1. The problem formulation and the motivation behind the proposed work is interesting. All the sections are well written with minimal grammatical errors.
+
+%     2. A well described background on optical flow, saliency map and transfer learning.
+%     Experimentation setup and hyperparameters are detailed in a very clear and transparent manner.
+
+%     3. The proposed approach was experimented on two publicly available datasets and the results are compared properly compared against the other existing methods in the literature.
+
+%     Comments to Address:
+
+%     1.
+No theoretical evidence was provided regarding why SVM was used as the final classification layer.
+Have you tried adding a few extra concatenation layers at the end for merging the three networks instead of SVM, thereby resulting in a more efficient backpropagation?
+
+%     2. It would be interesting to know if the authors have explored any other architectures instead of VGG-16, which might be more suitable for these features.
+
+%     3. It would be better to add statistical test results in order to verify the statistical significance of the proposed method over the other methods.
+
+%     Overall, I would recommend this paper as an accept, and the paper could be improved by adding a bit of theoretical evidence on the proposed work and describing about the pros and cons of the alternative approaches, and also by adding statistical significance results.

### 2019-10-07 2019_ICMLA/paper.tex
Version addressing revisors complaints and sent to Helio, so he can correct

@@
 \begin{abstract}
-With falls being at the same time more susceptible in advanced ages and the second most common cause of accidental death to elders, detecting falls became a crucial research topic to an aging population~\cite{who2007report}.
+Human falls are at the same time more susceptible in advanced ages and the second most common cause of accidental death to elders, detecting falls became a crucial research topic to an aging population~\cite{who2007report}.
 To this effect, we propose and evaluate the employment of a multi-stream approach to detect fall events.
@@
 \section{Introduction}
-With deteriorating health in advanced ages, even a minor fall can trigger a chain reaction of serious psychological and physical injuries to the elder population.
-Hence, the motivation for ambient assistant living solutions to both avoids falling from occurring and reducing the interval between a fall and help arrival.\par
+Advanced ages will deteriorate an individual's health, and even a minor fall can trigger a chain reaction of serious psychological and physical injuries to the elder population.
+Hence, the motivation for ambient assistant living solutions to both avoid falling from occurring and reducing the interval between a fall and help arrival.\par
 The studies that detect falls as soon as they happen can be split into two main categories: hardware reliant solutions and vision based ones.
@@
 Huang et al.~\cite{huang2018video} extracted the human pose with OpenPose and classified it with a VGG-16 architecture.
-Núñez-Marcos et al.~\cite{nunez2017vision} extracted the dense optical flow (OF) and also served it to a VGG-16.
+N\'u\~nez-Marcos et al.~\cite{nunez2017vision} extracted the dense optical flow (OF) and also served it to a VGG-16.
 Anishchenko et al.~\cite{anishchenko2018machine} employed a modified AlexNet as a classifier.
@@
 The extraction process considers a video frame as $I$ and $I(x, y, t)$ a pixel in this frame.
-Another frame collected $dt$ time later, and the distance that the same pixel moved $(dx, dy)$ is described in Equation~\ref{eq:of-dist}.
+Another frame collected $dt$ time later, and the distance that the same pixel moved $(dx, dy)$ is described in Equation~\ref{eq:of-dist}.\par
 \begin{equation}
@@
 Equation~\ref{eq:of} is formed after applying a Taylor series approximation of right-hand side and dividing by $dt$, $f_t$ is the gradient given time, $f_x$ , $f_y$ , $u$, and $v$ are given in Equation~\ref{eq:of-grad}.
-Values of $u$ and $v$ can be achieved by different methods, such as the classical Lucas-Kanade~\cite{jain2018abnormal} or the one used in this work: Gunnar-Farnebäck~\cite{lowhur2015dense}.
+Values of $u$ and $v$ can be achieved by different methods, such as the classical Lucas-Kanade~\cite{jain2018abnormal} or the one used in this work: Gunnar-Farneb\"ack~\cite{lowhur2015dense}.
 \begin{equation}
@@
 As further detailed in the following subsections, we used an ensemble of VGG-16s to classify between fall and not fall in video sequences.
+Since detecting falls needs to operate on real-time bases, we chose an architecture with depth to inference-speed balance, hence the VGG16 architecture.
 Figure~\ref{fig:overview} illustrates an overview of the proposed method.
@@
 The reasoning being that the network would initially learn low-level features from the ImageNet classes, and focus these features on human activities with the UCF101 videos, Figure~\ref{fig:pre14}.
-Núñez-Marcos et al.~\cite{nunez2017vision} executed this step and released their weight files publicly.\par
+N\'u\~nez-Marcos et al.~\cite{nunez2017vision} executed this step and released their weight files publicly.\par
 \begin{figure}[htbp]
@@
 Wang et al.~\cite{wang2015towards} reported that networks employing multi-stream classifiers outperformed their single-streamed peers.
-Inspired on this finding, an SVM classifier fed with the outputs of each stream, vectors between 0 and 1, generates a ($x$, $y$, $z$) vector.
+Inspired on this finding, an SVM classifier was chosen for its inference speed over a neural network, again aiming to approximate the output to real-time.
+We used an SVM classifier fed with the outputs of each stream, vectors between 0 and 1, that generates a ($x$, $y$, $z$) vector.
 A second SVM uses this vector to classify between fall and not fall (Figure~\ref{fig:overview}).
+This double SVM approach is executed so that the first SVM will classify the input, and the second SVM will weight which stream or streams are more important to detect a fall event.
 
@@
 Furthermore, given the neural networks capability of learning relevant features to describe their input, the RGB frame itself was fed to the third stream.
-\paragraph{Optical Flow} represents the temporal relation between frames and to fully gather this property it was used as a stack of optical flows on top of a sliding window of frames, as suggested by Núñez-Marcos et al.~\cite{nunez2017vision}.
-The sliding window has a size of $L$ frames and gathers 2$L$ components ($L$ horizontal ($d_t^x$) + $L$ vertical ($d_t^y$) optical flow component vector fields) creating a stack $O$ = \{$d_t^x$, $d_t^y$, $d_{t+1}^x$, $d_{t+1}^y$, ..., $d_{t+L}^x$, $d_{t+L}^y$ \}.
+\paragraph{Optical Flow} represents the temporal relation between frames and to fully gather this property it was used as a stack of optical flows on top of a sliding window of frames, as suggested by N\'u\~nez-Marcos et al.~\cite{nunez2017vision}.
+The sliding window has a size of $L$ frames and gathers 2$L$ components ($L$ horizontal ($d_t^x$) + $L$ vertical ($d_t^y$) optical flow component vector fields) creating a stack $O$ = \{$d_t^x$, $d_t^y$, $d_{t+1}^x$, $d_{t+1}^y$, ..., $d_{t+L}^x$, $d_{t+L}^y$\}.
 The total number of stacks is given by $N$-$L$+$1$, where $N$ is the number of frames in a video.
@@
 \end{figure}
-\paragraph{Saliency Map} is composed of pixels varying from 0 to 1, and was fed as a gray-scale image to the network. Figure~\ref{fig:sal} shows and extracted example.
+\paragraph{Saliency Map} represents the attention region in a frame, it was chosen over other techniques of silhouetting as it can focus on key regions in the human shape, instead of the whole foreground region of the frame.
+It is composed of pixels varying from 0 to 1 and was fed as a gray-scale image to the network.
+Figure~\ref{fig:sal} shows and extracted example.
 \begin{figure}[htbp]
@@
 We used a learning rate of $10^{−4}$ , 500 epochs, 5-fold cross-validation, mini-batches of $2^{10}$ , and Adam optimization.
-We also experimented with different classes and weights, however, further tuning of the hyper-parameters we were able to keep both classes on the same weight.
+We also experimented with different classes weights, however, further tuning of the hyper-parameters we were able to keep both classes on the same weight.
 As explained in Section~\ref{sec:classification}, a double SVM is used to ensemble the outputs.\par
@@
 In Table~\ref{tab:urfd-ensem}, we compare each single-stream feature with their multi-stream counterpart.
-The optical flow single-stream acquired the highest accuracy, at 97.57\%, and the multi-stream was still able to outperform it, at 98.84\%.
+The optical flow single-stream acquired the highest accuracy, at 97.57\%, however, the multi-stream was still able to outperform it, at 98.84\%.
 Table~\ref{tab:urfd-our-their} compares our result with other works in the literature, whilst not all works measured their sensitivity and specificity, all of them reported their accuracy.\par
@@
 We conjecture that the reason for such is the temporal importance to detect a fall event, and their usage of LSTM would better cater this relationship.\par
-Tables~\ref{tab:fdd-ensem} and~\ref{tab:fdd-our-their} report the results extracted from the FDD dataset.
-Homologous to the URFD report, Table~\ref{tab:fdd-ensem} compares each single-stream with the multi-stream approach.
-The multi-stream achieved 99.51\% accuracy, and the highest single-stream score was again the optical flow, with 99.11\%.
-When comparing our results against the literature, in Table~\ref{tab:fdd-our-their}, ours outperformed every other one, regarding accuracy and sensitivity.
-It was 0.05\% worse than Charfi et al.'s~\cite{charfi2013optimised} specificity.
-Our results also confirmed the findings of Wang et al.~\cite{wang2015towards} since each feature stream did not perform great on their own, however, when applied together, they contributed to the state-of-the-art results towards fall detection.
 \begin{table*}[]
@@
 \end{table*}
+Tables~\ref{tab:fdd-ensem} and~\ref{tab:fdd-our-their} report the results extracted from the FDD dataset.
+Homologous to the URFD report, Table~\ref{tab:fdd-ensem} compares each single-stream with the multi-stream approach.
+The multi-stream achieved 99.51\% accuracy, and the highest single-stream score was again the optical flow, with 99.11\%.
+When comparing our results against the literature, in Table~\ref{tab:fdd-our-their}, ours outperformed every other one, regarding accuracy and sensitivity.
+It was 0.05\% worse than Charfi et al.'s~\cite{charfi2013optimised} specificity.
+Our results also confirmed the findings of Wang et al.~\cite{wang2015towards} since each feature stream did not perform great on their own, however, when applied together, they contributed to the state-of-the-art results towards fall detection.
 
@@
 \end{document}
-
-%  3. Comments to authors
-
-%     Fall Detection in Video Sequences Based on a Three-Stream Convolutional Neural Network
-
-%     This paper proposes and evaluates the multi-stream approach for fall detection applications.
-Fall detection is an important and challenging application.
-This paper applies the standard technique used in action recognition for fall detection and shows strong results in two datasets URFD and FDD.
-
-%     Pros:
-%     The proposed approach gives decent results in two fall detection dataset.
-
-%     The proposed multi-stream approach is technically sound, and I also appreciate the ablation study results.
-
-%     Cons:
-%     I think this paper does not address the cross-dataset problem.
-Ideally, it would be better to train the model on one or two scenarios but test on the other unseen situations.
-This evaluation helps to understand if the proposed approach can generalize well for practical use.
-
-%     The other problem with the proposed approach is the lack of an important technical justification.
-It seems that the saliency map is an interesting attemp.
-But I am wondering why there is no evaluation on the foreground subtraction, which appears to be more common than the saliency map.
-
-%     Regarding the technical choice, I think SVM with the pre-trained imagenet features is a bit out of the dated technique.
-The current action recognition technique often involves end-to-end training, which would be useful to evaluate.
-
-%     I concern the metrics used in this paper too.
-Why is the only accuracy used?
-Ideally, precision and recall would be useful.
-In other action recognition papers, precision@1 and precision@5 are often used too.
-
-% 3. Comments to authors
-
-%     The authors propose a multi-stream method (optical flow, saliency map, RGB data) to detect fall events.
-Firstly, optical flow, saliency map, RGB data are extracted to fed a VGG-16, respectively.
-Then an SVM is used to classify whether there was a fall event.
-They demonstrate the efficacy of the proposed model on two datasets.
-
-%     However, there are some questions.
-
-%     # Why use SVM instead of direct neural network to supervise learning.
-
-%     #Why use two SVMs, the features of three streams can be concatenated, and use an SVM to classify.
-
-%  3. Comments to authors
-
-%     In this paper, the authors proposed the use of a deep learning approach to detect fall events.
-In order to detect the falls, the authors came up with a set of handcrafted features and used in conjunction with VGG-16 architecture.
-A SVM is used as a final classification layer on top of the VGG-16 outputs.
-Finally, different sets of architectures are trained and compared in terms of performance.
-
-%     Good Points:
-
-%     1. The problem formulation and the motivation behind the proposed work is interesting. All the sections are well written with minimal grammatical errors.
-
-%     2. A well described background on optical flow, saliency map and transfer learning.
-%     Experimentation setup and hyperparameters are detailed in a very clear and transparent manner.
-
-%     3. The proposed approach was experimented on two publicly available datasets and the results are compared properly compared against the other existing methods in the literature.
-
-%     Comments to Address:
-
-%     1.
-No theoretical evidence was provided regarding why SVM was used as the final classification layer.
-Have you tried adding a few extra concatenation layers at the end for merging the three networks instead of SVM, thereby resulting in a more efficient backpropagation?
-
-%     2. It would be interesting to know if the authors have explored any other architectures instead of VGG-16, which might be more suitable for these features.
-
-%     3. It would be better to add statistical test results in order to verify the statistical significance of the proposed method over the other methods.
-
-%     Overall, I would recommend this paper as an accept, and the paper could be improved by adding a bit of theoretical evidence on the proposed work and describing about the pros and cons of the alternative approaches, and also by adding statistical significance results.

### 2019-10-27 2019_ICMLA/paper.tex
helios review

--- 2019-09-12 paper.tex
@@
-\documentclass[conference]{IEEEtran}
+\documentclass[10pt, conference, compsocconf]{IEEEtran}
 
@@
 % The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
-\usepackage{cite}
+\usepackage{times}
+\usepackage[sort,nocompress]{cite}
 \usepackage{amsmath,amssymb,amsfonts}
@@
 \usepackage{textcomp}
+\usepackage{xcolor}
 \usepackage{booktabs}
+\usepackage{array}
+\usepackage{url}
+\usepackage{balance}
 \usepackage{flushend}
-\usepackage{xcolor}
+
 \def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
@@
 \begin{document}
-
 \sloppy
@@
 
-\title{Fall Detection in Video Sequences \\ Based on a Three-Stream Convolutional \\ Neural Network}
+\title{Fall Detection in Video Sequences Based on a \\ Three-Stream Convolutional Neural Network}
 
-\author{\vspace*{0.0cm}}
-
-%\author{\IEEEauthorblockN{1\textsuperscript{st} Guilherme Vieira Leite}
-%\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
-%\textit{name of organization (of Aff.)}\\
-%City, Country \\
-%email address}
-%\and
-%\IEEEauthorblockN{2\textsuperscript{nd} Gabriel Pellegrino da Silva}
-%\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
-%\textit{name of organization (of Aff.)}\\
-%City, Country \\
-%email address}
-%\and
-%\IEEEauthorblockN{2\textsuperscript{nd} Helio Pedrini}
-%\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
-%\textit{name of organization (of Aff.)}\\
-%City, Country \\
-%email address}
-%}
+\author{
+  \IEEEauthorblockN{
+    Guilherme Vieira Leite\IEEEauthorrefmark{1}\IEEEauthorrefmark{2},
+    Gabriel Pellegrino da Silva\IEEEauthorrefmark{1}\IEEEauthorrefmark{2},
+    Helio Pedrini\IEEEauthorrefmark{1}} \\
+  \IEEEauthorblockA{
+    \IEEEauthorrefmark{1}Institute of Computing, University of Campinas (UNICAMP), Campinas, SP, Brazil, 13083-852}
+    \IEEEauthorrefmark{2}Semantix Brasil, S\~ao Paulo, SP, Brazil, 03178-200
+}
 
@@
 \begin{abstract}
-With falls being at the same time more susceptible in advanced ages and the second most common cause of accidental death to elders, detecting falls became a crucial research topic to an aging population~\cite{who2007report}.
+Human falls are more susceptible in advanced ages and the second most common cause of accidental death to elders, because of the later detecting falls became a crucial research topic to an aging population~\cite{who2007report}.
 To this effect, we propose and evaluate the employment of a multi-stream approach to detect fall events.
@@
 
-With deteriorating health in advanced ages, even a minor fall can trigger a chain reaction of serious psychological and physical injuries to the elder population.
-Hence, the motivation for ambient assistant living solutions to both avoids falling from occurring and reducing the interval between a fall and help arrival.
+Advanced ages will deteriorate an individual's health, and even a minor fall can trigger a chain reaction of serious psychological and physical injuries to the elder population.
+Hence, the motivation for ambient assistant living solutions to both avoid falling from occurring and reducing the interval between a fall and help arrival~\cite{carneiro2019multi,carneiro2019deep}.
 
@@
 Bhandari et al.~\cite{bhandari2017novel} determined regions of interest via Shi-Tomasi, tracked them using Lucas-Kanade and set a threshold on the region of interest's speed and motion and also Albawendi et al.~\cite{albawendi2018video} who used a threshold activation on a silhouette shape.
+
 Another commonly used classification technique is the support vector machine (SVM), used by Harrou et al.~\cite{harrou2017vision}, that fed a feature extractor with the subject segmented from the frame.
@@
 Abobakr et al.~\cite{abobakr2017skeleton} also subtracted the background from depth images, applied a random decision forest to estimate the subject's posture, and an SVM to classify it.
+
 Regarding the subject's privacy, both Edgcomb et al.~\cite{edgcomb2012automated} and Lin et al.~\cite{lin2013fall} investigated privacy-prone features, such as blurring, silhouetting, and covering the body with shapes.
-Lu et al.~\cite{lu2019deep} employed a 3D convolutional neural network (CNN) followed by a long short-term memory (LSTM).
+Lu et al.~\cite{lu2018deep} employed a 3D convolutional neural network (CNN) followed by a long short-term memory (LSTM).
 Huang et al.~\cite{huang2018video} extracted the human pose with OpenPose and classified it with a VGG-16 architecture.
@@
 Anishchenko et al.~\cite{anishchenko2018machine} employed a modified AlexNet as a classifier.
+
 A few different approaches were also reported, such as K-nearest neighbor classifiers by Sehairi et al.~\cite{sehairi2018elderly} and Kwolek et al.~\cite{kwolek2015improving}.
@@
 
-Optical flow is a handcrafted feature that conveys movement information between two frames of a video, either by object or camera movement.
-Its ability to describe movement enables this feature to support the temporal aspect of a fall event in a deep network.
-
 \begin{figure*}[!htb]
-\centerline{\includegraphics[width=0.55\linewidth]{figures/overview.png}}
+\centerline{\includegraphics[width=0.57\linewidth]{figures/overview.png}}
 \caption{Main components of the proposed fall detection method.}
@@
 \end{figure*}
+
+Optical flow is a handcrafted feature that conveys movement information between two frames of a video, either by object or camera movement.
+Its ability to describe movement enables this feature to support the temporal aspect of a fall event in a deep network.
 
@@
 
-Equation~\ref{eq:of} is formed after applying a Taylor series approximation of right-hand side and dividing by $dt$, $f_t$ is the gradient given time, $f_x$, $f_y$, $u$, and $v$ are given in Equation~\ref{eq:of-grad}.
-Values of $u$ and $v$ can be achieved by different methods, such as the classical Lucas-Kanade~\cite{jain2018abnormal} or the one used in this work: Gunnar-Farneb{\"a}ck~\cite{lowhur2015dense}.
+Equation~\ref{eq:of} is formed after applying a Taylor series approximation of right-hand side and dividing by $dt$, $f_t$ is the gradient given time, $f_x$ , $f_y$ , $u$, and $v$ are given in Equation~\ref{eq:of-grad}.
+Values of $u$ and $v$ can be achieved by different methods, such as the classical Lucas-Kanade~\cite{jain2018abnormal} or the one used in this work: Gunnar-Farneb\"ack~\cite{lowhur2015dense}.
 \begin{equation}
@@
 Its extraction can occur in many ways, one of those being the practice of feeding an image $I$ and its class label $c$ to the network, then, freezing the weights on the network and compute the gradients of $c$ to the pixels of $I$.
-Consider $S_c(I)$ to be the class score function for an image $I$ and, for this simple explanation, that it is a simple linear function, $S_c(I) = w_c^{T} + b_c$.
+Consider $S_c(I)$ to be the class score function for an image $I$ and, for this simple explanation, that it is a simple linear function, $S_c(I) = w_c^T + b_c$.
 With $w$ being the weights of the network and $b$ the bias, it is possible to notice that the magnitude of elements of $w$ affects the importance of the corresponding pixels in $I$ with class $c$.
@@
 \begin{figure}[!htb]
-\centerline{\includegraphics[width=0.96\linewidth]{figures/pre14.png}}
-\caption{Deep layers being trained on ImageNet and UCF101 datasets.}
+\centerline{\includegraphics[width=0.9\linewidth]{figures/pre14.png}}
+\caption{Deep layers being trained on ImagetNet and UCF101.}
 \label{fig:pre14}
@@
 
-We froze the 14 initial layer's weights and fine-tuned the last two fully connected layers were fine-tuned, with dropout regularization.
-Each stream executed this last fine-tuning step, totaling three executions (Figure~\ref{fig:pos14}).
+We froze the 14 initial layer's weights and fine-tuned the
+last two fully connected layers were fine-tuned, with dropout regularization. Each stream executed this last fine-tuning step, totaling three executions (Figure~\ref{fig:pos14}).
 
 \begin{figure}[!htb]
-\centerline{\includegraphics[width=0.43\linewidth]{figures/pos14.png}}
-\caption{Fully connected layer training.}
+\centerline{\includegraphics[width=0.4\linewidth]{figures/pos14.png}}
+\caption{Fully connected layers training.}
 \label{fig:pos14}
@@
 Wang et al.~\cite{wang2015towards} reported that networks employing multi-stream classifiers outperformed their single-streamed peers.
-Inspired on this finding, an SVM classifier fed with the outputs of each stream, vectors between 0 and 1, generates a ($x$, $y$, $z$) vector.
+Inspired on this finding, an SVM classifier was chosen for its inference speed over a neural network, again aiming to approximate the output to real-time.
+We used an SVM classifier fed with the outputs of each stream, vectors between 0 and 1, that generates a ($x$, $y$, $z$) vector.
 A second SVM uses this vector to classify between fall and not fall (Figure~\ref{fig:overview}).
+This double SVM approach is executed so that the first SVM will classify the input, and the second SVM will weight which stream or streams are more important to detect a fall event.
 
-\subsection{Streams Input}
+\subsection{Input Streams}
 
@@
 \paragraph{Optical Flow} represents the temporal relation between frames and to fully gather this property it was used as a stack of optical flows on top of a sliding window of frames, as suggested by N\'u\~nez-Marcos et al.~\cite{nunez2017vision}.
-The sliding window has a size of $L$ frames and gathers 2$L$ components ($L$ horizontal ($d_t^x$) + $L$ vertical ($d_t^y$) optical flow component vector fields) creating a stack $O$ = \{$d_t^x$, $d_t^y$, $d_{t+1}^x$, $d_{t+1}^y$, ..., $d_{t+L}^x$, $d_{t+L}^y$ \}.
+The sliding window has a size of $L$ frames and gathers 2$L$ components ($L$ horizontal ($d_t^x$) + $L$ vertical ($d_t^y$) optical flow component vector fields) creating a stack $O$ = \{$d_t^x$, $d_t^y$, $d_{t+1}^x$, $d_{t+1}^y$, ..., $d_{t+L}^x$, $d_{t+L}^y$\}.
 The total number of stacks is given by $N$-$L$+$1$, where $N$ is the number of frames in a video.
@@
 
-\paragraph{Saliency Map} is composed of pixels varying from 0 to 1, and was fed as a gray-scale image to the network. Figure~\ref{fig:sal} shows and extracted example.
+\paragraph{Saliency Map} represents the attention region in a frame, it was chosen over other techniques of silhouetting as it can focus on key regions in the human shape, instead of the whole foreground region of the frame.
+It is composed of pixels varying from 0 to 1 and was fed as a gray-scale image to the network.
+Figure~\ref{fig:sal} shows and extracted example.
 
@@
 
-Our experiments were performed on two publicly available datasets: URFD~\cite{kwolek2014human} and FDD~\cite{charfi2013optimised}.
+Our experiments were performed on two publicly available
+datasets: URFD~\cite{kepski2014human} and FDD~\cite{charfi2013optimised}.
 
@@
 
-We used a learning rate of $10^{-4}$, 500 epochs, 5-fold cross-validation, mini-batches of $2^{10}$, and Adam optimization.
-We also experimented with different classes and weights, however, further tuning of the hyper-parameters we were able to keep both classes on the same weight.
+We used a learning rate of $10^{−4}$, 500 epochs, 5-fold cross-validation, mini-batches of $2^{10}$, and Adam optimization.
+We also experimented with different classes weights, however, further tuning of the hyper-parameters we were able to keep both classes on the same weight.
 As explained in Section~\ref{sec:classification}, a double SVM is used to ensemble the outputs.
@@
 In Table~\ref{tab:urfd-ensem}, we compare each single-stream feature with their multi-stream counterpart.
-The optical flow single-stream acquired the highest accuracy, at 97.57\%, and the multi-stream was still able to outperform it, at 98.84\%.
+The optical flow single-stream acquired the highest accuracy, at 97.57\%, however, the multi-stream was still able to outperform it, at 98.84\%.
 Table~\ref{tab:urfd-our-their} compares our result with other works in the literature, whilst not all works measured their sensitivity and specificity, all of them reported their accuracy.
@@
 The accuracy and specificity of our method performed better than most and kept the same 100\% sensitivity.
-The approach developed by Lu et al.~\cite{lu2019deep} was the only work that outperformed ours.
+The approach developed by Lu et al.~\cite{lu2018deep} was the only work that outperformed ours.
 We conjecture that the reason for such is the temporal importance to detect a fall event, and their usage of LSTM would better cater this relationship.
@@
 \begin{table*}[!htb]
-\renewcommand{\tabcolsep}{2.5mm}
-\renewcommand{\arraystretch}{1.15}
 \centering
@@
 \label{tab:urfd-ensem}
-\begin{tabular}{lccc}
-\toprule
- & Sensitivity (\%) & Specificity (\%) & Accuracy (\%) \\
- \midrule
- OF + RGB + Saliency & \textbf{100} & \textbf{98.77} & \textbf{98.84} \\
- Optical Flow        & \textbf{100} & 97.42          & 97.57          \\
- RGB                 & \textbf{100} & 96.35          & 96.56          \\
- Saliency            & 93.67        & 93.39          & 93.40          \\
- \bottomrule
+\begin{tabular}{llcccl}
+\hline
+ &  & Sensitivity (\%) & Specificity (\%) & Accuracy (\%) &  \\ \hline
+ & OF + RGB + Sal & \textbf{100} & \textbf{98.77} & \textbf{98.84} &  \\
+ & Optical Flow & \textbf{100} & 97.42 & 97.57 &  \\
+ & RGB & \textbf{100} & 96.35 & 96.56 &  \\
+ & Saliency & 93.67 & 93.39 & 93.40 &  \\ \hline
 \end{tabular}
@@
 \label{tab:urfd-our-their}
-\begin{tabular}{lccc}
- \toprule
-                                                      & Sensitivity (\%)  & Specificity (\%)  & Accuracy (\%)  \\
- \midrule
- Lu et al.~\cite{lu2019deep}                          & -                 & -                 & \textbf{99.27} \\
- Ours                                                 & \textbf{100}      & \textbf{98.77}    & 98.84          \\
- Carneiro et al.~\cite{Carneiro2019}                  & \textbf{100}      & 98.61             & 98.77          \\
- Panahi et al.~\cite{panahi2018human}                 & 97.05             & 97.02             & 97.14          \\
- Zerrouki and Houacine~\cite{zerrouki2018combined}    & -                 & -                 & 96.88          \\
- Harrou et al.~\cite{harrou2017vision}                & -                 & -                 & 96.66          \\
- Abobakr et al.~\cite{abobakr2017skeleton}            & \textbf{100}      & 0.91              & 96.00          \\
- Bhandari et al.~\cite{bhandari2017novel}             & 96.66             & -                 & 95.71          \\
- Kwolek and Kepski~\cite{kwolek2015improving}         & \textbf{100}      & 92.50             & 95.71          \\
- N\'u\~nez-Marcos et al.~\cite{nunez2017vision}       & \textbf{100}      & 92.00             & 95.00          \\
- Sase et al.~\cite{sase2018human}                     & 81.00             & -                 & 90.00          \\
- \bottomrule
+\begin{tabular}{llcccl}
+\hline
+ &                                                      & Sensitivity (\%)  & Specificity (\%)  & Accuracy (\%)     & \\ \hline
+ & Lu et al.~\cite{lu2018deep}                          & -                 & -                 & \textbf{99.27}    & \\
+ & Ours                                                 & \textbf{100}      & \textbf{98.77}    & 98.84             & \\
+ & Carneiro et al.~\cite{carneiro2019multi}                                                 & \textbf{100}      & \textbf{98.61}    & 98.77             & \\
+ & Panahi et al.~\cite{panahi2018human}                 & 97.05             & 97.02             & 97.14             & \\
+ & Zerrouki and Houacine~\cite{zerrouki2018combined}    & -                 & -                 & 96.88             & \\
+ & Harrou et al.~\cite{harrou2017vision}                & -                 & -                 & 96.66             & \\
+ & Abobakr et al.~\cite{abobakr2017skeleton}            & \textbf{100}      & 0.91              & 96.00             & \\
+ & Bhandari et al.~\cite{bhandari2017novel}             & 96.66             & -                 & 95.71             & \\
+ & Kwolek and Kepski~\cite{kwolek2015improving}         & \textbf{100}      & 92.50             & 95.71             & \\
+ & N\'u\~nez-Marcos et al.~\cite{nunez2017vision}       & \textbf{100}      & 92.00             & 95.00             & \\
+ & Sase et al.~\cite{sase2018human}                     & 81.00             & -                 & 90.00             & \\ \hline
+\end{tabular}
+\end{table*}
+
+\begin{table*}[!htb]
+\centering
+\caption{Results on FDD dataset for single-stream \textit{vs} multi-stream (descending order of accuracy).}
+\label{tab:fdd-ensem}
+\begin{tabular}{llcccl}
+\hline
+ &  & Sensitivity (\%) & Specificity (\%) & Accuracy (\%) &  \\ \hline
+ & OF + RGB + Sal & \textbf{99.43} & \textbf{99.55} & \textbf{99.51} &  \\
+ & Optical Flow & 99.07             & 99.12             & 99.11             &  \\
+ & RGB & 98.85             & 98.41             & 98.55             &  \\
+ & Saliency & 88.39             & 92.40             & 91.25             & \\ \hline
+\end{tabular}
+\end{table*}
+
+\begin{table*}[!htb]
+\centering
+\caption{Comparison of the results on FDD dataset (descending order of accuracy).}
+\label{tab:fdd-our-their}
+\begin{tabular}{llcccl}
+\hline
+ &                                                      & Sensitivity (\%)  & Specificity (\%)  & Accuracy (\%)     & \\ \hline
+ & Ours                                                 & \textbf{99.43}    & 99.55             & \textbf{99.51}    & \\
+ & Lu et al.~\cite{lu2018deep}                          & -                 & -                 & 99.36             & \\
+ & Sehairi et al.~\cite{sehairi2018elderly}             & -                 & -                 & 98.91             & \\
+ & Carneiro et al.~\cite{carneiro2019multi}                                                 & \textbf{99.9}      & \textbf{98.32}    & 98.43             & \\
+ & Zerrouki and Houacine~\cite{zerrouki2018combined}    & -                 & -                 & 97.02             & \\
+ & Harrou et al.~\cite{harrou2017vision}                & -                 & -                 & 97.02             & \\
+ & Charfi et al.~\cite{charfi2012definition}            & 98.0              & \textbf{99.60}    & -                 & \\
+ & N\'u\~nez-Marcos et al.~\cite{nunez2017vision}       & 99.0              & 97.00             & 97.00             & \\ \hline
 \end{tabular}
@@
 
-\begin{table*}[!htb]
-\renewcommand{\tabcolsep}{2.5mm}
-\renewcommand{\arraystretch}{1.15}
-\centering
-\caption{Results on FDD dataset for single-stream \textit{vs} multi-stream (descending order of accuracy).}
-\label{tab:fdd-ensem}
-\begin{tabular}{lccc}
-\toprule
- & Sensitivity (\%) & Specificity (\%) & Accuracy (\%) \\
- \midrule
- OF + RGB + Saliency & \textbf{99.43} & \textbf{99.55} & \textbf{99.51} \\
- Optical Flow        & 99.07          & 99.12          & 99.11          \\
- RGB                 & 98.85          & 98.41          & 98.55          \\
- Saliency            & 88.39          & 92.40          & 91.25          \\
- \bottomrule
-\end{tabular}
-\end{table*}
-
-\begin{table*}[!htb]
-\renewcommand{\tabcolsep}{2.5mm}
-\renewcommand{\arraystretch}{1.15}
-\centering
-\caption{Comparison of the results on FDD dataset (descending order of accuracy).}
-\label{tab:fdd-our-their}
-\begin{tabular}{lccc}
-\toprule
- & Sensitivity (\%)  & Specificity (\%)  & Accuracy (\%) \\
- \midrule
- Ours                                                 & 99.43             & 99.55             & \textbf{99.51} \\
- Lu et al.~\cite{lu2019deep}                          & -                 & -                 & 99.36          \\
- Sehairi et al.~\cite{sehairi2018elderly}             & -                 & -                 & 98.91          \\
- Carneiro et al.~\cite{Carneiro2019}                  & \textbf{99.9}     & 98.32             & 98.43          \\
- Zerrouki and Houacine~\cite{zerrouki2018combined}    & -                 & -                 & 97.02          \\
- Harrou et al.~\cite{harrou2017vision}                & -                 & -                 & 97.02          \\
- Charfi et al.~\cite{charfi2012definition}            & 98.0              & \textbf{99.60}    & -              \\
- N\'u\~nez-Marcos et al.~\cite{nunez2017vision}       & 99.0              & 97.00             & 97.00          \\
-\bottomrule
-\end{tabular}
-\end{table*}
-
-\section{Conclusion and Future Work}
+\section{Conclusions and Future Work}
 \label{sec:conclusion}
@@
 
-\section*{Acknowledgments}
+\section*{Acknowledgements}
 
-Omitted for blind review.
+The authors are thankful to FAPESP (grant \#2017/12646-3), CNPq (grant \#309330/2018-7) and CAPES for their financial support, as well as Semantix Brasil for the infrastructure and support provided during the development of the present work.
 
 \bibliographystyle{IEEEtran}
-\bibliography{paper}
+\bibliography{IEEEabrv,paper}
 

### 2019-11-28 2019_ICMLA/paper.tex
Updates from Overleaf

@@
  & Ours                                                 & \textbf{100}      & \textbf{98.77}    & 98.84             & \\
- & Carneiro et al.~\cite{carneiro2019multi}                                                 & \textbf{100}      & \textbf{98.61}    & 98.77             & \\
+ & Carneiro et al.~\cite{carneiro2019multi}                                                 & \textbf{100}      & 98.61    & 98.77             & \\
  & Panahi et al.~\cite{panahi2018human}                 & 97.05             & 97.02             & 97.14             & \\
@@
  & Harrou et al.~\cite{harrou2017vision}                & -                 & -                 & 96.66             & \\
- & Abobakr et al.~\cite{abobakr2017skeleton}            & \textbf{100}      & 0.91              & 96.00             & \\
+ & Abobakr et al.~\cite{abobakr2017skeleton}            & \textbf{100}      & 91.00              & 96.00             & \\
  & Bhandari et al.~\cite{bhandari2017novel}             & 96.66             & -                 & 95.71             & \\
@@
  &                                                      & Sensitivity (\%)  & Specificity (\%)  & Accuracy (\%)     & \\ \hline
- & Ours                                                 & \textbf{99.43}    & 99.55             & \textbf{99.51}    & \\
+ & Ours                                                 & 99.43    & 99.55             & \textbf{99.51}    & \\
  & Lu et al.~\cite{lu2018deep}                          & -                 & -                 & 99.36             & \\
  & Sehairi et al.~\cite{sehairi2018elderly}             & -                 & -                 & 98.91             & \\
- & Carneiro et al.~\cite{carneiro2019multi}                                                 & \textbf{99.9}      & \textbf{98.32}    & 98.43             & \\
+ & Carneiro et al.~\cite{carneiro2019multi}                                                 & \textbf{99.9}      & 98.32    & 98.43             & \\
  & Zerrouki and Houacine~\cite{zerrouki2018combined}    & -                 & -                 & 97.02             & \\
@@
 It is worth discussing the selected features and some literature results.
-As et al.~\cite{chernbumroong2012elderly} noticed that privacy concerns might arise on video-based approaches, the selected features can conceal one's identity.
+As Chernbumroong et al.~\cite{chernbumroong2012elderly} noticed that privacy concerns might arise on video-based approaches, the selected features can conceal one's identity.
 Despite their feature performance, both optical flow and saliency map are timely and computationally intensive to extract, which would halt their implementation in a real-time system.
